---
title: "Bidding Metrics"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_tex: false
    number_sections: true
header-includes:
 \usepackage{booktabs,longtable,dcolumn}
 \usepackage{multirow,array}
 \usepackage{wrapfig,float}
 \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = FALSE, warning=FALSE,message=FALSE)
```

```{r packages,warning=FALSE,message=FALSE,include=FALSE}
library(data.table)
library(dplyr)
library(fixest)
library(zoo) # for year quarter
library(DescTools) # for winsorize
```

```{r read_data,include=FALSE}
input_path='~/Dropbox/data_quickpay/qp_replication/input/'
reg_df=fread(paste0(input_path,
                 'quickpay_delays.csv'))

working_path='~/Dropbox/data_quickpay/qp_replication/working/'
reg_df_working=fread(paste0(working_path,
               'w_clean_control.csv'))
```


```{r remove_na,include=FALSE}
reg_df=reg_df[!is.na(recipient_duns)]
```

```{r setdf, echo=FALSE, results='asis'}
reg_df[,project_signed_after_quickpay:=case_when(initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter>=as.Date('2011-04-27')~1,
                                                 initial_start_date<as.Date('2011-04-27') ~ 0,
                                                 initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter<as.Date('2011-04-27')~NaN)]

reg_df[,quarter_when_project_signed:=as.Date(as.yearqtr(as.Date(initial_start_date)),
                                                       frac = 1)]
```

```{r define_var, include=FALSE}

# Number of projects held by a contractor in a given quarter
num_proj_per_contractor_df=reg_df[,
                .(num_projects=
                    n_distinct(contract_award_unique_key)),
              by=c('recipient_duns',
                   'action_date_year_quarter')]

# Number of projects of a given task type held by a contractor in a given quarter
num_proj_same_task_df=reg_df[,
                .(num_projects_same_task=
                    n_distinct(contract_award_unique_key)),
              by=c('recipient_duns',
                   'product_or_service_code',
                   'action_date_year_quarter')]

num_proj_same_task_df=num_proj_same_task_df[order(recipient_duns,
                                                   product_or_service_code,
                                                   action_date_year_quarter)]

num_proj_per_contractor_df=num_proj_per_contractor_df[order(recipient_duns,
                                                            action_date_year_quarter)]
```

```{r get_lags, include=FALSE}

# LAG OF 1 ------------------------------

# If same contractor last quarter + same task last quarter, take lag value. Else take zero.
# Zero can indicate:
# 1. Same contractor last quarter + different task last quarter, OR
# 2. Different contractor last quarter i.e., contractor is new entrant
num_proj_same_task_df[,num_projects_same_task_lag_1:=ifelse(recipient_duns==
                                                                 lag(recipient_duns)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code),
                                                            lag(num_projects_same_task),
                                                            0)]

num_proj_per_contractor_df[,num_projects_lag_1:=ifelse(recipient_duns==lag(recipient_duns),
                                                            lag(num_projects),
                                                            0)]

# LAG OF 2 ------------------------------

# If same contractor second-to-last quarter + same task second-to-last quarter, take lag-2 value. Else take zero.
# Zero can indicate:
# 1. Same contractor second-to-last quarter + different task second-to-last quarter, OR
# 2. Different contractor second-to-last quarter i.e., contractor is new entrant
num_proj_same_task_df[,num_projects_same_task_lag_2:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,2)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code,2),
                                                            lag(num_projects_same_task,2),
                                                            0)]

num_proj_per_contractor_df[,num_projects_lag_2:=ifelse(recipient_duns==lag(recipient_duns,2),
                                                            lag(num_projects,2),
                                                            0)]


# LAG OF 3  ------------------------------

num_proj_same_task_df[,num_projects_same_task_lag_3:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,3)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code,3),
                                                            lag(num_projects_same_task,3),
                                                            0)]


num_proj_per_contractor_df[,num_projects_lag_3:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,3),
                                                            lag(num_projects,3),
                                                            0)]


# ADD IT UP  ------------------------------

num_proj_same_task_df[,num_projs_same_task_past_three_qtrs:=num_projects_same_task_lag_2+
                                                          num_projects_same_task_lag_1+
                                                          num_projects_same_task_lag_3]


num_proj_per_contractor_df[,num_projs_past_three_qtrs:=num_projects_lag_1+
                                                  num_projects_lag_2+
                                                  num_projects_lag_3]

```

```{r merge, include=FALSE}
# Merge the two datasets
num_proj_same_task_df=merge(num_proj_same_task_df,
                            num_proj_per_contractor_df,
                            by=c('recipient_duns',
                                 'action_date_year_quarter'),
                            all.x=T)
```

* Let $n^{task}_{i}=$ Number of projects of the same task held by the contractor in the three quarters before starting project $i$
* Let $n_{i}=$ Number of projects held by the contractor in the three quarters before starting project $i$

* Define:
  * Inexperienced contractor$_i$ = 1 if $n^{task}_{i}=0$ 
  * New entrant$_i$ = 1 if $n_{i}=0$
  * Level of inexperience$_{i}= 1 - \frac{n^{task}_{i}}{n_{i}}$ if $n_{i}>0$
  * Level of inexperience$_{i}= 1$ if $n_{i,k,t}=0$.
    

```{r project_quarter, include=FALSE}
# Get first quarter for every project
project_quarter=reg_df[,.(start_quarter=min(action_date_year_quarter)),
                              by=c('contract_award_unique_key',
                                 'recipient_duns',
                                 'product_or_service_code')]

project_quarter=merge(project_quarter,
                      num_proj_same_task_df,
                      by.x=c('start_quarter',
                             'recipient_duns',
                             'product_or_service_code'),
                      by.y=c('action_date_year_quarter',
                             'recipient_duns',
                             'product_or_service_code'),
                      all.x=T)

# Task inexperienced if
project_quarter[,task_inexperienced_i:=ifelse(num_projs_same_task_past_three_qtrs==0,1,0)]
project_quarter[,new_entrant_i:=ifelse(num_projs_past_three_qtrs==0,1,0)]

# Proportion of projects on which contractor has past experience
project_quarter[,prop_exp:=ifelse(num_projs_past_three_qtrs>0,
                                 num_projs_same_task_past_three_qtrs/num_projs_past_three_qtrs,
                                       0)]

project_entrant=project_quarter[,c('contract_award_unique_key',
                                   'task_inexperienced_i',
                                   'new_entrant_i',
                                   'num_projs_same_task_past_three_qtrs',
                                   'num_projs_past_three_qtrs',
                                   'prop_exp')]

reg_df=merge(reg_df,
                    project_entrant,
                    by='contract_award_unique_key',
                    all.x = T)
```

```{r define_inexp, include=FALSE}
reg_df[,inexp:=1-prop_exp]
```

```{r clean_sample, include=FALSE}
reg_df=reg_df[contract_award_unique_key%in%reg_df_working$contract_award_unique_key]
```

# Effect on bids

```{r competition_delays_subsample, echo=FALSE, results='asis'}
reg_df=reg_df[order(contract_award_unique_key,action_date_year_quarter)]
reg_df_first_reported=unique(reg_df,
                             by='contract_award_unique_key')
 
reg_df_first_reported=subset(reg_df_first_reported,
                             initial_start_date>as.Date('2009-12-31') &
                               initial_start_date<as.Date('2012-03-31') &
                              competitively_awarded_i==1)
```

```{r experience_bids, echo=FALSE, results='asis'}
#  BIDS  ------------------------------------
all_bids=feols(wins_number_of_offers_received~treat_i+
                                  treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=subset(reg_df_first_reported,#&
                                     # number_of_offers_received>1 &
                                     # number_of_offers_received<32
                                     ))

inexp_bids=feols(wins_number_of_offers_received~treat_i+
                                  treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=subset(reg_df_first_reported,
                                      task_inexperienced_i==1#&
                                     # number_of_offers_received>1 &
                                     # number_of_offers_received<32
                                     ))

exp_bids=feols(wins_number_of_offers_received~treat_i+
                                  treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=subset(reg_df_first_reported,
                                      task_inexperienced_i==0 #&
                                     # number_of_offers_received>1 &
                                     # number_of_offers_received<32
                                     )) 
                          # remove outliers -- these are 0.1 and 0.99 quantile

#  DURATION  ------------------------------------

all_duration=feols(winsorized_initial_duration_in_days_i~treat_i+
                                  treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=reg_df_first_reported)

exp_duration=feols(winsorized_initial_duration_in_days_i~treat_i+
                                  treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=reg_df_first_reported[task_inexperienced_i==0])

inexp_duration=feols(winsorized_initial_duration_in_days_i~treat_i+
                                  treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=reg_df_first_reported[task_inexperienced_i==1])


#  BUDGET  ------------------------------------

all_budget=feols(I(winsorized_initial_budget_i/1000)~treat_i+
                                 treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=reg_df_first_reported)

exp_budget=feols(I(winsorized_initial_budget_i/1000)~treat_i+
                                 treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=reg_df_first_reported[task_inexperienced_i==0])

inexp_budget=feols(I(winsorized_initial_budget_i/1000)~treat_i+
                                 treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=reg_df_first_reported[task_inexperienced_i==1])

experienced=list(exp_bids,exp_duration,exp_budget)
inexperienced=list(inexp_bids,inexp_duration,inexp_budget)
all_projects=list(all_bids,all_duration,all_budget)
```

```{r entrant_bids, echo=FALSE, results='asis'}
#  BIDS ------------------------------------
new_entrant_bids=feols(wins_number_of_offers_received~treat_i+
                                  treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=subset(reg_df_first_reported,
                                      new_entrant_i==1#&
                                     # number_of_offers_received>1 &
                                     # number_of_offers_received<32
                                     ))

old_entrant_bids=feols(wins_number_of_offers_received~treat_i+
                                  treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=subset(reg_df_first_reported,
                                      new_entrant_i==0#&
                                     # number_of_offers_received>1 &
                                     # number_of_offers_received<32
                                     )) 
                          # remove outliers -- these are 0.1 and 0.99 quantile

#  DURATION  ------------------------------------

old_entrant_duration=feols(winsorized_initial_duration_in_days_i~treat_i+
                                  treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=reg_df_first_reported[new_entrant_i==0])

new_entrant_duration=feols(winsorized_initial_duration_in_days_i~treat_i+
                                  treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=reg_df_first_reported[new_entrant_i==1])

#  BUDGET  ------------------------------------

old_entrant_budget=feols(I(winsorized_initial_budget_i/1000)~treat_i+
                                 treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=reg_df_first_reported[new_entrant_i==0])

new_entrant_budget=feols(I(winsorized_initial_budget_i/1000)~treat_i+
                                 treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
                          cluster=~contract_award_unique_key,
                          data=reg_df_first_reported[new_entrant_i==1])

old_entrants=list(old_entrant_bids,old_entrant_duration,old_entrant_budget)
new_entrants=list(new_entrant_bids,new_entrant_duration,new_entrant_budget)
```

# Effect on Delays

```{r clean_sample_ii, eval=FALSE}
# reg_df=reg_df[contract_award_unique_key%in%reg_df_working$contract_award_unique_key]
```

## Old vs New Entrant

```{r new_entrant_bid_delays, include=FALSE}
m1=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)+
                            post_t,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,new_entrant_i==1&
                                        competitively_awarded_i==1))

m2=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,new_entrant_i==1&
                                        competitively_awarded_i==1))

m3=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,new_entrant_i==1&
                                        competitively_awarded_i==1))

m4=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            naics_code+
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,new_entrant_i==1&
                                        competitively_awarded_i==1))

new_entrant_delays=list(m1,m2,m3,m4)
```

```{r old_entrant_bid_delays, include=FALSE}
m1=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)+
                            post_t,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,new_entrant_i==0&
                                        competitively_awarded_i==1))

m2=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,new_entrant_i==0&
                                        competitively_awarded_i==1))

m3=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,new_entrant_i==0&
                                        competitively_awarded_i==1))

m4=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            naics_code+
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,new_entrant_i==0&
                                        competitively_awarded_i==1))

old_entrant_delays=list(m1,m2,m3,m4)
```

# Experienced vs Inexperienced

```{r inexperienced_bid_delays, include=FALSE}
m1=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)+
                            post_t,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,task_inexperienced_i==1&
                                        competitively_awarded_i==1))

m2=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,task_inexperienced_i==1&
                                        competitively_awarded_i==1))

m3=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,task_inexperienced_i==1&
                                        competitively_awarded_i==1))

m4=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            naics_code+
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,task_inexperienced_i==1&
                                        competitively_awarded_i==1))

task_inexperienced_delays=list(m1,m2,m3,m4)
```

```{r experienced_bid_delays, include=FALSE}
m1=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)+
                            post_t,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,task_inexperienced_i==0&
                                        competitively_awarded_i==1))

m2=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,task_inexperienced_i==0&
                                        competitively_awarded_i==1))

m3=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,task_inexperienced_i==0&
                                        competitively_awarded_i==1))

m4=feols(wins_percentage_delay~treat_i+
                                  project_signed_after_quickpay+
                                  treat_i:post_t+
                                  treat_i:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            naics_code+
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df,task_inexperienced_i==0&
                                        competitively_awarded_i==1))

task_experienced_delays=list(m1,m2,m3,m4)
```

# Output

```{r set_dict,include=FALSE}
setFixest_dict(c("project_signed_after_quickpay"="$SA_i$",
                 "contract_award_unique_key"="Project ID",
                 "product_or_service_code"="Task",
                 "treat_i"="$Treat_i$",
                 "I(winsorized_initial_budget_i/1000)"="Initial budget (000s)",
                 "winsorized_initial_duration_in_days_i"="Initial duration",
                 "wins_number_of_offers_received"="Number of offers",
                 "quarter_when_project_signed"="Time",
                 "wins_percentage_delay"="Percentage delay rate",
                 "treat_i"="Treat",
                 "post_t"="Post",
                 "project_signed_after_quickpay"="SA$_i$",
                 "inexp"="Level of inexperience",
                 "log(wins_project_quarter_stage)"="Ln(Stage)",
                 "new_entrant_i"="New Entrant",
                 "task_inexperienced_i"="Inexperienced contractor",
                 "action_date_year_quarter"="Time",
                 "naics_code"="Industry"))

```

```{r experience_bids_output, results='asis'}
etable(experienced,
       inexperienced,
       tex=T,
       headers=list("^:_:"=list("Experienced"=length(experienced),
                                    "Inexperienced"=length(inexperienced))),
       digits = 'r2',
       digits.stats = 'r2',
       style.tex = style.tex(model.format = "I",
                             depvar.title = "",
                             model.title = "",
                             yesNo=c("Yes","No"),
                             fixef.title = "\\midrule",
                             stats.title = "\\midrule",
                             var.title = "\\midrule",
                             line.top = "simple",
                             line.bottom = "simple",
                             fixef.suffix = " FE"),
       fontsize = 'footnotesize'
       )

etable(task_experienced_delays,
        task_inexperienced_delays,
        headers=list(":_:"=list("Experienced contractors"=4,
                    "Inxperienced contractors"=4)),
       tex=T,
       style.tex = style.tex(model.format = "I",
                             depvar.title = "",
                             model.title = "",
                             yesNo=c("Yes","No"),
                             fixef.title = "\\midrule",
                             stats.title = "\\midrule",
                             var.title = "\\midrule",
                             line.top = "simple",
                             line.bottom = "simple",
                             fixef.suffix = " FE"),
       digits='r3',
       digits.stats = 'r2',
       fontsize = "small")
```

```{r new_entrant_delays_output, echo=FALSE,results='asis'}
etable(old_entrants,
       new_entrants,
       tex=T,
       headers=list("^:_:"=list("Old entrants"=length(experienced),
                                    "New entrants"=length(inexperienced))),
       digits = 'r2',
       digits.stats = 'r2',
       style.tex = style.tex(model.format = "I",
                             depvar.title = "",
                             model.title = "",
                             yesNo=c("Yes","No"),
                             fixef.title = "\\midrule",
                             stats.title = "\\midrule",
                             var.title = "\\midrule",
                             line.top = "simple",
                             line.bottom = "simple",
                             fixef.suffix = " FE"),
       fontsize = 'footnotesize'
       )

etable(old_entrant_delays,
       new_entrant_delays,
        headers=list(":_:"=list("Old entrants"=4,
                    "New entrants"=4)),
       tex=T,
       style.tex = style.tex(model.format = "I",
                             depvar.title = "",
                             model.title = "",
                             yesNo=c("Yes","No"),
                             fixef.title = "\\midrule",
                             stats.title = "\\midrule",
                             var.title = "\\midrule",
                             line.top = "simple",
                             line.bottom = "simple",
                             fixef.suffix = " FE"),
       digits='r3',
       digits.stats = 'r2',
       fontsize = "small")
```