---
title: "Contractor Experience"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_tex: true
    number_sections: true
header-includes:
 \usepackage{booktabs}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = FALSE)
options(xtable.comment = FALSE)
```

```{r packages,warning=FALSE,message=FALSE,include=FALSE}
library(data.table)
library(dplyr)
library(fixest)
library(ggplot2)
library(DescTools) 
library(xtable)
library(car) # for deltaMethod
```

```{r read_data,include=FALSE}
input_path='~/Dropbox/data_quickpay/qp_replication/input/'
reg_df=fread(paste0(input_path,
               'quickpay_delays.csv'))

reg_df=reg_df[!(initial_start_date>as.Date('2011-04-27') 
                              & post_t==0)]

reg_df=reg_df[!is.na(recipient_duns)]
```

```{r competition_delays_subsample, echo=FALSE, results='asis'}
reg_df[,project_signed_after_quickpay:=case_when(initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter>=as.Date('2011-04-27')~1,
                                                 initial_start_date<as.Date('2011-04-27') ~ 0,
                                                 initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter<as.Date('2011-04-27')~NaN)]
```

```{r define_var, include=FALSE}

# Number of projects held by a contractor in a given quarter
num_proj_per_contractor_df=reg_df[,
                .(num_projects=
                    n_distinct(contract_award_unique_key)),
              by=c('recipient_duns',
                   'action_date_year_quarter')]

# Number of projects of a given task type held by a contractor in a given quarter
num_proj_same_task_df=reg_df[,
                .(num_projects_same_task=
                    n_distinct(contract_award_unique_key)),
              by=c('recipient_duns',
                   'product_or_service_code',
                   'action_date_year_quarter')]

num_proj_same_task_df=num_proj_same_task_df[order(recipient_duns,
                                                   product_or_service_code,
                                                   action_date_year_quarter)]

num_proj_per_contractor_df=num_proj_per_contractor_df[order(recipient_duns,
                                                            action_date_year_quarter)]
```

```{r get_lags, include=FALSE}

# LAG OF 1 ------------------------------

# If same contractor last quarter + same task last quarter, take lag value. Else take zero.
# Zero can indicate:
# 1. Same contractor last quarter + different task last quarter, OR
# 2. Different contractor last quarter i.e., contractor is new entrant
num_proj_same_task_df[,num_projects_same_task_lag_1:=ifelse(recipient_duns==
                                                                 lag(recipient_duns)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code),
                                                            lag(num_projects_same_task),
                                                            0)]

num_proj_per_contractor_df[,num_projects_lag_1:=ifelse(recipient_duns==lag(recipient_duns),
                                                            lag(num_projects),
                                                            0)]

# LAG OF 2 ------------------------------

# If same contractor second-to-last quarter + same task second-to-last quarter, take lag-2 value. Else take zero.
# Zero can indicate:
# 1. Same contractor second-to-last quarter + different task second-to-last quarter, OR
# 2. Different contractor second-to-last quarter i.e., contractor is new entrant
num_proj_same_task_df[,num_projects_same_task_lag_2:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,2)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code,2),
                                                            lag(num_projects_same_task,2),
                                                            0)]

num_proj_per_contractor_df[,num_projects_lag_2:=ifelse(recipient_duns==lag(recipient_duns,2),
                                                            lag(num_projects,2),
                                                            0)]


# LAG OF 3  ------------------------------

num_proj_same_task_df[,num_projects_same_task_lag_3:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,3)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code,3),
                                                            lag(num_projects_same_task,3),
                                                            0)]


num_proj_per_contractor_df[,num_projects_lag_3:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,3),
                                                            lag(num_projects,3),
                                                            0)]


# ADD IT UP  ------------------------------

num_proj_same_task_df[,num_projs_same_task_past_three_qtrs:=num_projects_same_task_lag_2+
                                                          num_projects_same_task_lag_1+
                                                          num_projects_same_task_lag_3]


num_proj_per_contractor_df[,num_projs_past_three_qtrs:=num_projects_lag_1+
                                                  num_projects_lag_2+
                                                  num_projects_lag_3]

```

```{r merge, include=FALSE}
# Merge the two datasets
num_proj_same_task_df=merge(num_proj_same_task_df,
                            num_proj_per_contractor_df,
                            by=c('recipient_duns',
                                 'action_date_year_quarter'),
                            all.x=T)
```

* Let $n^{task}_{i}=$ Number of projects of the same task held by the contractor in the three quarters before starting project $i$
* Let $n_{i}=$ Number of projects held by the contractor in the three quarters before starting project $i$

* Define:
  * Inexperienced contractor$_i$ = 1 if $n^{task}_{i}=0$ 
  * New entrant$_i$ = 1 if $n_{i}=0$
  * Level of inexperience$_{i}= 1 - \frac{n^{task}_{i}}{n_{i}}$ if $n_{i}>0$
  * Level of inexperience$_{i}= 1$ if $n_{i,k,t}=0$.
    

```{r project_quarter, include=FALSE}
# Get first quarter for every project
project_quarter=reg_df[,.(start_quarter=min(action_date_year_quarter)),
                              by=c('contract_award_unique_key',
                                 'recipient_duns',
                                 'product_or_service_code')]

project_quarter=merge(project_quarter,
                      num_proj_same_task_df,
                      by.x=c('start_quarter',
                             'recipient_duns',
                             'product_or_service_code'),
                      by.y=c('action_date_year_quarter',
                             'recipient_duns',
                             'product_or_service_code'),
                      all.x=T)

# Task inexperienced if
project_quarter[,task_inexperienced_i:=ifelse(num_projs_same_task_past_three_qtrs==0,1,0)]
project_quarter[,new_entrant_i:=ifelse(num_projs_past_three_qtrs==0,1,0)]

# Proportion of projects on which contractor has past experience
project_quarter[,prop_exp:=ifelse(num_projs_past_three_qtrs>0,
                                 num_projs_same_task_past_three_qtrs/num_projs_past_three_qtrs,
                                       0)]

project_entrant=project_quarter[,c('contract_award_unique_key',
                                   'task_inexperienced_i',
                                   'new_entrant_i',
                                   'num_projs_same_task_past_three_qtrs',
                                   'num_projs_past_three_qtrs',
                                   'prop_exp')]

reg_df=merge(reg_df,
                    project_entrant,
                    by='contract_award_unique_key',
                    all.x = T)
```

```{r clean_sample, include=FALSE}
working_path='~/Dropbox/data_quickpay/qp_replication/working/'
reg_df_working=fread(paste0(working_path,
                 'w_clean_control.csv'))

reg_df_sub=reg_df[,c('contract_award_unique_key',
                     'action_date_year_quarter',
                     'new_entrant_i',
                     'task_inexperienced_i')]

reg_df_working=merge(reg_df_sub,
                     reg_df_working,
                     by=c('contract_award_unique_key',
                     'action_date_year_quarter'),
                     all.y=T)
```

# Task Inexperience Bootstrap

```{r task_inexp_bs, include=FALSE}
df=subset(reg_df_working,competitively_awarded_i==1)
n = nrow(df)
nrep=100
# Create a "nrep" dimension vector of lists
delta.alpha.coefs = vector("list", nrep)
multiplier.coefs=vector("list",nrep)

# Do this nrep times
for(i in 1:nrep){
  print(i)
  set.seed(100+i)
  df_sub=df[sample(n, n/2, replace=T), ]
  m1=feglm(task_inexperienced_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=df_sub)
  delta.alpha.coefs[[i]]=coef(m1,'treat_i:post_t')

  m2=feols(wins_percentage_delay~treat_i+
                                  task_inexperienced_i+
                                  treat_i:task_inexperienced_i+
                                  post_t:task_inexperienced_i+
                                  treat_i:post_t+
                                  treat_i:post_t:task_inexperienced_i+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=df_sub)

  d2=deltaMethod(m2,
            "task_inexperienced_i+
            `treat_i:task_inexperienced_i`+
            `task_inexperienced_i:post_t`+
            `treat_i:task_inexperienced_i:post_t`",
            rhs=0)

  multiplier.coefs[[i]]=d2$Estimate
}
# Save all coefficients as a matrix
all_coef_multiplier = do.call("rbind", multiplier.coefs)
all_coef_delta_alpha_logit = do.call("rbind", delta.alpha.coefs)

coef_mat=cbind(all_coef_multiplier,
               all_coef_delta_alpha_logit)

coef_mat_task=as.data.frame(coef_mat)
setDT(coef_mat_task)
setnames(coef_mat_task,
         c("V1","treat_i:post_t"),
         c("multiplier","delta_alpha_logit"))
coef_mat_task[,product:=multiplier*delta_alpha_logit]
```

```{r export_csv, include=FALSE}
write.csv(coef_mat_task,
          '~/Desktop/coef_mat_task.csv')
```

# New Entrant Bootstrap

```{r new_entrant_bs, include=FALSE}
n = nrow(df)
nrep=100
# Create a "nrep" dimension vector of lists
delta.alpha.coefs = vector("list", nrep)
multiplier.coefs=vector("list",nrep)

# Do this nrep times
for(i in 1:nrep){
  print(i)
  set.seed(100+i)
  df_sub=df[sample(n, n/2, replace=T), ]
  m1_entrant=feglm(new_entrant_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=df_sub)
  delta.alpha.coefs[[i]]=coef(m1_entrant,'treat_i:post_t')

  m2_entrant=feols(wins_percentage_delay~treat_i+
                                  new_entrant_i+
                                  treat_i:new_entrant_i+
                                  post_t:new_entrant_i+
                                  treat_i:post_t+
                                  treat_i:post_t:new_entrant_i+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=df_sub)

  d2_entrant=deltaMethod(m2_entrant,
            "new_entrant_i+
            `treat_i:new_entrant_i`+
            `new_entrant_i:post_t`+
            `treat_i:new_entrant_i:post_t`",
            rhs=0)

  multiplier.coefs[[i]]=d2_entrant$Estimate
}
# Save all coefficients as a matrix
all_coef_multiplier = do.call("rbind", multiplier.coefs)
all_coef_delta_alpha_logit = do.call("rbind", delta.alpha.coefs)

coef_mat=cbind(all_coef_multiplier,
               all_coef_delta_alpha_logit)

coef_mat_entrant=as.data.frame(coef_mat)
setDT(coef_mat_entrant)
setnames(coef_mat_entrant,
         c("V1","treat_i:post_t"),
         c("multiplier","delta_alpha_logit"))
coef_mat_entrant[,product:=multiplier*delta_alpha_logit]
```

```{r export_csv_entrant, include=FALSE}
write.csv(coef_mat_entrant,
          '~/Desktop/coef_mat_entrant.csv')
```

```{r make_hist,include=FALSE}
entrant_plot=ggplot(coef_mat_entrant, aes(x = product)) + 
  geom_histogram(color = "black",
                 fill = "gray", 
                 bins = 20, 
                 alpha = 0.7) +  
  theme_minimal(base_size = 14) +  
  xlab("Estimate") +
  ylab("Frequency") +
  ggtitle("New Entrant") +  
  geom_vline(xintercept = 0, 
             linetype = "solid", 
             color = "darkred", 
             size = 0.8) +
  theme(panel.grid = element_blank(),  
        panel.border = element_rect(color = "black", fill = NA),  
        plot.title = element_text(hjust = 0.5, size = 20),  
        axis.title.x = element_text(size = 20),  
        axis.title.y = element_text(size = 20),  
        axis.text = element_text(size = 10),  
        axis.ticks = element_line(color = "gray"),  
        plot.background = element_rect(fill = "white", color = NA)) +  
  scale_x_continuous(limits = c(-max(abs(coef_mat_entrant$product)), 
                                max(abs(coef_mat_entrant$product))))  

task_plot=ggplot(coef_mat_task, aes(x = product)) + 
  geom_histogram(color = "black",
                 fill = "gray", 
                 bins = 20, 
                 alpha = 0.7) +  
  theme_minimal(base_size = 14) +  
  xlab("Estimate") +
  ylab("Frequency") +
  ggtitle("Task inexperienced") +  
  geom_vline(xintercept = 0, 
             linetype = "solid", 
             color = "darkred", 
             size = 0.8) +
  theme(panel.grid = element_blank(),  
        panel.border = element_rect(color = "black", fill = NA),  
        plot.title = element_text(hjust = 0.5, size = 20),  
        axis.title.x = element_text(size = 20),  
        axis.title.y = element_text(size = 20),  
        axis.text = element_text(size = 10),  
        axis.ticks = element_line(color = "gray"),  
        plot.background = element_rect(fill = "white", color = NA)) +  
  scale_x_continuous(limits = c(-max(abs(coef_mat_task$product)), 
                                max(abs(coef_mat_task$product)))) 

```

```{r save_plots, include=FALSE}
ggsave('~/Desktop/entrant_hist.png',
       entrant_plot,
        width=10,
       dpi=300)

ggsave('~/Desktop/task_hist.png',
       task_plot,
        width=10,
       dpi=300)
```
