---
title: "Full Sample -- Contractor Experience"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_tex: true
    number_sections: true
header-includes:
 \usepackage{booktabs,longtable,dcolumn}
 \usepackage{multirow,array,makecell}
 \usepackage{wrapfig,float}
 \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = FALSE)
options(xtable.comment = FALSE)
```

```{r packages,warning=FALSE,message=FALSE,include=FALSE}
library(data.table)
library(dplyr)
library(fixest)
#library(tidyverse)
library(DescTools) 
library(xtable)
library(car) # for deltaMethod
```

```{r read_data,include=FALSE}
input_path='~/Dropbox/data_quickpay/qp_replication/input/'
reg_df=fread(paste0(input_path,
               'quickpay_delays.csv'))

reg_df=reg_df[!(initial_start_date>as.Date('2011-04-27') 
                              & post_t==0)]

reg_df=reg_df[!is.na(recipient_duns)]
```

```{r competition_delays_subsample, echo=FALSE, results='asis'}
reg_df[,project_signed_after_quickpay:=case_when(initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter>=as.Date('2011-04-27')~1,
                                                 initial_start_date<as.Date('2011-04-27') ~ 0,
                                                 initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter<as.Date('2011-04-27')~NaN)]
```

```{r define_var, include=FALSE}

# Number of projects held by a contractor in a given quarter
num_proj_per_contractor_df=reg_df[,
                .(num_projects=
                    n_distinct(contract_award_unique_key)),
              by=c('recipient_duns',
                   'action_date_year_quarter')]

# Number of projects of a given task type held by a contractor in a given quarter
num_proj_same_task_df=reg_df[,
                .(num_projects_same_task=
                    n_distinct(contract_award_unique_key)),
              by=c('recipient_duns',
                   'product_or_service_code',
                   'action_date_year_quarter')]

# Merge the two datasets
num_proj_same_task_df=merge(num_proj_same_task_df,
                            num_proj_per_contractor_df,
                            by=c('recipient_duns',
                                 'action_date_year_quarter'),
                            all.x=T)

# Proportion of projects of same task type held by a contractor in a given quarter
#num_proj_same_task_df[,prop_projects_same_task:=num_projects_same_task/num_projects]

num_proj_same_task_df=num_proj_same_task_df[order(recipient_duns,
                                                   product_or_service_code,
                                                   action_date_year_quarter)]
```

```{r get_lags, include=FALSE}

# LAG OF 1 ------------------------------

# If same contractor last quarter + same task last quarter, take lag value. Else take zero.
# Zero can indicate:
# 1. Same contractor last quarter + different task last quarter, OR
# 2. Different contractor last quarter i.e., contractor is new entrant
num_proj_same_task_df[,num_projects_same_task_lag_1:=ifelse(recipient_duns==
                                                                 lag(recipient_duns)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code),
                                                            lag(num_projects_same_task),
                                                            0)]

num_proj_same_task_df[,num_projects_lag_1:=ifelse(recipient_duns==lag(recipient_duns),
                                                            lag(num_projects),
                                                            0)]

# LAG OF 2 ------------------------------

# If same contractor second-to-last quarter + same task second-to-last quarter, take lag-2 value. Else take zero.
# Zero can indicate:
# 1. Same contractor second-to-last quarter + different task second-to-last quarter, OR
# 2. Different contractor second-to-last quarter i.e., contractor is new entrant
num_proj_same_task_df[,num_projects_same_task_lag_2:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,2)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code,2),
                                                            lag(num_projects_same_task,2),
                                                            0)]

num_proj_same_task_df[,num_projects_lag_2:=ifelse(recipient_duns==lag(recipient_duns,2),
                                                            lag(num_projects,2),
                                                            0)]


# LAG OF 3  ------------------------------

num_proj_same_task_df[,num_projects_same_task_lag_3:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,3)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code,3),
                                                            lag(num_projects_same_task,3),
                                                            0)]


num_proj_same_task_df[,num_projects_lag_3:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,3),
                                                            lag(num_projects,3),
                                                            0)]


# ADD IT UP  ------------------------------

num_proj_same_task_df[,num_projs_same_task_past_three_qtrs:=num_projects_same_task_lag_2+
                                                          num_projects_same_task_lag_1+
                                                          num_projects_same_task_lag_3]


num_proj_same_task_df[,num_projs_past_three_qtrs:=num_projects_lag_1+
                                                  num_projects_lag_2+
                                                  num_projects_lag_3]

```

* Let $n^{task}_{i}=$ Number of projects of the same task held by the contractor in the three quarters before starting project $i$
* Let $n_{i}=$ Number of projects held by the contractor in the three quarters before starting project $i$

* Define:
  * Inexperienced contractor$_i$ = 1 if $n^{task}_{i}=0$ 
  * New entrant$_i$ = 1 if $n_{i}=0$
  * Level of inexperience$_{i}= 1 - \frac{n^{task}_{i}}{n_{i}}$ if $n_{i}>0$
  * Level of inexperience$_{i}= 1$ if $n_{i,k,t}=0$.
    

```{r project_quarter, include=FALSE}
# Get first quarter for every project
project_quarter=reg_df[,.(start_quarter=min(action_date_year_quarter)),
                              by=c('contract_award_unique_key',
                                 'recipient_duns',
                                 'product_or_service_code')]

project_quarter=merge(project_quarter,
                      num_proj_same_task_df,
                      by.x=c('start_quarter',
                             'recipient_duns',
                             'product_or_service_code'),
                      by.y=c('action_date_year_quarter',
                             'recipient_duns',
                             'product_or_service_code'),
                      all.x=T)

# Task inexperienced if
project_quarter[,task_inexperienced_i:=ifelse(num_projs_same_task_past_three_qtrs==0,1,0)]
project_quarter[,new_entrant_i:=ifelse(num_projs_past_three_qtrs==0,1,0)]

# Proportion of projects on which contractor has past experience
project_quarter[,prop_exp:=ifelse(num_projs_past_three_qtrs>0,
                                 num_projs_same_task_past_three_qtrs/num_projs_past_three_qtrs,
                                       0)]

project_entrant=project_quarter[,c('contract_award_unique_key',
                                   'task_inexperienced_i',
                                   'new_entrant_i',
                                   'num_projs_same_task_past_three_qtrs',
                                   'num_projs_past_three_qtrs',
                                   'prop_exp')]

reg_df=merge(reg_df,
                    project_entrant,
                    by='contract_award_unique_key',
                    all.x = T)
```

```{r define_inexp, include=FALSE}
reg_df[,inexp:=1-prop_exp]
```

```{r clean_sample, include=FALSE}
working_path='~/Dropbox/data_quickpay/qp_replication/working/'
reg_df_clean=fread(paste0(working_path,
                 'w_clean_control.csv'))

reg_df=reg_df[contract_award_unique_key%in%reg_df_clean$contract_award_unique_key]
```

# Parallel trends test

```{r define_qt, include=FALSE}
df_qn<-unique(reg_df,by='action_date_year_quarter')[,"action_date_year_quarter"]
df_qn=df_qn[order(action_date_year_quarter)][,quarter_number:=seq.int(nrow(df_qn))]
reg_df=merge(reg_df,df_qn,by='action_date_year_quarter')
```

```{r pt_new_entrant, include=FALSE}
m1=feglm(new_entrant_i~treat_i+
                             quarter_number:treat_i+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            wins_number_of_offers_received+
                          quarter_number:log(1+winsorized_initial_duration_in_days_i)+
                            quarter_number:log(1+winsorized_initial_budget_i)+
                            quarter_number:wins_number_of_offers_received|
                            action_date_year_quarter,
         cluster=~contract_award_unique_key,
         family='binomial',
                          data=subset(reg_df, competitively_awarded_i==1 &
                                              post_t==0))

m2=feglm(new_entrant_i~treat_i+
                              quarter_number:treat_i+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            wins_number_of_offers_received+
                            quarter_number:log(1+winsorized_initial_duration_in_days_i)+
                            quarter_number:log(1+winsorized_initial_budget_i)+
                            quarter_number:wins_number_of_offers_received|
                            product_or_service_code+action_date_year_quarter,
         cluster=~contract_award_unique_key,
         family='binomial',
                          data=subset(reg_df, competitively_awarded_i==1 &
                                              post_t==0))

m3=feglm(new_entrant_i~treat_i+
                            quarter_number:treat_i+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            wins_number_of_offers_received+
                            quarter_number:log(1+winsorized_initial_duration_in_days_i)+
                            quarter_number:log(1+winsorized_initial_budget_i)+
                            quarter_number:wins_number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter,
         cluster=~contract_award_unique_key,
         family='binomial',
                          data=subset(reg_df, competitively_awarded_i==1 &
                                              post_t==0))

pt_new_entrant=list(m1,m2,m3)
```

```{r pt_task_inexperienced, include=FALSE}
m1=feglm(task_inexperienced_i~treat_i+
                             quarter_number:treat_i+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            wins_number_of_offers_received+
                          quarter_number:log(1+winsorized_initial_duration_in_days_i)+
                            quarter_number:log(1+winsorized_initial_budget_i)+
                            quarter_number:wins_number_of_offers_received|
                            action_date_year_quarter,
         cluster=~contract_award_unique_key,
         family='binomial',
                          data=subset(reg_df, competitively_awarded_i==1 &
                                              post_t==0))

m2=feglm(task_inexperienced_i~treat_i+
                              quarter_number:treat_i+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            wins_number_of_offers_received+
                            quarter_number:log(1+winsorized_initial_duration_in_days_i)+
                            quarter_number:log(1+winsorized_initial_budget_i)+
                            quarter_number:wins_number_of_offers_received|
                            product_or_service_code+action_date_year_quarter,
         cluster=~contract_award_unique_key,
         family='binomial',
                          data=subset(reg_df, competitively_awarded_i==1 &
                                              post_t==0))

m3=feglm(task_inexperienced_i~treat_i+
                            quarter_number:treat_i+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            wins_number_of_offers_received+
                            quarter_number:log(1+winsorized_initial_duration_in_days_i)+
                            quarter_number:log(1+winsorized_initial_budget_i)+
                            quarter_number:wins_number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter,
         cluster=~contract_award_unique_key,
         family='binomial',
                          data=subset(reg_df, competitively_awarded_i==1 &
                                              post_t==0))

pt_task_inexperienced=list(m1,m2,m3)
```

# Regression results

```{r inexp_logit, include=FALSE}
m1=feglm(task_inexperienced_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m2=feglm(new_entrant_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m3=feols(inexp~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

contractor_pool_entry=list(m1,m2)
```

```{r inexp_ols, include=FALSE}
m1=feols(wins_percentage_delay~treat_i+
                                  task_inexperienced_i+
                                  treat_i:task_inexperienced_i+
                                  post_t:task_inexperienced_i+
                                  treat_i:post_t+
                                  treat_i:post_t:task_inexperienced_i+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m2=feols(wins_percentage_delay~treat_i+
                                  new_entrant_i+
                                  treat_i:new_entrant_i+
                                  post_t:new_entrant_i+
                                  treat_i:post_t+
                                  treat_i:post_t:new_entrant_i+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m3=feols(wins_percentage_delay~treat_i+
                                  inexp+
                                  treat_i:inexp+
                                  post_t:inexp+
                                  treat_i:post_t+
                                  treat_i:post_t:inexp+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

contractor_pool_delays=list(m1,m2)
```

```{r output, echo=FALSE, results='asis'}
setFixest_dict(c("wins_percentage_delay"="Percentage delay rate",
                 "treat_i"="$Treat_i$",
                 "post_t"="$Post_t$",
                 "project_signed_after_quickpay"="$SA_i$",
                 "inexp"="IE",
                 "log(wins_project_quarter_stage)"="Ln(Stage)",
                 "new_entrant_i"="IE",
                 "task_inexperienced_i"="IE",
                 "action_date_year_quarter"="Time",
                      "quarter_number"="$QtrNum$",
                 "product_or_service_code"="Task",
                 "naics_code"="Industry",
                 "contract_award_unique_key"="Project ID",
                 "wins_number_of_offers_received"="Num offers",
                 "log(winsorized_initial_budget_i)"="Ln(Initial Budget)",
                  "log(winsorized_initial_duration_in_days_i)"="Ln(Initial Duration)"))

etable(pt_task_inexperienced,
       pt_new_entrant,
       tex=T,
       drop=c('%wins_project_quarter_stage',
              '%wins_number_of_offers_received',
              '%winsorized_initial_budget_i',
              '%winsorized_initial_duration_in_days_i',
              '%post_t:wins_number_of_offers_received',
              '%post_t:winsorized_initial_budget_i',
              '%post_t:winsorized_initial_duration_in_days_i'),
       style.tex = style.tex(depvar.title = "",
                             model.title = "\\midrule",
                             model.format = "I",
                             var.title = "\\midrule",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "\\midrule",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       headers=list("Task inexperienced"=length(pt_task_inexperienced),
                    "New entrant"=length(pt_new_entrant)),
       digits='r3',
       digits.stats = 'r2',
       fitstat = c('r2','pr2','n'),
       title="Parallel trends test",
       fontsize = "small")

etable(contractor_pool_entry,
       tex=T,
       drop=c('%wins_project_quarter_stage',
              '%wins_number_of_offers_received',
              '%winsorized_initial_budget_i',
              '%winsorized_initial_duration_in_days_i',
              '%post_t:wins_number_of_offers_received',
              '%post_t:winsorized_initial_budget_i',
              '%post_t:winsorized_initial_duration_in_days_i'),
       style.tex = style.tex(depvar.title = "",
                             model.title = "\\midrule",
                             model.format = "I",
                             var.title = "\\midrule",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "\\midrule",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       headers=list("Task inexperienced"=1,
                    "New entrant"=1),
       digits='r3',
       digits.stats = 'r2',
       fitstat = c('r2','pr2','n'),
       title="Logit model",
       fontsize = "small")

etable(contractor_pool_delays,
       tex=T,
       drop=c('%wins_project_quarter_stage',
              '%wins_number_of_offers_received',
              '%winsorized_initial_budget_i',
              '%winsorized_initial_duration_in_days_i',
              '%post_t:wins_number_of_offers_received',
              '%post_t:winsorized_initial_budget_i',
              '%post_t:winsorized_initial_duration_in_days_i'),
       style.tex = style.tex(depvar.title = "",
                             model.title = "\\midrule",
                             model.format = "I",
                             var.title = "\\midrule",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "\\midrule",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       headers=list("Task inexperienced"=1,
                    "New entrant"=1),
       digits='r3',
       digits.stats = 'r2',
       fitstat = c('r2','pr2','n'),
       fontsize = "small")
```

* For $IE + Treat \times IE + IE \times Post + Treat \times IE \times Post$ using the two discrete metrics, we get:

```{r task_inexp_sum, echo=FALSE, results='asis'}
# using first principles
# relevant regressors have indices 2, 7, and 8
# cov_matrix=vcov(m1) # this is already clustered
# v=c(0,1,0,0,0,0,1,1,0,0,0,0,0)
# sqrt(t(v)%*%cov_matrix%*%v)
# coef_m1[2]+coef_m1[7]+coef_m1[8]

# vcov(m1) is same as vcov_cluster(m1,cluster='contract_award_unique_key')
# this is because cluster variable was specified in m1
# But vcov(m1)!=vcov_cluster(m1) because then a different clustering variable is picked by default

# using delta method from library car
d1=deltaMethod(m1,
            "task_inexperienced_i+
            `treat_i:task_inexperienced_i`+
            `task_inexperienced_i:post_t`+
            `treat_i:task_inexperienced_i:post_t`",
            rhs=0)
d1_df <- as.data.frame(d1)
rownames(d1_df) <- c("Task inexperienced")
print(xtable(d1_df,type='latex'))

d2=deltaMethod(m2,
            "new_entrant_i+
            `treat_i:new_entrant_i`+
            `new_entrant_i:post_t`+
            `treat_i:new_entrant_i:post_t`",
            rhs=0)

d2_df <- as.data.frame(d2)
rownames(d2_df) <- c("New entrant")
print(xtable(d2_df,type='latex'))
```