---
title: "Contractor Experience"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_tex: true
    number_sections: true
header-includes:
 \usepackage{booktabs}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = FALSE)
options(xtable.comment = FALSE)
```

```{r packages,warning=FALSE,message=FALSE,include=FALSE}
library(data.table)
library(dplyr)
library(fixest)
library(ggplot2)
library(DescTools) 
library(xtable)
library(car) # for deltaMethod
```

```{r read_data,include=FALSE}
input_path='~/Dropbox/data_quickpay/qp_replication/input/'
reg_df=fread(paste0(input_path,
               'quickpay_delays.csv'))

reg_df=reg_df[!(initial_start_date>as.Date('2011-04-27') 
                              & post_t==0)]

reg_df=reg_df[!is.na(recipient_duns)]
reg_df[,action_date_year_quarter:=as.Date(action_date_year_quarter)]
```

```{r competition_delays_subsample, echo=FALSE, results='asis'}
reg_df[,project_signed_after_quickpay:=case_when(initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter>=as.Date('2011-04-27')~1,
                                                 initial_start_date<as.Date('2011-04-27') ~ 0,
                                                 initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter<as.Date('2011-04-27')~NaN)]
```

```{r define_var, include=FALSE}

# Number of projects held by a contractor in a given quarter
num_proj_per_contractor_df=reg_df[,
                .(num_projects=
                    n_distinct(contract_award_unique_key)),
              by=c('recipient_duns',
                   'action_date_year_quarter')]

# Number of projects of a given task type held by a contractor in a given quarter
num_proj_same_task_df=reg_df[,
                .(num_projects_same_task=
                    n_distinct(contract_award_unique_key)),
              by=c('recipient_duns',
                   'product_or_service_code',
                   'action_date_year_quarter')]
```

```{r num_projs_lag}
num_proj_per_contractor_df=num_proj_per_contractor_df[order(recipient_duns,
                                                            action_date_year_quarter)]

num_proj_per_contractor_df[,num_projects_lag_1:=ifelse(recipient_duns==
                                                         lag(recipient_duns),
                                                            lag(num_projects),
                                                            0)]

num_proj_per_contractor_df[,num_projects_lag_2:=ifelse(recipient_duns==lag(recipient_duns,2),
                                                            lag(num_projects,2),
                                                            0)]

num_proj_per_contractor_df[,num_projects_lag_3:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,3),
                                                            lag(num_projects,3),
                                                            0)]

num_proj_per_contractor_df[,num_projs_past_three_qtrs:=num_projects_lag_1+
                                                  num_projects_lag_2+
                                                  num_projects_lag_3]

```

```{r get_lags, include=FALSE}
num_proj_same_task_df=num_proj_same_task_df[order(recipient_duns,
                                                   product_or_service_code,
                                                   action_date_year_quarter)]

# LAG OF 1 ------------------------------

# If same contractor last quarter + same task last quarter, take lag value. Else take zero.
# Zero can indicate:
# 1. Same contractor last quarter + different task last quarter, OR
# 2. Different contractor last quarter i.e., contractor is new entrant
num_proj_same_task_df[,num_projects_same_task_lag_1:=ifelse(recipient_duns==
                                                                 lag(recipient_duns)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code),
                                                            lag(num_projects_same_task),
                                                            0)]


# LAG OF 2 ------------------------------

# If same contractor second-to-last quarter + same task second-to-last quarter, take lag-2 value. Else take zero.
# Zero can indicate:
# 1. Same contractor second-to-last quarter + different task second-to-last quarter, OR
# 2. Different contractor second-to-last quarter i.e., contractor is new entrant
num_proj_same_task_df[,num_projects_same_task_lag_2:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,2)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code,2),
                                                            lag(num_projects_same_task,2),
                                                            0)]

# LAG OF 3  ------------------------------

num_proj_same_task_df[,num_projects_same_task_lag_3:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,3)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code,3),
                                                            lag(num_projects_same_task,3),
                                                            0)]


# ADD IT UP  ------------------------------

num_proj_same_task_df[,num_projs_same_task_past_three_qtrs:=num_projects_same_task_lag_2+
                                                          num_projects_same_task_lag_1+
                                                          num_projects_same_task_lag_3]
```

```{r merge, include=FALSE}
# Merge the two datasets
num_proj_same_task_df=merge(num_proj_same_task_df,
                            num_proj_per_contractor_df,
                            by=c('recipient_duns',
                                 'action_date_year_quarter'),
                            all.x=T)

num_proj_same_task_df=num_proj_same_task_df[num_projs_same_task_past_three_qtrs<=
                                              num_projs_past_three_qtrs]
```

* Let $n^{task}_{i}=$ Number of projects of the same task held by the contractor in the three quarters before starting project $i$
* Let $n_{i}=$ Number of projects held by the contractor in the three quarters before starting project $i$

* Define:
  * Level of inexperience$_{i}= 1 - \frac{n^{task}_{i}}{n_{i}}$ if $n_{i}>0$
  * Level of inexperience$_{i}= 1$ if $n_{i}=0$

```{r project_quarter_task, include=FALSE}
# Get first quarter for every project
project_quarter=reg_df[,.(start_quarter=min(action_date_year_quarter)),
                              by=c('contract_award_unique_key',
                                 'recipient_duns',
                                 'product_or_service_code')]

project_quarter=merge(project_quarter,
                      num_proj_same_task_df,
                      by.x=c('start_quarter',
                             'recipient_duns',
                             'product_or_service_code'),
                      by.y=c('action_date_year_quarter',
                             'recipient_duns',
                             'product_or_service_code'),
                      all.x=T)
```


```{r prop_exp,include=FALSE}
# Proportion of projects on which contractor has past experience
project_quarter[,prop_exp:=ifelse(num_projs_past_three_qtrs>0,
                                 num_projs_same_task_past_three_qtrs/num_projs_past_three_qtrs,
                                       0)]

project_entrant=project_quarter[,c('contract_award_unique_key',
                                   'num_projs_same_task_past_three_qtrs',
                                   'num_projs_past_three_qtrs',
                                   'prop_exp')]

reg_df=merge(reg_df,
                    project_entrant,
                    by='contract_award_unique_key',
                    all.x = T)
```

```{r clean_sample, include=FALSE}
working_path='~/Dropbox/data_quickpay/qp_replication/working/'
reg_df_working=fread(paste0(working_path,
                 'w_clean_control.csv'))
reg_df_working[,action_date_year_quarter:=as.Date(action_date_year_quarter)]

reg_df_sub=reg_df[,c('contract_award_unique_key',
                     'action_date_year_quarter',
                                   'num_projs_same_task_past_three_qtrs',
                                   'num_projs_past_three_qtrs',
                     'prop_exp')]

reg_df_working=merge(reg_df_sub,
                     reg_df_working,
                     by=c('contract_award_unique_key',
                     'action_date_year_quarter'),
                     all.y=T)
```

```{r cts_measure, include=FALSE}
reg_df_working[,inexp:=1-prop_exp]
```

```{r cts_measure_reg,include=FALSE}
m1=feols(num_projs_same_task_past_three_qtrs~treat_i+
          treat_i:post_t+
          log(wins_project_quarter_stage)+
          wins_number_of_offers_received+
          log(winsorized_initial_budget_i)+
          log(winsorized_initial_duration_in_days_i)+
          post_t:wins_number_of_offers_received+
          post_t:log(winsorized_initial_budget_i)+
          post_t:log(winsorized_initial_duration_in_days_i)|
          action_date_year_quarter+
          product_or_service_code+
          naics_code,
      cluster=~contract_award_unique_key, # clustered at project level
      data=subset(reg_df_working,competitively_awarded_i==1))

m2=feols(num_projs_past_three_qtrs~treat_i+
          treat_i:post_t+
          log(wins_project_quarter_stage)+
          wins_number_of_offers_received+
          log(winsorized_initial_budget_i)+
          log(winsorized_initial_duration_in_days_i)+
          post_t:wins_number_of_offers_received+
          post_t:log(winsorized_initial_budget_i)+
          post_t:log(winsorized_initial_duration_in_days_i)|
          action_date_year_quarter+
          product_or_service_code+
          naics_code,
      cluster=~contract_award_unique_key, # clustered at project level
      data=subset(reg_df_working,competitively_awarded_i==1))

m3=feols(inexp~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df_working,competitively_awarded_i==1))

cts_ols=list(m1,m2,m3)
```

# Discretizing 

* Inexperienced $= 1$(Level of inexperience$_{i}>0.5$)
    * This means less than 50% of contractor projects in the last three quarters were of same task
* Inexperienced $= 1$(Level of inexperience$_{i}>0.7$)
    * This means less than 30% of contractor projects in the last three quarters were of same task type

```{r task_inexperienced, include=FALSE}
reg_df_working[,inexperienced_0.5:=ifelse(inexp>0.5,1,0)]
reg_df_working[,inexperienced_0.7:=ifelse(inexp>0.7,1,0)]
```

```{r cutoff_0, include=FALSE}
m1=feglm(inexperienced_0.5~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df_working,competitively_awarded_i==1))

m2=feglm(inexperienced_0.7~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df_working,competitively_awarded_i==1))

discretized_regs=list(m1,m2)
```

```{r output, echo=FALSE, results='asis'}
setFixest_dict(c("wins_percentage_delay"="\\textit{Percent delay rate}$_{it}$",
                 "treat_i"="$Treat_i$",
                 "post_t"="$Post_t$",
                 "num_projs_past_three_qtrs"="Num projects past 3 qtrs",
                 "num_projs_same_task_past_three_qtrs"="Num projects of same task past 3 qtrs",
                 "project_signed_after_quickpay"="$SA_i$",
                 "inexp"="IE",
                 "inexperienced_0.7"="IE",
                 "inexperienced_0.5"="IE",
                 "log(wins_project_quarter_stage)"="Ln(Stage)",
                 "action_date_year_quarter"="Time",
                      "quarter_number"="$QtrNum$",
                 "product_or_service_code"="Task",
                 "naics_code"="Industry",
                 "contract_award_unique_key"="Project ID",
                 "wins_number_of_offers_received"="Num offers",
                 "log(winsorized_initial_budget_i)"="Ln(Initial Budget)",
                  "log(winsorized_initial_duration_in_days_i)"="Ln(Initial Duration)"))

etable(cts_ols,
       tex=T,
       drop=c('%wins_project_quarter_stage',
              '%wins_number_of_offers_received',
              '%winsorized_initial_budget_i',
              '%winsorized_initial_duration_in_days_i',
              '%post_t:wins_number_of_offers_received',
              '%post_t:winsorized_initial_budget_i',
              '%post_t:winsorized_initial_duration_in_days_i'),
       style.tex = style.tex(depvar.title = "",
                             model.title = "\\midrule",
                             model.format = "I",
                             var.title = "\\midrule",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "\\midrule",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       title="Continuous measure",
       digits='r3',
       digits.stats = 'r2',
       fitstat = c('r2','pr2','n'),
       fontsize = "small")

etable(discretized_regs,
       tex=T,
       drop=c('%wins_project_quarter_stage',
              '%wins_number_of_offers_received',
              '%winsorized_initial_budget_i',
              '%winsorized_initial_duration_in_days_i',
              '%post_t:wins_number_of_offers_received',
              '%post_t:winsorized_initial_budget_i',
              '%post_t:winsorized_initial_duration_in_days_i'),
       style.tex = style.tex(depvar.title = "",
                             model.title = "\\midrule",
                             model.format = "I",
                             var.title = "\\midrule",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "\\midrule",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       headers=list("Threshold=0.5"=1,
                    "Threshold=0.7"=1),
       digits='r3',
       digits.stats = 'r2',
       fitstat = c('r2','pr2','n'),
       fontsize = "small")
```

