---
title: "Bidding Metrics"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_tex: false
    number_sections: true
header-includes:
 \usepackage{booktabs,longtable,dcolumn}
 \usepackage{multirow,array}
 \usepackage{wrapfig,float}
 \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages,warning=FALSE,message=FALSE,include=FALSE}
library(data.table)
library(dplyr)
library(lfe)
library(stargazer)
library(fixest)
library(tidyverse)
library(zoo) # for year quarter
library(DescTools) 
library(corrplot)
```

```{r read_data,include=FALSE}
working_path='~/Dropbox/data_quickpay/qp_replication/working/'
reg_df_subset=fread(paste0(working_path,
                 'w_clean_control.csv'))
```

```{r remove_na,include=FALSE}
reg_df_subset=reg_df_subset[!is.na(recipient_duns)]
```

```{r competition_delays_subsample, echo=FALSE, results='asis'}
reg_df_subset[,project_signed_after_quickpay:=case_when(initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter>=as.Date('2011-04-27')~1,
                                                 initial_start_date<as.Date('2011-04-27') ~ 0,
                                                 initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter<as.Date('2011-04-27')~NaN)]

reg_df_subset[,quarter_when_project_signed:=as.Date(as.yearqtr(as.Date(initial_start_date)),
                                                       frac = 1)]
```

```{r define_var, include=FALSE}
# Number of projects held by a contractor in a given quarter
num_proj_per_contractor_df=reg_df_subset[,
                .(num_projects=
                    n_distinct(contract_award_unique_key)),
              by=c('recipient_duns',
                   'action_date_year_quarter')]

# Number of projects of a given task type held by a contractor in a given quarter
num_proj_same_task_df=reg_df_subset[,
                .(num_projects_same_task=
                    n_distinct(contract_award_unique_key)),
              by=c('recipient_duns',
                   'product_or_service_code',
                   'action_date_year_quarter')]

# Merge the two datasets
num_proj_same_task_df=merge(num_proj_same_task_df,
                            num_proj_per_contractor_df,
                            by=c('recipient_duns',
                                 'action_date_year_quarter'),
                            all.x=T)

num_proj_same_task_df=num_proj_same_task_df[order(recipient_duns,
                                                   product_or_service_code,
                                                   action_date_year_quarter)]
```

```{r get_lags, include=FALSE}
###########################################
# LAG OF 1
##########################################
# If same contractor last quarter + same task last quarter, take lag value. Else take zero.
# Zero can indicate:
# 1. Same contractor last quarter + different task last quarter, OR
# 2. Different contractor last quarter i.e., contractor is new entrant
num_proj_same_task_df[,num_projects_same_task_lag_1:=ifelse(recipient_duns==
                                                                 lag(recipient_duns)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code),
                                                            lag(num_projects_same_task),
                                                            0)]

num_proj_same_task_df[,num_projects_lag_1:=ifelse(recipient_duns==lag(recipient_duns),
                                                            lag(num_projects),
                                                            0)]
###########################################
# LAG OF 2
##########################################
# If same contractor second-to-last quarter + same task second-to-last quarter, take lag-2 value. Else take zero.
# Zero can indicate:
# 1. Same contractor second-to-last quarter + different task second-to-last quarter, OR
# 2. Different contractor second-to-last quarter i.e., contractor is new entrant
num_proj_same_task_df[,num_projects_same_task_lag_2:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,2)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code,2),
                                                            lag(num_projects_same_task,2),
                                                            0)]

num_proj_same_task_df[,num_projects_lag_2:=ifelse(recipient_duns==lag(recipient_duns,2),
                                                            lag(num_projects,2),
                                                            0)]

###########################################
# LAG OF 3
##########################################
num_proj_same_task_df[,num_projects_same_task_lag_3:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,3)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code,3),
                                                            lag(num_projects_same_task,3),
                                                            0)]


num_proj_same_task_df[,num_projects_lag_3:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,3),
                                                            lag(num_projects,3),
                                                            0)]

###########################################
# ADD IT UP
##########################################

num_proj_same_task_df[,num_projs_same_task_past_three_qtrs:=num_projects_same_task_lag_2+
                                                          num_projects_same_task_lag_1+
                                                          num_projects_same_task_lag_3]


num_proj_same_task_df[,num_projs_past_three_qtrs:=num_projects_lag_1+
                                                  num_projects_lag_2+
                                                  num_projects_lag_3]

```

* Let $n^{task}_{i}=$ Number of projects of the same task held by the contractor in the three quarters before starting project $i$
* Let $n_{i}=$ Number of projects held by the contractor in the three quarters before starting project $i$

* Define:
  * Inexperienced contractor$_i$ = 1 if $n^{task}_{i}=0$ 
  * New entrant$_i$ = 1 if $n_{i}=0$
  * Level of inexperience$_{i}= 1 - \frac{n^{task}_{i}}{n_{i}}$ if $n_{i}>0$
  * Level of inexperience$_{i}= 1$ if $n_{i,k,t}=0$.
    

```{r project_quarter, include=FALSE}
# Get first quarter for every project
project_quarter=reg_df_subset[,.(start_quarter=min(action_date_year_quarter)),
                              by=c('contract_award_unique_key',
                                 'recipient_duns',
                                 'product_or_service_code')]

project_quarter=merge(project_quarter,
                      num_proj_same_task_df,
                      by.x=c('start_quarter',
                             'recipient_duns',
                             'product_or_service_code'),
                      by.y=c('action_date_year_quarter',
                             'recipient_duns',
                             'product_or_service_code'),
                      all.x=T)

# Task inexperienced if
project_quarter[,task_inexperienced_i:=ifelse(num_projs_same_task_past_three_qtrs==0,1,0)]
project_quarter[,new_entrant_i:=ifelse(num_projs_past_three_qtrs==0,1,0)]

# Proportion of projects on which contractor has past experience
project_quarter[,prop_exp:=ifelse(num_projs_past_three_qtrs>0,
                                 num_projs_same_task_past_three_qtrs/num_projs_past_three_qtrs,
                                       0)]

project_entrant=project_quarter[,c('contract_award_unique_key',
                                   'task_inexperienced_i',
                                   'new_entrant_i',
                                   'num_projs_same_task_past_three_qtrs',
                                   'num_projs_past_three_qtrs',
                                   'prop_exp')]

reg_df_subset=merge(reg_df_subset,
                    project_entrant,
                    by='contract_award_unique_key',
                    all.x = T)
```

```{r define_inexp, include=FALSE}
reg_df_subset[,inexp:=1-prop_exp]
```

```{r get_first_reported, include=FALSE}
reg_df_first_reported=unique(reg_df_subset,
                             by='contract_award_unique_key')

reg_df_first_reported=subset(reg_df_first_reported,
                             initial_start_date>as.Date('2009-12-31') & 
                               initial_start_date<as.Date('2012-03-31')&
                              competitively_awarded_i==1 )

reg_df_first_reported=reg_df_first_reported[!(quarter_when_project_signed>as.Date('2011-04-27')
                      & project_signed_after_quickpay==0)]
```

```{r cor_plot, echo=FALSE, eval=FALSE}
old_names=c('treat_new',
          #  'wins_percentage_delay',
          #  'post_t',
                         'project_signed_after_quickpay',
                         'new_entrant_i',
                         'number_of_offers_received',
                         'winsorized_initial_duration_in_days_i',
                         'winsorized_initial_budget_i')
a=reg_df_first_reported[,..old_names]
a=na.omit(a)

new_names=c('Treat',
          #  'Delay',
         #   'Post',
            'SA',
            'Entrant',
            'Bids',
            'Duration',
            'Budget')


setnames(a,old=old_names,new=new_names)
corrplot::corrplot(cor(a),method="color")
```

# Effect on Bids

```{r competition_subsample_i, include=FALSE}
bids=feols(number_of_offers_received~treat_new+
           treat_new:project_signed_after_quickpay+
           treat_new:project_signed_after_quickpay:new_entrant_i+
           new_entrant_i+
           treat_new:new_entrant_i+
           new_entrant_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
       cluster=~contract_award_unique_key,
       data=reg_df_first_reported[number_of_offers_received>=1])

duration=feols(winsorized_initial_duration_in_days_i~treat_new+
                                   treat_new:project_signed_after_quickpay+
                                  treat_new:project_signed_after_quickpay:new_entrant_i+
                                new_entrant_i+
                                treat_new:new_entrant_i+
                                new_entrant_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
             cluster=~contract_award_unique_key,
             data=reg_df_first_reported)

budget=feols(I(winsorized_initial_budget_i/1000)~treat_new+
                                   treat_new:project_signed_after_quickpay+
                                  treat_new:project_signed_after_quickpay:new_entrant_i+
                                new_entrant_i+
                                treat_new:new_entrant_i+
                                new_entrant_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
             cluster=~contract_award_unique_key,
             data=reg_df_first_reported)

entrant=list(bids,duration,budget)

```

```{r competition_subsample_ii, include=FALSE}
bids=feols(number_of_offers_received~treat_new+
           treat_new:project_signed_after_quickpay+
           treat_new:project_signed_after_quickpay:task_inexperienced_i+
           task_inexperienced_i+
           treat_new:task_inexperienced_i+
           task_inexperienced_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
       cluster=~contract_award_unique_key,
       data=reg_df_first_reported[number_of_offers_received>=1])

duration=feols(winsorized_initial_duration_in_days_i~treat_new+
                                   treat_new:project_signed_after_quickpay+
                                  treat_new:project_signed_after_quickpay:task_inexperienced_i+
                                task_inexperienced_i+
                                treat_new:task_inexperienced_i+
                                task_inexperienced_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
             cluster=~contract_award_unique_key,
             data=reg_df_first_reported)

budget=feols(I(winsorized_initial_budget_i/1000)~treat_new+
                                   treat_new:project_signed_after_quickpay+
                                  treat_new:project_signed_after_quickpay:task_inexperienced_i+
                                task_inexperienced_i+
                                treat_new:task_inexperienced_i+
                                task_inexperienced_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed,
             cluster=~contract_award_unique_key,
             data=reg_df_first_reported)

task_experience=list(bids,duration,budget)
```

```{r output, echo=FALSE,results='asis'}
setFixest_dict(c("wins_percentage_delay"="Percentage delay rate",
                 "treat_new"="Treat",
                 "post_t"="Post",
                 "project_signed_after_quickpay"="SA$_i$",
                 "inexp"="Level of inexperience",
                 "log(wins_project_quarter_stage)"="Ln(Stage)",
                 "new_entrant_i"="New Entrant",
                 "task_inexperienced_i"="Inexperienced contractor",
                 "action_date_year_quarter"="Time",
                 "product_or_service_code"="Task",
                 "naics_code"="Industry",
                 "contract_award_unique_key"="Project ID",
                 "number_of_offers_received"="Num offers",
                 "quarter_when_project_signed"="Time",
                 "I(winsorized_initial_budget_i/1000)"="Initial Budget (000s)",
                  "winsorized_initial_duration_in_days_i"="Initial Duration"))

etable(entrant,
       tex=T,
       style.tex = style.tex(depvar.title = "",
                             model.title = "",
                             model.format = "I",
                             var.title = "",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       digits='r2',
       digits.stats = 'r2',
       fontsize = "small")

etable(task_experience,
       tex=T,
       style.tex = style.tex(depvar.title = "",
                             model.title = "",
                             model.format = "I",
                             var.title = "",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       digits='r2',
       digits.stats = 'r2',
       fontsize = "small")
```

# Effect on Delays

## Old vs New Entrant

```{r new_entrant_bid_delays, include=FALSE}
m1=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)+
                            post_t,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,new_entrant_i==1&
                                        competitively_awarded_i==1))

m2=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,new_entrant_i==1&
                                        competitively_awarded_i==1))

m3=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,new_entrant_i==1&
                                        competitively_awarded_i==1))

m4=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            naics_code+
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,new_entrant_i==1&
                                        competitively_awarded_i==1))

new_entrant_delays=list(m1,m2,m3,m4)
```

```{r old_entrant_bid_delays, include=FALSE}
m1=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)+
                            post_t,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,new_entrant_i==0&
                                        competitively_awarded_i==1))

m2=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,new_entrant_i==0&
                                        competitively_awarded_i==1))

m3=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,new_entrant_i==0&
                                        competitively_awarded_i==1))

m4=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            naics_code+
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,new_entrant_i==0&
                                        competitively_awarded_i==1))

old_entrant_delays=list(m1,m2,m3,m4)
```

```{r output_3, echo=FALSE,results='asis'}
etable(old_entrant_delays,
       new_entrant_delays,
        headers=list(":_:"=list("Old entrants"=4,
                    "New entrants"=4)),
       tex=T,
       style.tex = style.tex(depvar.title = "",
                             model.title = "",
                             model.format = "I",
                             var.title = "",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       digits='r3',
       digits.stats = 'r2',
       fontsize = "small")

```

# Experienced vs Inexperienced

```{r inexperienced_bid_delays, include=FALSE}
m1=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)+
                            post_t,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,task_inexperienced_i==1&
                                        competitively_awarded_i==1))

m2=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,task_inexperienced_i==1&
                                        competitively_awarded_i==1))

m3=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,task_inexperienced_i==1&
                                        competitively_awarded_i==1))

m4=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            naics_code+
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,task_inexperienced_i==1&
                                        competitively_awarded_i==1))

task_inexperienced_delays=list(m1,m2,m3,m4)
```

```{r experienced_bid_delays, include=FALSE}
m1=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)+
                            post_t,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,task_inexperienced_i==0&
                                        competitively_awarded_i==1))

m2=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,task_inexperienced_i==0&
                                        competitively_awarded_i==1))

m3=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,task_inexperienced_i==0&
                                        competitively_awarded_i==1))

m4=feols(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            naics_code+
                            product_or_service_code+
                            action_date_year_quarter,
                            cluster=~contract_award_unique_key,
                          data=subset(reg_df_subset,task_inexperienced_i==0&
                                        competitively_awarded_i==1))

task_experienced_delays=list(m1,m2,m3,m4)
```

```{r output_4, echo=FALSE,results='asis'}
etable(task_experienced_delays,
        task_inexperienced_delays,
        headers=list(":_:"=list("Experienced contractors"=4,
                    "Inxperienced contractors"=4)),
       tex=T,
       style.tex = style.tex(depvar.title = "",
                             model.title = "",
                             model.format = "I",
                             var.title = "",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       digits='r3',
       digits.stats = 'r2',
       fontsize = "small")
```