---
title: "Competition -- Contractor Experience"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_tex: true
    number_sections: true
header-includes:
 \usepackage{booktabs,longtable,dcolumn}
 \usepackage{multirow,array,makecell}
 \usepackage{wrapfig,float}
 \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages,warning=FALSE,message=FALSE,include=FALSE}
library(data.table)
library(dplyr)
library(fixest)
library(tidyverse)
library(DescTools) 
```

```{r read_data,include=FALSE}
input_path='~/Dropbox/data_quickpay/qp_replication/input/'
reg_df=fread(paste0(input_path,
               'quickpay_delays.csv'))

reg_df=reg_df[!(initial_start_date>as.Date('2011-04-27') 
                              & post_t==0)]

reg_df=reg_df[!is.na(recipient_duns)]
```

```{r competition_delays_subsample, echo=FALSE, results='asis'}
reg_df[,project_signed_after_quickpay:=case_when(initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter>=as.Date('2011-04-27')~1,
                                                 initial_start_date<as.Date('2011-04-27') ~ 0,
                                                 initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter<as.Date('2011-04-27')~NaN)]
```

```{r define_var, include=FALSE}

# Number of projects held by a contractor in a given quarter
num_proj_per_contractor_df=reg_df[,
                .(num_projects=
                    n_distinct(contract_award_unique_key)),
              by=c('recipient_duns',
                   'action_date_year_quarter')]

# Number of projects of a given task type held by a contractor in a given quarter
num_proj_same_task_df=reg_df[,
                .(num_projects_same_task=
                    n_distinct(contract_award_unique_key)),
              by=c('recipient_duns',
                   'product_or_service_code',
                   'action_date_year_quarter')]

# Merge the two datasets
num_proj_same_task_df=merge(num_proj_same_task_df,
                            num_proj_per_contractor_df,
                            by=c('recipient_duns',
                                 'action_date_year_quarter'),
                            all.x=T)

# Proportion of projects of same task type held by a contractor in a given quarter
#num_proj_same_task_df[,prop_projects_same_task:=num_projects_same_task/num_projects]

num_proj_same_task_df=num_proj_same_task_df[order(recipient_duns,
                                                   product_or_service_code,
                                                   action_date_year_quarter)]
```

```{r get_lags, include=FALSE}
###########################################
# LAG OF 1
##########################################
# If same contractor last quarter + same task last quarter, take lag value. Else take zero.
# Zero can indicate:
# 1. Same contractor last quarter + different task last quarter, OR
# 2. Different contractor last quarter i.e., contractor is new entrant
num_proj_same_task_df[,num_projects_same_task_lag_1:=ifelse(recipient_duns==
                                                                 lag(recipient_duns)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code),
                                                            lag(num_projects_same_task),
                                                            0)]

num_proj_same_task_df[,num_projects_lag_1:=ifelse(recipient_duns==lag(recipient_duns),
                                                            lag(num_projects),
                                                            0)]
###########################################
# LAG OF 2
##########################################
# If same contractor second-to-last quarter + same task second-to-last quarter, take lag-2 value. Else take zero.
# Zero can indicate:
# 1. Same contractor second-to-last quarter + different task second-to-last quarter, OR
# 2. Different contractor second-to-last quarter i.e., contractor is new entrant
num_proj_same_task_df[,num_projects_same_task_lag_2:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,2)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code,2),
                                                            lag(num_projects_same_task,2),
                                                            0)]

num_proj_same_task_df[,num_projects_lag_2:=ifelse(recipient_duns==lag(recipient_duns,2),
                                                            lag(num_projects,2),
                                                            0)]

###########################################
# LAG OF 3
##########################################
num_proj_same_task_df[,num_projects_same_task_lag_3:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,3)&
                                                            product_or_service_code==
                                                              lag(product_or_service_code,3),
                                                            lag(num_projects_same_task,3),
                                                            0)]


num_proj_same_task_df[,num_projects_lag_3:=ifelse(recipient_duns==
                                                                 lag(recipient_duns,3),
                                                            lag(num_projects,3),
                                                            0)]

###########################################
# ADD IT UP
##########################################

num_proj_same_task_df[,num_projs_same_task_past_three_qtrs:=num_projects_same_task_lag_2+
                                                          num_projects_same_task_lag_1+
                                                          num_projects_same_task_lag_3]


num_proj_same_task_df[,num_projs_past_three_qtrs:=num_projects_lag_1+
                                                  num_projects_lag_2+
                                                  num_projects_lag_3]

```

# Time Invariant Status

* Let $n^{task}_{i}=$ Number of projects of the same task held by the contractor in the three quarters before starting project $i$
* Let $n_{i}=$ Number of projects held by the contractor in the three quarters before starting project $i$

* Define:
  * Inexperienced contractor$_i$ = 1 if $n^{task}_{i}=0$ 
  * New entrant$_i$ = 1 if $n_{i}=0$
  * Level of inexperience$_{i}= 1 - \frac{n^{task}_{i}}{n_{i}}$ if $n_{i}>0$
  * Level of inexperience$_{i}= 1$ if $n_{i,k,t}=0$.
    

```{r project_quarter, include=FALSE}
# Get first quarter for every project
project_quarter=reg_df[,.(start_quarter=min(action_date_year_quarter)),
                              by=c('contract_award_unique_key',
                                 'recipient_duns',
                                 'product_or_service_code')]

project_quarter=merge(project_quarter,
                      num_proj_same_task_df,
                      by.x=c('start_quarter',
                             'recipient_duns',
                             'product_or_service_code'),
                      by.y=c('action_date_year_quarter',
                             'recipient_duns',
                             'product_or_service_code'),
                      all.x=T)

# Task inexperienced if
project_quarter[,task_inexperienced_i:=ifelse(num_projs_same_task_past_three_qtrs==0,1,0)]
project_quarter[,new_entrant_i:=ifelse(num_projs_past_three_qtrs==0,1,0)]

# Proportion of projects on which contractor has past experience
project_quarter[,prop_exp:=ifelse(num_projs_past_three_qtrs>0,
                                 num_projs_same_task_past_three_qtrs/num_projs_past_three_qtrs,
                                       0)]

project_entrant=project_quarter[,c('contract_award_unique_key',
                                   'task_inexperienced_i',
                                   'new_entrant_i',
                                   'num_projs_same_task_past_three_qtrs',
                                   'num_projs_past_three_qtrs',
                                   'prop_exp')]

reg_df=merge(reg_df,
                    project_entrant,
                    by='contract_award_unique_key',
                    all.x = T)
```

```{r define_inexp, include=FALSE}
reg_df[,inexp:=1-prop_exp]
```

```{r hist_1, echo=FALSE, fig.height=4, fig.width=5, results='asis'}
hist(subset(reg_df,competitively_awarded_i==1)$task_inexperienced_i,
     main="Task inexperience",
     xlab="",
     ylab="")
```

```{r hist_2, echo=FALSE, fig.height=4, fig.width=5,results='asis'}
hist(subset(reg_df,competitively_awarded_i==1)$new_entrant_i,
     main="New Entrant",
     xlab="",
     ylab="")
```

```{r hist_3, echo=FALSE, fig.height=4, fig.width=5,results='asis'}
hist(subset(reg_df,competitively_awarded_i==1)$inexp,
     main="Inexperience",
     xlab="",
     ylab="")
```

```{r plot_new_entrants, echo=FALSE,fig.height=4, fig.width=5,results='asis'}
num_new_entrants=unique(subset(reg_df,competitively_awarded_i==1),by='contract_award_unique_key')[,
                                    .(num_new_entrants=sum(new_entrant_i,na.rm=T),
                                      num_inexperienced_entrants=sum(task_inexperienced_i,na.rm=T)),
                                        by=c('action_date_year_quarter',
                                             'treat_i')]

num_new_entrants[,business_type:=ifelse(treat_i==1,'S','O')]
num_new_entrants[,year_quarter:=format(action_date_year_quarter,"%Y-%b")]
num_new_entrants=num_new_entrants[order(action_date_year_quarter,treat_i)]

ggplot(num_new_entrants,
       aes(x=year_quarter,
           y=num_new_entrants,
           group=treat_i))+
  geom_point(aes(shape=business_type),size=1.5)+
  geom_line(aes(linetype=business_type, color=business_type),alpha=0.7)+
  scale_x_discrete(limits=num_new_entrants$year_quarter)+
  theme_minimal()+
  labs(x="Time", 
       y = "Number of projects held \n by new entrants")+
  scale_linetype_manual(name  ="",
                        breaks=c("S", "O"),
                        labels=c("Treated","Control"),
                        values=c("solid","dashed"))+
  scale_color_manual(name  ="",
                     breaks=c("S", "O"),
                     labels=c("Treated","Control"),
                     values=c('black','black'))+
  scale_shape_manual(name  ="",
                     breaks=c("S", "O"),
                     labels=c("Treated","Control"),
                     values=c(16,17))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))
```

```{r plot_inexp_contractors, echo=FALSE,fig.height=4, fig.width=5,results='asis'}
ggplot(num_new_entrants,
       aes(x=year_quarter,
           y=num_inexperienced_entrants,
           group=treat_i))+
  geom_point(aes(shape=business_type),size=1.5)+
  geom_line(aes(linetype=business_type, color=business_type),alpha=0.7)+
  scale_x_discrete(limits=num_new_entrants$year_quarter)+
  theme_minimal()+
  labs(x="Time", 
       y = "Number of projects held \n by inexperienced contractors")+
  scale_linetype_manual(name  ="",
                        breaks=c("S", "O"),
                        labels=c("Treated","Control"),
                        values=c("solid","dashed"))+
  scale_color_manual(name  ="",
                     breaks=c("S", "O"),
                     labels=c("Treated","Control"),
                     values=c('black','black'))+
  scale_shape_manual(name  ="",
                     breaks=c("S", "O"),
                     labels=c("Treated","Control"),
                     values=c(16,17))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))
```

```{r low_exp_contractors, echo=FALSE,fig.height=4, fig.width=5,results='asis'}
reg_df[,inexp_levels:=case_when(num_projs_same_task_past_three_qtrs==0~
                                         "No task experience",
                                       num_projs_same_task_past_three_qtrs>0 &
                                         num_projs_same_task_past_three_qtrs<=25~
                                         "1-25 tasks previously",
                                       num_projs_same_task_past_three_qtrs>25 ~
                                         ">25 tasks previously")
                                       ]

no_exp_tasks=unique(subset(reg_df,
                           competitively_awarded_i==1 &
                             inexp_levels=="No task experience"),
                        by='contract_award_unique_key')[,
                                    .(num_new_entrants=.N),
                                        by=c('action_date_year_quarter',
                                             'treat_i')]

no_exp_tasks[,business_type:=ifelse(treat_i==1,'S','O')]
no_exp_tasks[,year_quarter:=format(action_date_year_quarter,"%Y-%b")]
no_exp_tasks=no_exp_tasks[order(action_date_year_quarter,treat_i)]

ggplot(no_exp_tasks,
       aes(x=year_quarter,
           y=num_new_entrants,
           group=business_type))+
  geom_point(aes(shape=business_type),size=1.5)+
  geom_line(aes(linetype=business_type, color=business_type),alpha=0.7)+
  scale_x_discrete(limits=num_new_entrants$year_quarter)+
  theme_minimal()+
  labs(x="Time", 
       y = "Number of projects held \n by contractors with \n NO task experience")+
  scale_linetype_manual(name  ="",
                        breaks=c("S", "O"),
                        labels=c("Treated","Control"),
                        values=c("solid","dashed"))+
  scale_color_manual(name  ="",
                     breaks=c("S", "O"),
                     labels=c("Treated","Control"),
                     values=c('black','black'))+
  scale_shape_manual(name  ="",
                     breaks=c("S", "O"),
                     labels=c("Treated","Control"),
                     values=c(16,17))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))
```

```{r mod_exp_contractors, echo=FALSE,fig.height=4, fig.width=5,results='asis'}
mod_exp_tasks=unique(subset(reg_df,
                           competitively_awarded_i==1 &
                             inexp_levels=="1-25 tasks previously"),
                        by='contract_award_unique_key')[,
                                    .(num_new_entrants=.N),
                                        by=c('action_date_year_quarter',
                                             'treat_i')]

mod_exp_tasks[,business_type:=ifelse(treat_i==1,'S','O')]
mod_exp_tasks[,year_quarter:=format(action_date_year_quarter,"%Y-%b")]
mod_exp_tasks=mod_exp_tasks[order(action_date_year_quarter,treat_i)]
ggplot(mod_exp_tasks,
       aes(x=year_quarter,
           y=num_new_entrants,
           group=business_type))+
  geom_point(aes(shape=business_type),size=1.5)+
  geom_line(aes(linetype=business_type, color=business_type),alpha=0.7)+
  scale_x_discrete(limits=num_new_entrants$year_quarter)+
  theme_minimal()+
  labs(x="Time", 
       y = "Number of projects held \n by contractors with moderate \n task experience (1-25) projects")+
  scale_linetype_manual(name  ="",
                        breaks=c("S", "O"),
                        labels=c("Treated","Control"),
                        values=c("solid","dashed"))+
  scale_color_manual(name  ="",
                     breaks=c("S", "O"),
                     labels=c("Treated","Control"),
                     values=c('black','black'))+
  scale_shape_manual(name  ="",
                     breaks=c("S", "O"),
                     labels=c("Treated","Control"),
                     values=c(16,17))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))
```

```{r high_exp_contractors, echo=FALSE,fig.height=4, fig.width=5,results='asis'}
high_exp_tasks=unique(subset(reg_df,
                           competitively_awarded_i==1 &
                             inexp_levels==">25 tasks previously"),
                        by='contract_award_unique_key')[,
                                    .(num_new_entrants=.N),
                                        by=c('action_date_year_quarter',
                                             'treat_i')]

high_exp_tasks[,business_type:=ifelse(treat_i==1,'S','O')]
high_exp_tasks[,year_quarter:=format(action_date_year_quarter,"%Y-%b")]
high_exp_tasks=high_exp_tasks[order(action_date_year_quarter,treat_i)]
ggplot(high_exp_tasks,
       aes(x=year_quarter,
           y=num_new_entrants,
           group=business_type))+
  geom_point(aes(shape=business_type),size=1.5)+
  geom_line(aes(linetype=business_type, color=business_type),alpha=0.7)+
  scale_x_discrete(limits=num_new_entrants$year_quarter)+
  theme_minimal()+
  labs(x="Time", 
       y = "Number of projects held \n by contractors with high \n task experience (>25 projects)")+
  scale_linetype_manual(name  ="",
                        breaks=c("S", "O"),
                        labels=c("Treated","Control"),
                        values=c("solid","dashed"))+
  scale_color_manual(name  ="",
                     breaks=c("S", "O"),
                     labels=c("Treated","Control"),
                     values=c('black','black'))+
  scale_shape_manual(name  ="",
                     breaks=c("S", "O"),
                     labels=c("Treated","Control"),
                     values=c(16,17))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))
```

# Regression results

```{r inexp_logit, include=FALSE}
m1=feglm(task_inexperienced_i~treat_i+
                                  treat_i:post_t+
                                  post_t,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))


m2=feglm(task_inexperienced_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 post_t,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))


m3=feglm(task_inexperienced_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))


m4=feglm(task_inexperienced_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter+
                                  product_or_service_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m5=feglm(task_inexperienced_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m6=feglm(task_inexperienced_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m7=feglm(task_inexperienced_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

task_inexperience_logit=list(m1,m2,m3,m4,m5,m6,m7)
```

```{r inexp_ols, include=FALSE}
m1=feols(wins_percentage_delay~treat_i+
                                  task_inexperienced_i+
                                  treat_i:task_inexperienced_i+
                                  post_t:task_inexperienced_i+
                                  treat_i:post_t+
                                  treat_i:post_t:task_inexperienced_i+
                                  post_t,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m2=feols(wins_percentage_delay~treat_i+
                                  task_inexperienced_i+
                                  treat_i:task_inexperienced_i+
                                  post_t:task_inexperienced_i+
                                  treat_i:post_t+
                                  treat_i:post_t:task_inexperienced_i+
                                 log(wins_project_quarter_stage)+
                                  post_t,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m3=feols(wins_percentage_delay~treat_i+
                                  task_inexperienced_i+
                                  treat_i:task_inexperienced_i+
                                  post_t:task_inexperienced_i+
                                  treat_i:post_t+
                                  treat_i:post_t:task_inexperienced_i+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m4=feols(wins_percentage_delay~treat_i+
                                  task_inexperienced_i+
                                  treat_i:task_inexperienced_i+
                                  post_t:task_inexperienced_i+
                                  treat_i:post_t+
                                  treat_i:post_t:task_inexperienced_i+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter+
                                  product_or_service_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m5=feols(wins_percentage_delay~treat_i+
                                  task_inexperienced_i+
                                  treat_i:task_inexperienced_i+
                                  post_t:task_inexperienced_i+
                                  treat_i:post_t+
                                  treat_i:post_t:task_inexperienced_i+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m6=feols(wins_percentage_delay~treat_i+
                                  task_inexperienced_i+
                                  treat_i:task_inexperienced_i+
                                  post_t:task_inexperienced_i+
                                  treat_i:post_t+
                                  treat_i:post_t:task_inexperienced_i+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m7=feols(wins_percentage_delay~treat_i+
                                  task_inexperienced_i+
                                  treat_i:task_inexperienced_i+
                                  post_t:task_inexperienced_i+
                                  treat_i:post_t+
                                  treat_i:post_t:task_inexperienced_i+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

task_inexperience_delays=list(m1,m2,m3,m4,m5,m6,m7)
```

```{r new_entrant_logit, include=FALSE}
m1=feglm(new_entrant_i~treat_i+
                                  treat_i:post_t+
                                  post_t,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))


m2=feglm(new_entrant_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 post_t,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))


m3=feglm(new_entrant_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))


m4=feglm(new_entrant_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter+
                                  product_or_service_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m5=feglm(new_entrant_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m6=feglm(new_entrant_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m7=feglm(new_entrant_i~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  family='binomial',
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

new_entrant_logit=list(m1,m2,m3,m4,m5,m6,m7)
```

```{r new_entrant_ols, include=FALSE}
m1=feols(wins_percentage_delay~treat_i+
                                  new_entrant_i+
                                  treat_i:new_entrant_i+
                                  post_t:new_entrant_i+
                                  treat_i:post_t+
                                  treat_i:post_t:new_entrant_i+
                                  post_t,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m2=feols(wins_percentage_delay~treat_i+
                                  new_entrant_i+
                                  treat_i:new_entrant_i+
                                  post_t:new_entrant_i+
                                  treat_i:post_t+
                                  treat_i:post_t:new_entrant_i+
                                 log(wins_project_quarter_stage)+
                                  post_t,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m3=feols(wins_percentage_delay~treat_i+
                                  new_entrant_i+
                                  treat_i:new_entrant_i+
                                  post_t:new_entrant_i+
                                  treat_i:post_t+
                                  treat_i:post_t:new_entrant_i+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m4=feols(wins_percentage_delay~treat_i+
                                  new_entrant_i+
                                  treat_i:new_entrant_i+
                                  post_t:new_entrant_i+
                                  treat_i:post_t+
                                  treat_i:post_t:new_entrant_i+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter+
                                  product_or_service_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m5=feols(wins_percentage_delay~treat_i+
                                  new_entrant_i+
                                  treat_i:new_entrant_i+
                                  post_t:new_entrant_i+
                                  treat_i:post_t+
                                  treat_i:post_t:new_entrant_i+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m6=feols(wins_percentage_delay~treat_i+
                                  new_entrant_i+
                                  treat_i:new_entrant_i+
                                  post_t:new_entrant_i+
                                  treat_i:post_t+
                                  treat_i:post_t:new_entrant_i+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m7=feols(wins_percentage_delay~treat_i+
                                  new_entrant_i+
                                  treat_i:new_entrant_i+
                                  post_t:new_entrant_i+
                                  treat_i:post_t+
                                  treat_i:post_t:new_entrant_i+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

new_entrant_delays=list(m1,m2,m3,m4,m5,m6,m7)
```

```{r output, echo=FALSE, results='asis'}
setFixest_dict(c("wins_percentage_delay"="Percentage delay rate",
                 "treat_i"="Treat",
                 "post_t"="Post",
                 "project_signed_after_quickpay"="SA$_i$",
                 "inexp"="Level of inexperience",
                 "log(wins_project_quarter_stage)"="Ln(Stage)",
                 "new_entrant_i"="New Entrant",
                 "task_inexperienced_i"="Inexperienced contractor",
                 "action_date_year_quarter"="Time",
                 "product_or_service_code"="Task",
                 "naics_code"="Industry",
                 "contract_award_unique_key"="Project ID",
                 "wins_number_of_offers_received"="Num offers",
                 "log(winsorized_initial_budget_i)"="Ln(Initial Budget)",
                  "log(winsorized_initial_duration_in_days_i)"="Ln(Initial Duration)"))

etable(task_inexperience_logit,
       tex=T,
       style.tex = style.tex(depvar.title = "",
                             model.title = "",
                             model.format = "I",
                             var.title = "",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       digits='r3',
       digits.stats = 'r2',
       title="Logit model",
       fontsize = "small")

etable(task_inexperience_delays,
       tex=T,
       style.tex = style.tex(depvar.title = "",
                             model.title = "",
                             model.format = "I",
                             var.title = "",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       digits='r3',
       digits.stats = 'r2',
       fontsize = "small")

etable(new_entrant_logit,
       tex=T,
       style.tex = style.tex(depvar.title = "",
                             model.title = "",
                             model.format = "I",
                             var.title = "",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       digits='r3',
       digits.stats = 'r2',
       title="Logit model",
       fontsize = "small")

etable(new_entrant_delays,
       tex=T,
       style.tex = style.tex(depvar.title = "",
                             model.title = "",
                             model.format = "I",
                             var.title = "",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       digits='r3',
       digits.stats = 'r2',
       fontsize = "small")
```

# Regressions -- Continuous variable

```{r cts_inexp_1, include=FALSE}
m1=feols(inexp~treat_i+
                                  treat_i:post_t+
                                  post_t,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))


m2=feols(inexp~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 post_t,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))


m3=feols(inexp~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))


m4=feols(inexp~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter+
                                  product_or_service_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m5=feols(inexp~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m6=feols(inexp~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m7=feols(inexp~treat_i+
                                  treat_i:post_t+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

cts_task_inexperience_dep=list(m1,m2,m3,m4,m5,m6,m7)
```

```{r cts_inexp_ols, include=FALSE}
m1=feols(wins_percentage_delay~treat_i+
                                  inexp+
                                  treat_i:inexp+
                                  post_t:inexp+
                                  treat_i:post_t+
                                  treat_i:post_t:inexp+
                                  post_t,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m2=feols(wins_percentage_delay~treat_i+
                                  inexp+
                                  treat_i:inexp+
                                  post_t:inexp+
                                  treat_i:post_t+
                                  treat_i:post_t:inexp+
                                 log(wins_project_quarter_stage)+
                                  post_t,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m3=feols(wins_percentage_delay~treat_i+
                                  inexp+
                                  treat_i:inexp+
                                  post_t:inexp+
                                  treat_i:post_t+
                                  treat_i:post_t:inexp+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m4=feols(wins_percentage_delay~treat_i+
                                  inexp+
                                  treat_i:inexp+
                                  post_t:inexp+
                                  treat_i:post_t+
                                  treat_i:post_t:inexp+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter+
                                  product_or_service_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m5=feols(wins_percentage_delay~treat_i+
                                  inexp+
                                  treat_i:inexp+
                                  post_t:inexp+
                                  treat_i:post_t+
                                  treat_i:post_t:inexp+
                                 log(wins_project_quarter_stage)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))

m6=feols(wins_percentage_delay~treat_i+
                                  inexp+
                                  treat_i:inexp+
                                  post_t:inexp+
                                  treat_i:post_t+
                                  treat_i:post_t:inexp+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))
                                  
m7=feols(wins_percentage_delay~treat_i+
                                  inexp+
                                  treat_i:inexp+
                                  post_t:inexp+
                                  treat_i:post_t+
                                  treat_i:post_t:inexp+
                                 log(wins_project_quarter_stage)+
                                 wins_number_of_offers_received+
                                 log(winsorized_initial_budget_i)+
                                 log(winsorized_initial_duration_in_days_i)+
                                 post_t:wins_number_of_offers_received+
                                 post_t:log(winsorized_initial_budget_i)+
                                 post_t:log(winsorized_initial_duration_in_days_i)|
                                 action_date_year_quarter+
                                  product_or_service_code+
                                  naics_code,
                                  cluster=~contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df,competitively_awarded_i==1))
         
cts_task_inexperience_delays=list(m1,m2,m3,m4,m5,m6,m7)
```

```{r output_2, echo=FALSE,results='asis'}
etable(cts_task_inexperience_dep,
       tex=T,
       style.tex = style.tex(depvar.title = "",
                             model.title = "",
                             model.format = "I",
                             var.title = "",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       digits='r3',
       digits.stats = 'r2',
       fontsize = "small")

etable(cts_task_inexperience_delays,
       tex=T,
       style.tex = style.tex(depvar.title = "",
                             model.title = "",
                             model.format = "I",
                             var.title = "",
                             line.bottom = "simple",
                             line.top = "simple",
                             stats.title = "",
                             fixef.title = "",
                             fixef.suffix = " FE",
                             yesNo = c("Yes","No")),
       digits='r3',
       digits.stats = 'r2',
       fontsize = "small")
```