---
title: "Parallel Trends (Indirectly Treated): QuickPay (2009-2012)"
date: " `r format(Sys.time(), '%b %d, %Y')`"
output: 
  pdf_document:
    keep_tex: true
    number_sections: true
header-includes:
 \usepackage{booktabs,longtable,dcolumn}
 \usepackage{multirow,array}
 \usepackage{wrapfig,float}
 \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages,warning=FALSE,message=FALSE,include=FALSE}
library(openxlsx)
library(tidyverse)
library(dplyr)
library(pryr)
library(lfe) # linear fixed effects 
library(DescTools) 
library(zoo) # for year quarter
library(stargazer)
library(broom)
library(fixest)
library(data.table)
library(scales)
library(coefplot)
library(MatchIt)
library(pBrackets)
library(grid)
library(fixest)
library(xtable)
```

```{r set_path_for_exporting, include=FALSE}
tables_folder='~/Desktop/Research/QuickPay/paper/Tables/percentage_delay_rate'
figures_folder='~/Desktop/Research/QuickPay/paper/Figures'
data_folder='~/Dropbox/data_quickpay/qp_data/'
```

```{r read_data, include=FALSE}
# Keep only projects whose start dates match with API one
projects_to_keep=fread(paste0(data_folder,'projects_to_keep.csv'))

# read quarterly resampled data
df=fread(paste0(data_folder,'resampled_qp_data/qp_resampled_data_fy10_to_fy12_with_zero_obs.csv'))
# specify date columns
date_cols=c("action_date_year_quarter","last_reported_start_date","last_reported_end_date")
df[,(date_cols):= lapply(.SD, as.Date), .SDcols = date_cols]

# restrict to quarter ending June 30, 2012
df=subset(df,as.Date(action_date_year_quarter)<as.Date('2012-07-01')&
          contract_award_unique_key%in%projects_to_keep$contract_award_unique_key)

# data is truncated at July 1, 2012 -- 
# so quarter ending Sept 30, 2012 will only have values as of July 1, 2012

df_first_reported=fread(paste0(data_folder,'qp_data_first_reported.csv'))
# contains time-invariant contract characteristics -- info when contract first appeared in the data

```

```{r assign_variables_1, include=FALSE}
# Assign variables: Delay, Winsorized Delay, Post_t, Treat_i

# some projects have action dates beyond project end date 
# some could indicate projects that ended in the beginning of a quarter -- so taking 90 days difference
# dropping these -- likely admin/documentation changes

df[,diff_end_date_and_action_date:=as.numeric(last_reported_end_date-action_date_year_quarter)]
# to ensure project ended sometime this quarter
df=subset(df,diff_end_date_and_action_date>-90)


# AD: 2015-06-30; End Date: 2015-03-31

# sort by contract id and date 
df=df[order(contract_award_unique_key,
            action_date_year_quarter)]

# determine quarter-to-quarter delay
df[,delay:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1), 
                  last_reported_end_date-lag(last_reported_end_date,1),NaN)]

# winsorize quarter-to-quarter delay
df[,winsorized_delay:=Winsorize(delay,
                                probs=c(0.05,0.95),
                                na.rm=TRUE)]

#Post_t: A dummy that period t is post-treatment
df[,post_t:=ifelse(action_date_year_quarter>as.Date("2011-04-27"),1,0)]
# quickpay implemented on 27 April 2011. So all quarters starting 30 June 2011 will be in post-period

#Treat_i: A dummy that contract i is in the treatment group
df[,treat_i:=ifelse(business_type=="S",1,0)]
# quickpay was implemented for small business contracts

```

```{r delay_over_two_quarters, include=FALSE}
# keep_dates=as.Date(c('2009-12-31',
#                       '2010-06-30',
#                       '2010-12-31',
#                        '2011-06-30',
#                         '2011-12-31', 
#                         '2012-06-30'))

keep_dates=as.Date(c('2010-09-30',
                      '2011-03-31',
                       '2011-09-30',
                        '2012-03-31'))

df=df[order(contract_award_unique_key,
            action_date_year_quarter)]

df[,two_quarter_delay:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1)&
                                action_date_year_quarter%in%keep_dates,
                              delay+lag(delay,1),NaN)]

df[,two_quarter_delay:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1)&
                                action_date_year_quarter%in%keep_dates &
                                is.na(lag(delay,1)),
                              delay,two_quarter_delay)]
```

```{r assign_variables_2, include=FALSE}

# ContractFinancing_i
df_first_reported[,contract_financing_i:=ifelse(!is.null(contract_financing_code)&
                                       !contract_financing_code%in%c("Z", ""),1,0)]
# Receives financial assistance
df_first_reported[,receives_financial_assistance:=ifelse(receives_grants=="t",1,0)]

# Competition_i
df_first_reported[,competitively_awarded_i:=ifelse(!extent_competed_code%in%c("G","B", "C"),1,0)]

df_first_reported[,initial_end_date:=period_of_performance_current_end_date]
df_first_reported[,initial_start_date:=period_of_performance_start_date]

# InitialDuration_i
df_first_reported[,initial_duration_in_days_i:=
                    as.numeric(
                    as.Date(initial_end_date)-
                    as.Date(initial_start_date))]

select_cols=c("contract_award_unique_key",
              "naics_code",
              "product_or_service_code",
              "number_of_offers_received",
              "contract_financing_i",
              "receives_financial_assistance",
              "competitively_awarded_i",
              "recipient_duns",
              "initial_end_date",
              "initial_start_date",
              "initial_duration_in_days_i",
              "base_and_all_options_value",
              "awarding_sub_agency_code")

# not necessary but speed efficient to set keys
setkey(df_first_reported[,..select_cols],
       contract_award_unique_key)
setkey(df,contract_award_unique_key)
```

```{r combine_dfs, include=FALSE}
# Combine all variables into dataframe needed for regression 
reg_df=merge(df,
             df_first_reported[,..select_cols],
             all.x = TRUE, # keep values in df, add columns of df_first_reported_cols
             by=c("contract_award_unique_key"))

reg_df[,initial_start_date:=as.Date(initial_start_date)]
reg_df[,initial_end_date:=as.Date(initial_end_date)]
reg_df[,action_date_year_quarter:=as.Date(action_date_year_quarter)]

reg_df[,winsorized_initial_duration_in_days_i:=
                    Winsorize(initial_duration_in_days_i,
                    probs=c(0.05,0.95),
                    na.rm=T)]

# InitialBudget_i

reg_df[,winsorized_initial_budget_i:=
                    Winsorize(base_and_all_options_value,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

reg_df[,number_of_offers_received_original:=number_of_offers_received]

reg_df[,number_of_offers_received:=Winsorize(number_of_offers_received_original,
                                             probs=c(0.05,0.95),
                                             na.rm=T)]

# sort by contract id and date (just to be doubly sure)
reg_df=reg_df[order(contract_award_unique_key,
            action_date_year_quarter)]

```

```{r percentage_delay,include=FALSE}

reg_df[,last_reported_duration:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1),
                                      as.numeric(lag(last_reported_end_date,1)-initial_start_date),
                                      initial_duration_in_days_i)]

# "period_of_performance_start_date" here comes from first reported info
# So it is the actual start date for a project
# get project duration as of last quarter in the denominator
reg_df[,percentage_delay:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1),
         delay/last_reported_duration,
         NaN)]

reg_df[,wins_percentage_delay:=Winsorize(100*percentage_delay,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

# time spent in the project so far/total time of the project
# if project was active in previous quarter
reg_df[,project_quarter_stage:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1),as.numeric(lag(action_date_year_quarter,1)-initial_start_date)/as.numeric(lag(last_reported_end_date,1)-initial_start_date),NaN)]

# (action_date_year_quarter-90) to get beginning of the quarter

reg_df[,wins_project_quarter_stage:=Winsorize(project_quarter_stage,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]
```

```{r relative_delay,include=FALSE}

# get project duration as of last quarter in the denominator
reg_df[,relative_delay:=ifelse(initial_duration_in_days_i>0,
                               delay/(initial_duration_in_days_i),
                               NaN)]

reg_df[,wins_relative_delay:=100*Winsorize(relative_delay,na.rm=T)]
```

```{r get_num_project_types, include=FALSE}
num_small_projects=subset(reg_df,treat_i==1)[,n_distinct(contract_award_unique_key),
                                             by='recipient_duns']
setnames(num_small_projects,'V1','num_small_projects')

num_large_projects=subset(reg_df,treat_i==0)[,n_distinct(contract_award_unique_key),
                                             by='recipient_duns']
setnames(num_large_projects,'V1','num_large_projects')

num_small_large_projects=merge(num_large_projects,
                               num_small_projects,
                               by='recipient_duns',
                               all=TRUE)
num_small_large_projects[is.na(num_small_large_projects)]=0

reg_df=merge(reg_df,
             num_small_large_projects,
             by='recipient_duns',
             all.x=TRUE)
```

```{r clean_control,include=FALSE}

##

small_contractors=unique(subset(reg_df,treat_i==1)$recipient_duns)
large_contractors=unique(subset(reg_df,treat_i==0)$recipient_duns)

reg_df[,treat_new:=case_when(treat_i==1 ~ 1,
                             treat_i==0 & !(recipient_duns%in%small_contractors)~0,
                             treat_i==0 & recipient_duns%in%small_contractors~NaN)]

# Small project & contractor does not hold any large project at any point == 1
# Small project & contractor holds a large project at any point == 0
# Large project & contractor does not hold any small project at any point == 0 [Clean control]
# Large project & contractor holds a small project at any point == NaN

reg_df[,treat_only_small:=case_when(treat_i==1 & !(recipient_duns%in%large_contractors)~1,
                                    treat_i==1 & recipient_duns%in%large_contractors~0,
                                    treat_i==0 & !(recipient_duns%in%small_contractors)~0,
                                    treat_i==0 & recipient_duns%in%small_contractors~NaN)]

# Small project & contractor holds large project at any point == 1
reg_df[,treat_small_with_large_new:=case_when(treat_i==1 & !(recipient_duns%in%large_contractors)~0,
                                    treat_i==1 & recipient_duns%in%large_contractors~1,
                                    treat_i==0 & !(recipient_duns%in%small_contractors)~0,
                                    treat_i==0 & recipient_duns%in%small_contractors~NaN)]
       
# already adjusted above, but to be super cautius!
reg_df_subset=subset(reg_df,!(treat_i==0 & recipient_duns%in%small_contractors))

reg_df_subset[,wins_percentage_delay:=Winsorize(100*percentage_delay,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

reg_df_subset[,winsorized_delay:=Winsorize(delay,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

reg_df_subset[,wins_relative_delay:=100*Winsorize(relative_delay,na.rm=T)]

# time spent in the project so far/total time of the project
# if project was active in previous quarter
reg_df_subset[,project_quarter_stage:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1),as.numeric(lag(action_date_year_quarter,1)-initial_start_date)/as.numeric(lag(last_reported_end_date,1)-initial_start_date),NaN)]

# (action_date_year_quarter-90) to get beginning of the quarter

reg_df_subset[,wins_project_quarter_stage:=Winsorize(project_quarter_stage,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

reg_df_subset[,winsorized_initial_duration_in_days_i:=
                    Winsorize(initial_duration_in_days_i,
                    probs=c(0.05,0.95),
                    na.rm=T)]

# InitialBudget_i

reg_df_subset[,winsorized_initial_budget_i:=
                    Winsorize(base_and_all_options_value,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

reg_df_subset[,number_of_offers_received:=
                    Winsorize(number_of_offers_received_original,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

reg_df_subset[,winsorized_two_quarter_delay:=Winsorize(two_quarter_delay,na.rm=T)]


```

```{r contractor_one_type,include=FALSE}
one_type_contractors=reg_df[,n_distinct(treat_i),by='recipient_duns']
one_type_contractors=unique(subset(one_type_contractors,V1==1 &
                                     !is.na(recipient_duns))$recipient_duns)

reg_df_one_type=subset(reg_df,recipient_duns%in%one_type_contractors)

reg_df_one_type[,wins_percentage_delay:=Winsorize(100*percentage_delay,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

# time spent in the project so far/total time of the project
# if project was active in previous quarter
reg_df_one_type[,project_quarter_stage:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1),as.numeric(lag(action_date_year_quarter,1)-initial_start_date)/as.numeric(lag(last_reported_end_date,1)-initial_start_date),NaN)]

# (action_date_year_quarter-90) to get beginning of the quarter

reg_df_one_type[,wins_project_quarter_stage:=Winsorize(project_quarter_stage,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

reg_df_one_type[,winsorized_initial_duration_in_days_i:=
                    Winsorize(initial_duration_in_days_i,
                    probs=c(0.05,0.95),
                    na.rm=T)]

# InitialBudget_i

reg_df_one_type[,winsorized_initial_budget_i:=
                    Winsorize(base_and_all_options_value,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]
```

```{r contractor_two_type, include=FALSE}
two_type_contractors=reg_df[,n_distinct(treat_i),by='recipient_duns']
two_type_contractors=unique(subset(two_type_contractors,V1==2 &
                                     !is.na(recipient_duns))$recipient_duns)

reg_df_two_type=subset(reg_df,recipient_duns%in%two_type_contractors)

reg_df_two_type[,wins_percentage_delay:=Winsorize(100*percentage_delay,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

# time spent in the project so far/total time of the project
# if project was active in previous quarter
reg_df_two_type[,project_quarter_stage:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1),as.numeric(lag(action_date_year_quarter,1)-initial_start_date)/as.numeric(lag(last_reported_end_date,1)-initial_start_date),NaN)]

# (action_date_year_quarter-90) to get beginning of the quarter

reg_df_two_type[,wins_project_quarter_stage:=Winsorize(project_quarter_stage,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

reg_df_two_type[,winsorized_initial_duration_in_days_i:=
                    Winsorize(initial_duration_in_days_i,
                    probs=c(0.05,0.95),
                    na.rm=T)]

# InitialBudget_i

reg_df_two_type[,winsorized_initial_budget_i:=
                    Winsorize(base_and_all_options_value,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

```

# Indirectly Treated Projects

* Checking Parallel Trends for Indirectly Treated Projects
* Sample restricted to large projects only. Formally,
* Indirectly Treated = 1 if Treat_i = 0 and Num Small Projects > 0
* Indirectly Treated = 0 if Treat_i = 0 and Num Small Projects == 0
* Indirectly Treated = NaN if Treat_i = 1

```{r delay_plot_setup_1, echo=FALSE, results='asis',warning=FALSE}
reg_df[,indirect_treat_i:=case_when(treat_i==0 & num_small_projects>0 ~ 1,
                                    treat_i==0 & num_small_projects==0 ~ 0,
                                    treat_i==1 ~ NaN)]

mean_delay=subset(reg_df,!is.na(indirect_treat_i))[!is.na(wins_percentage_delay) 
                         & action_date_year_quarter<=as.Date('2012-06-30'), 
                         mean(wins_percentage_delay),  
                         by = c('action_date_year_quarter','indirect_treat_i')]
mean_delay[,year_quarter:=format(action_date_year_quarter,"%Y-%b")]
mean_delay=mean_delay[order(action_date_year_quarter,indirect_treat_i)]

pre_qp_mean_treated=mean(subset(mean_delay,
                                action_date_year_quarter<=as.Date('2011-04-27') &
                                indirect_treat_i==1)$V1,na.rm=T)
pre_qp_mean_control=mean(subset(mean_delay,
                                action_date_year_quarter<=as.Date('2011-04-27') &
                                indirect_treat_i==0)$V1,na.rm=T)

mean_delay[,demeaned_delay:=ifelse(indirect_treat_i==1,
                                   V1-pre_qp_mean_treated,
                                   V1-pre_qp_mean_control)]

mean_delay[,business_type:=ifelse(indirect_treat_i==1,"Indirectly treated","Untreated")]
setnames(mean_delay,'V1','mean_percentage_delay')
```

## Percentage delay rate

```{r raw_percentage_delay_plot, echo=FALSE, results='asis',warning=FALSE}

ggplot(mean_delay, aes(x=year_quarter,
                       y=mean_percentage_delay, 
                       group = business_type))+
  geom_point(aes(shape=business_type),size=1.5)+
  geom_line(aes(linetype=business_type, color=business_type),alpha=0.7) +    
  scale_x_discrete(limits=mean_delay$year_quarter)+
  geom_vline(xintercept =10.2,alpha=0.8,linewidth=0.15,linetype="solid")+
  theme_minimal()+
  labs(x="Time", 
       y = "Average percentage delay rate")+
  scale_linetype_manual(name  ="",
                        values=c("solid","dashed"))+
  scale_color_manual(name  ="",
                     values=c('black','black'))+
  scale_shape_manual(name  ="",
                     values=c(16,17))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))
```

## Percentage delay rate (demeaned)

```{r demeaned_delay_plot, echo=FALSE, results='asis',warning=FALSE}
ggplot(mean_delay, aes(x=year_quarter,
                       y=demeaned_delay, 
                       group = business_type))+
  geom_point(aes(shape=business_type),size=1.5)+
  geom_line(aes(linetype=business_type, color=business_type),alpha=0.7) +    
  scale_x_discrete(limits=mean_delay$year_quarter)+
  geom_vline(xintercept =10.2,alpha=0.8,linewidth=0.15,linetype="solid")+
  theme_minimal()+
  labs(x="Time", 
       y = "Average percentage delay rate (demeaned)")+
  scale_linetype_manual(name  ="",
                        values=c("solid","dashed"))+
  scale_color_manual(name  ="",
                     values=c('black','black'))+
  scale_shape_manual(name  ="",
                     values=c(16,17))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))
```

# Treatment Categories

* Remove indirectly treated large projects.
* Treat Category = "Only small projects" if Treat_i = 1 & Num Large Projects == 0
* Treat Category = "Both small + large projects" if Treat_i = 1 & Num Large Projects > 0

```{r delay_plot_setup_2, echo=FALSE, results='asis',warning=FALSE}
reg_df[,treat_category:=case_when(treat_i==0 & num_small_projects>0 ~ "Not defined",
                                  treat_i==0 & num_small_projects==0 ~ "Only large",
                                  treat_i==1 & num_large_projects==0 ~ "Only small",
                                  treat_i==1 & num_large_projects>0 ~ "Small with large")]

mean_delay_2=subset(reg_df,treat_category!="Not defined")[!is.na(wins_percentage_delay) 
                         & action_date_year_quarter<=as.Date('2012-06-30'), 
                         mean(wins_percentage_delay),  
                         by = c('action_date_year_quarter','treat_category')]
mean_delay_2[,year_quarter:=format(action_date_year_quarter,"%Y-%b")]
mean_delay_2=mean_delay_2[order(action_date_year_quarter,treat_category)]

pre_qp_mean_only_small=mean(subset(mean_delay_2,
                                action_date_year_quarter<=as.Date('2011-04-27') &
                                treat_category=="Only small")$V1,na.rm=T)

pre_qp_mean_small_with_large=mean(subset(mean_delay_2,
                                action_date_year_quarter<=as.Date('2011-04-27') &
                                treat_category=="Small with large")$V1,na.rm=T)

pre_qp_mean_control=mean(subset(mean_delay_2,
                                action_date_year_quarter<=as.Date('2011-04-27') &
                                treat_category=="Only large")$V1,na.rm=T)

mean_delay_2[,demeaned_delay:=case_when(treat_category=="Only small"~V1-pre_qp_mean_only_small,
                                        treat_category=="Small with large"~V1-pre_qp_mean_small_with_large,
                                        treat_category=="Only large"~V1-pre_qp_mean_control)]

setnames(mean_delay_2,'V1','mean_percentage_delay')
```

```{r delay_plot_treat_groups, echo=FALSE, results='asis',warning=FALSE}
ggplot(mean_delay_2, aes(x=year_quarter,
                       y=mean_percentage_delay, 
                       group = treat_category))+
  geom_point(aes(shape=treat_category),size=1.5)+
  geom_line(aes(linetype=treat_category, color=treat_category),alpha=0.7) +    
  scale_x_discrete(limits=mean_delay$year_quarter)+
  geom_vline(xintercept =10.2,alpha=0.8,linewidth=0.15,linetype="solid")+
  theme_minimal()+
  labs(x="Time", 
       y = "Average percentage delay rate")+
  scale_linetype_manual(name  ="",
                        values=c("solid","dashed","dotted"))+
  scale_color_manual(name  ="",
                     values=c('black','black','black'))+
  scale_shape_manual(name  ="",
                     values=c(16,17,20))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))
```

## De-meaned perentage delay rate

```{r demeaned_delay_plot_treat_groups, echo=FALSE, results='asis',warning=FALSE}
ggplot(mean_delay_2, aes(x=year_quarter,
                       y=demeaned_delay, 
                       group = treat_category))+
  geom_point(aes(shape=treat_category),size=1.5)+
  geom_line(aes(linetype=treat_category, color=treat_category),alpha=0.7) +    
  scale_x_discrete(limits=mean_delay$year_quarter)+
  geom_vline(xintercept =10.2,alpha=0.8,linewidth=0.15,linetype="solid")+
  theme_minimal()+
  labs(x="Time", 
       y = "Average percentage delay rate (demeaned)")+
  scale_linetype_manual(name  ="",
                        values=c("solid","dashed","dotted"))+
  scale_color_manual(name  ="",
                     values=c('black','black','black'))+
  scale_shape_manual(name  ="",
                     values=c(16,17,20))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))
```