---
title: "Budget Overruns: First Implementation of QuickPay (2009-2012)"
date: " `r format(Sys.time(), '%b %d, %Y')`"
output: 
  pdf_document :
    keep_tex: true
    number_sections: true
header-includes:
 \usepackage{booktabs,longtable,dcolumn}
 \usepackage{multirow,array}
 \usepackage{wrapfig,float}
 \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages,warning=FALSE,message=FALSE,include=FALSE}
library(openxlsx)
library(tidyverse)
library(dplyr)
library(pryr)
library(lfe) # linear fixed effects 
library(DescTools) 
library(zoo) # for year quarter
library(stargazer)
library(broom)
library(data.table)
library(scales)
``` 

```{r paths, include=FALSE}
tables_folder='~/Desktop/Research/QuickPay/paper/Tables/robustness'
directory='~/Dropbox/data_quickpay/qp_data/'
```

```{r read_data, include=FALSE}
# Keep only projects whose start dates match with API one
projects_to_keep=fread(paste0(directory,'projects_to_keep.csv'))

# read quarterly resampled data
df=fread(paste0(directory,'resampled_qp_data/qp_resampled_data_fy10_to_fy12_with_zero_obs.csv'))
# specify date columns
date_cols=c("action_date_year_quarter","last_reported_start_date","last_reported_end_date")
df[,(date_cols):= lapply(.SD, as.Date), .SDcols = date_cols]

# restrict to quarter ending June 30, 2012
df=subset(df,as.Date(action_date_year_quarter)<max(as.Date('2012-07-01'))&
             contract_award_unique_key%in%projects_to_keep$contract_award_unique_key)
# data is truncated at July 1, 2012 -- 
# so quarter ending Sept 30, 2012 will only have values as of July 1, 2012

df_first_reported=fread(paste0(directory,'qp_data_first_reported.csv'))
# contains time-invariant contract characteristics -- info when contract first appeared in the data
```


```{r assign_variables_1, include=FALSE}
# Assign variables: overrun, Winsorized overrun, Post_t, Treat_i

# sort by contract id and date 
df=df[order(contract_award_unique_key,
            action_date_year_quarter)]

# determine quarter-to-quarter overrun
df[,overrun:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1), 
                  last_reported_budget-lag(last_reported_budget,1),NaN)]

# winsorize quarter-to-quarter overrun
df[,winsorized_overrun:=Winsorize(overrun,na.rm=TRUE)]

#Post_t: A dummy that period t is post-treatment
df[,post_t:=ifelse(action_date_year_quarter>as.Date("2011-04-27"),1,0)]
# quickpay implemented on 27 April 2011. So all quarters starting 30 June 2011 will be in post-period

#Treat_i: A dummy that contract i is in the treatment group
df[,treat_i:=ifelse(business_type=="S",1,0)]
# quickpay was implemented for small business contracts
```

```{r assign_variables_2, include=FALSE}
# Assign variables: ContractFinancing_i, Competition_i, PerformanceBased_i, Financial_Aid_i
df_first_reported[,contract_financing_i:=ifelse(!is.null(contract_financing_code)&
                                       !contract_financing_code%in%c("Z", ""),1,0)]
#### 
# unique(df_first_reported[,c('extent_competed','extent_competed_code')])
# df_first_reported[,competitively_awarded_i:=ifelse(!is.null(extent_competed_code)&
#                                           !extent_competed_code%in%c("","G","B", "C"),1,0)]

# E: FOLLOW ON TO COMPETED ACTION
df_first_reported[,competitively_awarded_i:=ifelse(!is.null(extent_competed_code)&
                                          !extent_competed_code%in%c("","G","B", "C","E"),1,0)]
#### 
df_first_reported[,performance_based_contract_i:=ifelse(performance_based_service_acquisition_code=='Y',1,0)]

df_first_reported[,performance_based_contract_i:=ifelse(performance_based_service_acquisition_code=='X',NaN,performance_based_contract_i)]

#### 
df_first_reported[,receives_financial_aid_i:=ifelse(receives_grants=='t'|
                                           c8a_program_participant=='t',1,0)]
#### 
df_first_reported[,receives_contracts_and_financial_aid_i:=ifelse(receives_contracts_and_grants=='t'|
                                                         receives_grants=='t'|
                                                         c8a_program_participant=='t',1,0)]

df_first_reported[,winsorized_initial_duration_in_days_i:=Winsorize(as.numeric(
                               as.Date(period_of_performance_current_end_date)-
                               as.Date(period_of_performance_start_date)),na.rm=T)]

df_first_reported[,winsorized_initial_budget_i:=Winsorize(base_and_all_options_value,na.rm=T)]

df_first_reported[,initial_budget_i:=base_and_all_options_value]

select_cols=c("contract_award_unique_key",
              "recipient_duns",
              "naics_code",
              "product_or_service_code",
              "number_of_offers_received",
              "contract_financing_i",
              "competitively_awarded_i",
              "performance_based_contract_i",
              "receives_financial_aid_i",
              "receives_contracts_and_financial_aid_i",
              "winsorized_initial_duration_in_days_i",
              "initial_budget_i",
              "winsorized_initial_budget_i")

df_first_reported_cols=df_first_reported[,..select_cols]
# not necessary but speed efficient to set keys
setkey(df_first_reported_cols,contract_award_unique_key)
setkey(df,contract_award_unique_key)
```

```{r combine_dfs, include=FALSE}
# Combine all variables into dataframe needed for regression 
reg_df=merge(df,
             df_first_reported_cols,
             all.x = TRUE, # keep values in df, add columns of df_first_reported_cols
             by=c("contract_award_unique_key"))

# assign number of quarters since project started: "project age" in some sense
setorder(reg_df,contract_award_unique_key,action_date_year_quarter)[, 
           project_quarter_age := rowid(contract_award_unique_key)]
reg_df[,project_quarter_tercile:=as.factor(ntile(project_quarter_age,3))]
# Project age is a highly skewed variable
# Including it as fixed effects doesn't work because projects in treatment and control are not always in same "tercile" while controling for everything else. 

```

```{r stargazer_format, include=FALSE}
# Code to extract only the inner part (nested within tabular) of table from stargazer
# We will use this along with threeparttable in latex later 
# Code adapted from Patrick Baylis's blog on the topic:
# https://www.patrickbaylis.com/blog/2019-11-25-r-reg-tables/
make_tex_pieces <- function(stargazer_output) {
  # Split up into header, footer, and inner
  idx0 <- grep("begin{tabular}", stargazer_output, fixed = T) # Start of \begin{tabular}
  idx1 <- grep("end{tabular}", stargazer_output, fixed = T) # End of \begin{tabular}
  idx2<-grep("Adjusted",stargazer_output,fixed=T)
  
  tex_header <- c(stargazer_output[idx0],"\\toprule")
  tex_footer <- c("\\bottomrule", stargazer_output[idx1])
  tex_inner<-c(stargazer_output[(idx0+3):idx2])
  
  # Remove [-1.8ex] and replace \hline with \midrule
  tex_inner <- gsub("\\\\[-[\\.0-9]+ex]", "", tex_inner)
  
  tex_inner <- gsub("\\hline ", "\\midrule", tex_inner)
  # Return these as a 3 element list so that the user can insert header rows (column labels)
  # and footer rows (summary statistics, fixed effects)
  # list(header = tex_header, inner = tex_inner, footer = tex_footer)
  c(tex_header,tex_inner,tex_footer)
}
```
# Note

- Sample restricted to projects for which start dates matches the one in API
   - This is done by using first reported "action_date" and "date_signed" 
- Below is the definition of `base_and_all_options_value` from the data dictionary:
  - The change (from this transaction only) to the potential contract value (i.e., the base contract and any exercised or unexercised options).
- This means that every observation in raw data shows incremental change from previous budget. So some of the values can be zero. 
- We, therefore, need to calculate the new budget at each point in time (by adding all previous values). We did this in the resampling step, but mentioning here for reference.
- This is different from calculation of delays, where `period_of_performance_current_end_date` indicated the new deadline of the project.

# Budget Overrun over Time

```{r plot, echo=FALSE, results='asis'}
mean_overrun=df[!is.na(winsorized_overrun) & action_date_year_quarter<=as.Date('2012-06-30'), 
              mean(winsorized_overrun),  
              by = c('action_date_year_quarter','business_type')]
mean_overrun[,year_quarter:=format(action_date_year_quarter,"%Y-%b")]
mean_overrun=mean_overrun[order(action_date_year_quarter,business_type)]

ggplot(mean_overrun, aes(x=year_quarter,
               y=V1, 
               group = business_type, 
               shape=business_type, 
               linetype=business_type))+
    geom_line() +    
    scale_x_discrete(limits=mean_overrun$year_quarter)+
    geom_point(size=3)+
    labs(x="Year-Quarter", y = "Average overrun rate per quarter")+  
    annotate("text", label = "QuickPay\n implemented", x = 8, y = 50,color="dimgrey")+
    geom_vline(xintercept = 10.2, linetype="solid", 
                color = "gray", size=1.5)+
    scale_shape_discrete(name  ="Business Size",
                          breaks=c("O", "S"),
                          labels=c("Large", "Small"))+
    scale_linetype_discrete(name="Business Size",
                          breaks=c("O", "S"),
                          labels=c("Large", "Small"))+
    theme(axis.text.x = element_text(angle = 90),
    axis.line = element_line(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    legend.text = element_text(size=12))
```

## Normalized Overrun

```{r normalized_plot,echo=FALSE,results='asis'}

small_baseline=subset(mean_overrun,business_type=="S" & year_quarter=="2010-Mar")$V1
large_baseline=subset(mean_overrun,business_type=="O" & year_quarter=="2010-Mar")$V1

mean_overrun[,V2:=ifelse(business_type=="S",V1*100/small_baseline,V1*100/large_baseline)]

ggplot(mean_overrun, aes(x=year_quarter,
               y=V2, 
               group = business_type, 
               shape=business_type, 
               linetype=business_type))+
    geom_line() +    
    scale_x_discrete(limits=mean_overrun$year_quarter)+
    geom_point(size=3)+
    labs(x="Year-Quarter", y = "Average overrun rate per quarter")+  
    annotate("text", label = "QuickPay\n implemented", x = 8, y = 180,color="dimgrey")+
    geom_vline(xintercept = 10.2, linetype="solid", 
                color = "gray", size=1.5)+
    scale_shape_discrete(name  ="Business Size",
                          breaks=c("O", "S"),
                          labels=c("Large", "Small"))+
    scale_linetype_discrete(name="Business Size",
                          breaks=c("O", "S"),
                          labels=c("Large", "Small"))+
    theme(axis.text.x = element_text(angle = 90),
    axis.line = element_line(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    legend.text = element_text(size=12))
```

# Notation 

* Project $i$, Year-Quarter $t$
* $X_i$ denotes project level controls: initial duration, initial budget, number of offers received
* $\mu_t,\theta_{firm},\lambda_{task}$: Year-Quarter, Firm, and Product/Service code Fixed effects
* All continuous variables are winsorized at the 5\% level
$$ Treat_i = \begin{cases} 1, \text{ if project } i \text{ is a small business}\\
0, \text{ otherwise} \end{cases}$$
$$ Post_t = \begin{cases} 1, \text{ if year-quarter } t > \text{ April 27, 2011}\\
0, \text{ otherwise} \end{cases}$$

# Baseline Regressions

$$ Overrun_{it} = \alpha+\beta_0 Treat_i + \beta_1 Post_t + \beta_2 (Treat_i \times Post_t) + \epsilon_{it}$$ 

$$ \begin{aligned} Overrun_{it} &=& \alpha+\beta_0 Treat_i + \beta_1 Post_t + \beta_2 (Treat_i \times Post_t)\\
&+&  X_i + (Post_t \times X_i) + \mu_t + \theta_{firm} + \lambda_{task}+ \epsilon_{it}
\end{aligned}$$

```{r baseline_regressions, echo=FALSE, results='asis'}
# Baseline Regressions 
baseline_reg=felm(winsorized_overrun~treat_i+
                     post_t:treat_i+
                     post_t|
                    0| # no fixed effects
                    0| # no IV
                    contract_award_unique_key, # clustered at project level
                  data=reg_df, 
                  exactDOF = TRUE, 
                  cmethod = "reghdfe")

# time fixed effects also included in the following specs
controls_and_no_fe=felm(winsorized_overrun~treat_i+
                           post_t:treat_i+
                           post_t+
                           project_quarter_tercile+
                            winsorized_initial_duration_in_days_i+
                            winsorized_initial_budget_i+
                            number_of_offers_received+
                            post_t:winsorized_initial_duration_in_days_i+
                            post_t:winsorized_initial_budget_i+
                            post_t:number_of_offers_received|
                            0|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

# time fixed effects also included in the following specs
controls_and_time_fe=felm(winsorized_overrun~treat_i+
                             post_t:treat_i+
                           project_quarter_tercile+
                            winsorized_initial_duration_in_days_i+
                            winsorized_initial_budget_i+
                            number_of_offers_received+
                            post_t:winsorized_initial_duration_in_days_i+
                            post_t:winsorized_initial_budget_i+
                            post_t:number_of_offers_received|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

controls_time_task_fe=felm(winsorized_overrun~treat_i+
                              post_t:treat_i+
                           project_quarter_tercile+
                            winsorized_initial_duration_in_days_i+
                            winsorized_initial_budget_i+
                            number_of_offers_received+
                            post_t:winsorized_initial_duration_in_days_i+
                            post_t:winsorized_initial_budget_i+
                            post_t:number_of_offers_received|
                            product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

controls_and_all_fe=felm(winsorized_overrun~treat_i+
                            post_t:treat_i+
                           project_quarter_tercile+
                            winsorized_initial_duration_in_days_i+
                            winsorized_initial_budget_i+
                            number_of_offers_received+
                            post_t:winsorized_initial_duration_in_days_i+
                            post_t:winsorized_initial_budget_i+
                            post_t:number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

base_table=stargazer(baseline_reg,
          controls_and_no_fe,
          controls_and_time_fe,
          controls_time_task_fe,
          controls_and_all_fe,
          title = "Quickpay 2009-2011",
          dep.var.labels="$Overrun_{it}$ (in days)",
          dep.var.caption = "",
          covariate.labels = c("$Treat_i$","$Post_t$","$Treat_i \\times Post_t$","Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          digits=2,
          digits.extra=2,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(c("Duration, Budget, Bids","No",rep("Yes",4)),
                           c("$Post_t \\times$  (Duration, Budget, Bids)","No",rep("Yes",4)),
                           c("Project Age Tercile","No",rep("Yes",4)),
                           c("Year-Quarter Fixed Effects",rep("No",2),rep("Yes",3)),
                           c("Task Fixed Effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:winsorized_initial_budget_i',
                   'post_t:number_of_offers_received',
                   'project_quarter_tercile'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level."),
          header=F)

#base_table_cost_overruns.tex
```

# Percentage Overrun

$$ PercentOverrun_{it} = \beta_0 + \beta_1 Treat_i + \beta_2 Post_t + \beta_3 (Treat_i \times Post_t) + e_{it}$$ 

$$ \begin{aligned} PercentOverrun_{it} &=& \alpha+\beta_0 Treat_i + \beta_1 Post_t + \beta_2 (Treat_i \times Post_t)\\
&+&  X_i + (Post_t \times X_i) + \mu_t + \theta_{firm} + \lambda_{task}+ \epsilon_{it}
\end{aligned}$$

```{r percentage_overrun,include=FALSE}
reg_df[,percentage_overrun:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1) &
                                     lag(last_reported_budget,1)>0,
         overrun/lag(last_reported_budget,1),
         NaN)]
reg_df[,wins_percentage_overrun:=100*Winsorize(percentage_overrun,na.rm=T)]
```


## Percentage Overrun over time

* Sample restricted to projects with modification zero when they first appeared in our sample.
* $PercentOverrun_{it}=100 \times Overrun_{it}/Budget_{i,t-1}$

```{r plot_pc_overrun, echo=FALSE, results='asis'}
mean_overrun=reg_df[!is.na(wins_percentage_overrun) 
                  & action_date_year_quarter<=as.Date('2012-06-30'), 
              mean(wins_percentage_overrun),  
              by = c('action_date_year_quarter','business_type')]
mean_overrun[,year_quarter:=format(action_date_year_quarter,"%Y-%b")]
mean_overrun=mean_overrun[order(action_date_year_quarter,business_type)]
ggplot(mean_overrun, aes(x=year_quarter,
               y=V1, 
               group = business_type, 
               shape=business_type, 
               linetype=business_type))+
    geom_line() +    
    scale_x_discrete(limits=mean_overrun$year_quarter)+
    geom_point(size=3)+
    labs(x="Year-Quarter", y = "Average overrun rate per quarter")+  
    annotate("text", label = "QuickPay\n implemented", x = 8, y = 0.45,color="dimgrey")+
    geom_vline(xintercept = 10.2, linetype="solid", 
                color = "gray", size=1.5)+
    scale_shape_discrete(name  ="Business Size",
                          breaks=c("O", "S"),
                          labels=c("Large", "Small"))+
    scale_linetype_discrete(name="Business Size",
                          breaks=c("O", "S"),
                          labels=c("Large", "Small"))+
    theme(axis.text.x = element_text(angle = 90),
    axis.line = element_line(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    legend.text = element_text(size=12))
```

### Normalized Overrun

```{r normalized_pc_plot,echo=FALSE, results='asis'}
large_baseline=subset(mean_overrun,year_quarter=='2010-Mar' & business_type=="O")$V1
small_baseline=subset(mean_overrun,year_quarter=='2010-Mar' & business_type=="S")$V1
mean_overrun[,V2:=ifelse(business_type=="S",V1*100/small_baseline,V1*100/large_baseline)]
ggplot(mean_overrun, aes(x=year_quarter,
               y=V2, 
               group = business_type, 
               shape=business_type, 
               linetype=business_type))+
    geom_line() +    
    scale_x_discrete(limits=mean_overrun$year_quarter)+
    geom_point(size=3)+
    labs(x="Year-Quarter", y = "Average overrun rate per quarter \n (normalized by overrun in 2010-Mar) ")+  
    annotate("text", label = "QuickPay\n implemented", x = 8, y = 150,color="dimgrey")+
    geom_vline(xintercept = 10.2, linetype="solid", 
                color = "gray", size=1.5)+
    scale_shape_discrete(name  ="Business Size",
                          breaks=c("O", "S"),
                          labels=c("Large", "Small"))+
    scale_linetype_discrete(name="Business Size",
                          breaks=c("O", "S"),
                          labels=c("Large", "Small"))+
    theme(axis.text.x = element_text(angle = 90),
    axis.line = element_line(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    legend.text = element_text(size=12))
```

```{r pc_regressions, echo=FALSE, results='asis'}
# Baseline Regressions 
baseline_reg=felm(wins_percentage_overrun~treat_i+
                     post_t:treat_i+
                     post_t|
                    0| # no fixed effects
                    0| # no IV
                    contract_award_unique_key, # clustered at project level
                  data=reg_df, 
                  exactDOF = TRUE, 
                  cmethod = "reghdfe")

# time fixed effects also included in the following specs
controls_and_no_fe=felm(wins_percentage_overrun~treat_i+
                           post_t:treat_i+
                           post_t+
                           project_quarter_tercile+
                            winsorized_initial_duration_in_days_i+
                            winsorized_initial_budget_i+
                            number_of_offers_received+
                            post_t:winsorized_initial_duration_in_days_i+
                            post_t:winsorized_initial_budget_i+
                            post_t:number_of_offers_received|
                            0|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
# time fixed effects also included in the following specs
controls_and_time_fe=felm(wins_percentage_overrun~treat_i+
                             post_t:treat_i+
                           project_quarter_tercile+
                            winsorized_initial_duration_in_days_i+
                            winsorized_initial_budget_i+
                            number_of_offers_received+
                            post_t:winsorized_initial_duration_in_days_i+
                            post_t:winsorized_initial_budget_i+
                            post_t:number_of_offers_received|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_time_task_fe=felm(wins_percentage_overrun~treat_i+
                              post_t:treat_i+
                           project_quarter_tercile+
                            winsorized_initial_duration_in_days_i+
                            winsorized_initial_budget_i+
                            number_of_offers_received+
                            post_t:winsorized_initial_duration_in_days_i+
                            post_t:winsorized_initial_budget_i+
                            post_t:number_of_offers_received|
                            product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_all_fe=felm(wins_percentage_overrun~treat_i+
                            post_t:treat_i+
                           project_quarter_tercile+
                            winsorized_initial_duration_in_days_i+
                            winsorized_initial_budget_i+
                            number_of_offers_received+
                            post_t:winsorized_initial_duration_in_days_i+
                            post_t:winsorized_initial_budget_i+
                            post_t:number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
base_table<-stargazer(baseline_reg,
          controls_and_no_fe,
          controls_and_time_fe,
          controls_time_task_fe,
          controls_and_all_fe,
          title = "Effect of QuickPay on project overrun rates",
          dep.var.labels="$PercentOverrun_{it}$",
          dep.var.caption = "",
          covariate.labels = c("$Treat_i$","$Post_t$","$Treat_i \\times Post_t$","Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          digits=2,
          digits.extra=2,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(c("Duration, Budget, Bids","No",rep("Yes",4)),
                           c("$Post_t \\times$  (Duration, Budget, Bids)","No",rep("Yes",4)),
                           c("Project age","No",rep("Yes",4)),
                           c("Year-Quarter fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:winsorized_initial_budget_i',
                   'post_t:number_of_offers_received',
                   'project_quarter_tercile'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level."),
          header=F)

base_table_tex=make_tex_pieces(base_table)
# Write to file
write(base_table_tex,
      paste0(tables_folder,"/base_table_cost_overruns.tex"))
```

# Relative Overrun

```{r relative_overrun,include=FALSE}
reg_df[,relative_overrun:=overrun/(1+initial_budget_i)]
reg_df[,wins_relative_overrun:=Winsorize(100*relative_overrun,na.rm=T)]
```

## Relative overruns over time

* Sample restricted to projects with modification zero when they first appeared in our sample.

* $RelativeOverrun_{it} = 100 \times RelativeOverrun_{it}/IntialBudget_i$

```{r plot_relative_overrun, echo=FALSE, results='asis'}
mean_overrun=reg_df[!is.na(wins_relative_overrun) 
                  & action_date_year_quarter<=as.Date('2012-06-30'), 
              mean(wins_relative_overrun),  
              by = c('action_date_year_quarter','business_type')]
mean_overrun[,year_quarter:=format(action_date_year_quarter,"%Y-%b")]
mean_overrun=mean_overrun[order(action_date_year_quarter,business_type)]
ggplot(mean_overrun, aes(x=year_quarter,
               y=V1, 
               group = business_type, 
               shape=business_type, 
               linetype=business_type))+
    geom_line() +    
    scale_x_discrete(limits=mean_overrun$year_quarter)+
    geom_point(size=3)+
    labs(x="Year-Quarter", y = "Average overrun rate per quarter  ")+  
    annotate("text", label = "QuickPay\n implemented", x = 8, y = 40,color="dimgrey")+
    geom_vline(xintercept = 10.2, linetype="solid", 
                color = "gray", size=1.5)+
    scale_shape_discrete(name  ="Business Size",
                          breaks=c("O", "S"),
                          labels=c("Large", "Small"))+
    scale_linetype_discrete(name="Business Size",
                          breaks=c("O", "S"),
                          labels=c("Large", "Small"))+
    theme(axis.text.x = element_text(angle = 90),
    axis.line = element_line(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    legend.text = element_text(size=12))
# ggsave(path=figures_folder,
#        width = 8,
#        height = 4,
#        filename = "trends_figure.png")
```

### Normalized overrun

```{r normalized_relative_plot,echo=FALSE, results='asis'}
large_baseline=subset(mean_overrun,year_quarter=='2010-Mar' & business_type=="O")$V1
small_baseline=subset(mean_overrun,year_quarter=='2010-Mar' & business_type=="S")$V1
mean_overrun[,V2:=ifelse(business_type=="S",V1*100/small_baseline,V1*100/large_baseline)]
ggplot(mean_overrun, aes(x=year_quarter,
               y=V2, 
               group = business_type, 
               shape=business_type, 
               linetype=business_type))+
    geom_line() +    
    scale_x_discrete(limits=mean_overrun$year_quarter)+
    geom_point(size=3)+
    labs(x="Year-Quarter", y = "Average overrun rate per quarter 
                                \n (normalized by overrun in 2010-Mar) ")+  
    annotate("text", label = "QuickPay\n implemented", x = 8, y = 150,color="dimgrey")+
    geom_vline(xintercept = 10.2, linetype="solid", 
                color = "gray", size=1.5)+
    scale_shape_discrete(name  ="Business Size",
                          breaks=c("O", "S"),
                          labels=c("Large", "Small"))+
    scale_linetype_discrete(name="Business Size",
                          breaks=c("O", "S"),
                          labels=c("Large", "Small"))+
    theme(axis.text.x = element_text(angle = 90),
    axis.line = element_line(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    legend.text = element_text(size=12))
```

```{r relative_regressions, echo=FALSE, results='asis'}
# Baseline Regressions 
baseline_reg=felm(wins_relative_overrun~treat_i+
                     post_t:treat_i+
                     post_t|
                    0| # no fixed effects
                    0| # no IV
                    contract_award_unique_key, # clustered at project level
                  data=reg_df, 
                  exactDOF = TRUE, 
                  cmethod = "reghdfe")
# time fixed effects also included in the following specs
controls_and_no_fe=felm(wins_relative_overrun~treat_i+
                           post_t:treat_i+
                           post_t+
                           project_quarter_tercile+
                            winsorized_initial_duration_in_days_i+
                            number_of_offers_received+
                            post_t:winsorized_initial_duration_in_days_i+
                            post_t:number_of_offers_received|
                            0|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
# time fixed effects also included in the following specs
controls_and_time_fe=felm(wins_relative_overrun~treat_i+
                             post_t:treat_i+
                           project_quarter_tercile+
                            winsorized_initial_duration_in_days_i+
                            number_of_offers_received+
                            post_t:winsorized_initial_duration_in_days_i+
                            post_t:number_of_offers_received|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_time_task_fe=felm(wins_relative_overrun~treat_i+
                              post_t:treat_i+
                           project_quarter_tercile+
                            winsorized_initial_duration_in_days_i+
                            number_of_offers_received+
                            post_t:winsorized_initial_duration_in_days_i+
                            post_t:number_of_offers_received|
                            product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_all_fe=felm(wins_relative_overrun~treat_i+
                            post_t:treat_i+
                           project_quarter_tercile+
                            winsorized_initial_duration_in_days_i+
                            number_of_offers_received+
                            post_t:winsorized_initial_duration_in_days_i+
                            post_t:number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
base_table<-stargazer(baseline_reg,
          controls_and_no_fe,
          controls_and_time_fe,
          controls_time_task_fe,
          controls_and_all_fe,
          title = "Effect of QuickPay on project overrun rates",
          dep.var.labels="$RelativeOverrun_{it}$",
          dep.var.caption = "",
          covariate.labels = c("$Treat_i$","$Post_t$","$Treat_i \\times Post_t$","Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          digits=2,
          digits.extra=2,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(c("Duration, Bids","No",rep("Yes",4)),
                           c("$Post_t \\times$  (Duration, Bids)","No",rep("Yes",4)),
                           c("Project age","No",rep("Yes",4)),
                           c("Year-Quarter fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:number_of_offers_received',
                   'project_quarter_tercile'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level."),
          header=F)
# base_table_tex=make_tex_pieces(base_table)
# # Write to file 
# write(base_table_tex, 
#       paste0(tables_folder,"/base_table.tex"))
```

