---
title: "Percentage Delay Rate (with Time Independent Clean Control): QuickPay (2009-2012)"
date: " `r format(Sys.time(), '%b %d, %Y')`"
output: 
  pdf_document:
    keep_tex: true
    number_sections: true
header-includes:
 \usepackage{booktabs,longtable,dcolumn}
 \usepackage{multirow,array}
 \usepackage{wrapfig,float}
 \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

* Sample consists of a "time independent" clean control group
   * This means we keep all small projects.
   * We keep only those large projects that don't have a concurrent small project in *any* quarter.
   
* When we analyze congestion effect, we restrict to only one type of contractor. That is, contractors that hold only small project or only large project in the sample horizon.

# Setup

```{r packages,warning=FALSE,message=FALSE,include=FALSE}
library(openxlsx)
library(tidyverse)
library(dplyr)
library(pryr)
library(lfe) # linear fixed effects 
library(DescTools) 
library(zoo) # for year quarter
library(stargazer)
library(broom)
library(fixest)
library(data.table)
library(scales)
library(coefplot)
library(MatchIt)
library(pBrackets)
library(grid)
```

```{r set_path_for_exporting, include=FALSE}
tables_folder='~/Desktop/Research/QuickPay/paper/Tables/percentage_delay_rate'
figures_folder='~/Desktop/Research/QuickPay/paper/Figures'
data_folder='~/Dropbox/data_quickpay/qp_data/'
```

```{r read_data, include=FALSE}
# Keep only projects whose start dates match with API one
projects_to_keep=fread(paste0(data_folder,'projects_to_keep.csv'))

# read quarterly resampled data
df=fread(paste0(data_folder,'resampled_qp_data/qp_resampled_data_fy10_to_fy12_with_zero_obs.csv'))
# specify date columns
date_cols=c("action_date_year_quarter","last_reported_start_date","last_reported_end_date")
df[,(date_cols):= lapply(.SD, as.Date), .SDcols = date_cols]

# restrict to quarter ending June 30, 2012
df=subset(df,as.Date(action_date_year_quarter)<as.Date('2012-07-01')&
          contract_award_unique_key%in%projects_to_keep$contract_award_unique_key)

# data is truncated at July 1, 2012 -- 
# so quarter ending Sept 30, 2012 will only have values as of July 1, 2012

df_first_reported=fread(paste0(data_folder,'qp_data_first_reported.csv'))
# contains time-invariant contract characteristics -- info when contract first appeared in the data

```

```{r assign_variables_1, include=FALSE}
# Assign variables: Delay, Winsorized Delay, Post_t, Treat_i

# some projects have action dates beyond project end date 
# some could indicate projects that ended in the beginning of a quarter -- so taking 90 days difference
# dropping these -- likely admin/documentation changes

df[,diff_end_date_and_action_date:=as.numeric(last_reported_end_date-action_date_year_quarter)]
# to ensure project ended sometime this quarter
df=subset(df,diff_end_date_and_action_date>-90)


# AD: 2015-06-30; End Date: 2015-03-31

# sort by contract id and date 
df=df[order(contract_award_unique_key,
            action_date_year_quarter)]

# determine quarter-to-quarter delay
df[,delay:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1), 
                  last_reported_end_date-lag(last_reported_end_date,1),NaN)]

# winsorize quarter-to-quarter delay
df[,winsorized_delay:=Winsorize(delay,
                                probs=c(0.05,0.95),
                                na.rm=TRUE)]

#Post_t: A dummy that period t is post-treatment
df[,post_t:=ifelse(action_date_year_quarter>as.Date("2011-04-27"),1,0)]
# quickpay implemented on 27 April 2011. So all quarters starting 30 June 2011 will be in post-period

#Treat_i: A dummy that contract i is in the treatment group
df[,treat_i:=ifelse(business_type=="S",1,0)]
# quickpay was implemented for small business contracts

```

```{r assign_variables_2, include=FALSE}

# ContractFinancing_i
df_first_reported[,contract_financing_i:=ifelse(!is.null(contract_financing_code)&
                                       !contract_financing_code%in%c("Z", ""),1,0)]
# Receives financial assistance
df_first_reported[,receives_financial_assistance:=ifelse(receives_grants=="t",1,0)]

# Competition_i
df_first_reported[,competitively_awarded_i:=ifelse(!extent_competed_code%in%c("G","B", "C"),1,0)]

df_first_reported[,initial_end_date:=period_of_performance_current_end_date]
df_first_reported[,initial_start_date:=period_of_performance_start_date]

# InitialDuration_i
df_first_reported[,initial_duration_in_days_i:=
                    as.numeric(
                    as.Date(initial_end_date)-
                    as.Date(initial_start_date))]

select_cols=c("contract_award_unique_key",
              "naics_code",
              "product_or_service_code",
              "number_of_offers_received",
              "contract_financing_i",
              "receives_financial_assistance",
              "competitively_awarded_i",
              "recipient_duns",
              "initial_end_date",
              "initial_start_date",
              "initial_duration_in_days_i",
              "base_and_all_options_value",
              "awarding_sub_agency_code")

# not necessary but speed efficient to set keys
setkey(df_first_reported[,..select_cols],
       contract_award_unique_key)
setkey(df,contract_award_unique_key)
```

```{r combine_dfs, include=FALSE}
# Combine all variables into dataframe needed for regression 
reg_df=merge(df,
             df_first_reported[,..select_cols],
             all.x = TRUE, # keep values in df, add columns of df_first_reported_cols
             by=c("contract_award_unique_key"))

reg_df[,initial_start_date:=as.Date(initial_start_date)]
reg_df[,initial_end_date:=as.Date(initial_end_date)]
reg_df[,action_date_year_quarter:=as.Date(action_date_year_quarter)]

reg_df[,winsorized_initial_duration_in_days_i:=
                    Winsorize(initial_duration_in_days_i,
                    probs=c(0.05,0.95),
                    na.rm=T)]

# InitialBudget_i

reg_df[,winsorized_initial_budget_i:=
                    Winsorize(base_and_all_options_value,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

# sort by contract id and date (just to be doubly sure)
reg_df=reg_df[order(contract_award_unique_key,
            action_date_year_quarter)]

```

```{r percentage_delay,include=FALSE}

reg_df[,last_reported_duration:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1),
                                      as.numeric(lag(last_reported_end_date,1)-initial_start_date),
                                      initial_duration_in_days_i)]

# "period_of_performance_start_date" here comes from first reported info
# So it is the actual start date for a project
# get project duration as of last quarter in the denominator
reg_df[,percentage_delay:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1),
         delay/last_reported_duration,
         NaN)]

reg_df[,wins_percentage_delay:=Winsorize(100*percentage_delay,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

# time spent in the project so far/total time of the project
# if project was active in previous quarter
reg_df[,project_quarter_stage:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1),as.numeric(lag(action_date_year_quarter,1)-initial_start_date)/as.numeric(lag(last_reported_end_date,1)-initial_start_date),NaN)]

# (action_date_year_quarter-90) to get beginning of the quarter

reg_df[,wins_project_quarter_stage:=Winsorize(project_quarter_stage,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]
```

```{r clean_control,include=FALSE}

##

small_contractors=unique(subset(reg_df,treat_i==1)$recipient_duns)
large_contractors=unique(subset(reg_df,treat_i==0)$recipient_duns)

## Contractor-Quarter definitions

# contractors holding large projects in a given quarter
contractors_holding_large_projects=subset(reg_df,treat_i==0)[,unique(recipient_duns),
                                                             by='action_date_year_quarter']
contractors_holding_large_projects[,contractor_quarter_large_projects:=paste(V1,action_date_year_quarter,sep='_')]
contractors_holding_large_projects=unique(contractors_holding_large_projects$contractor_quarter_large_projects)

# contractors holding small projects in a given quarter
contractors_holding_small_projects=subset(reg_df,treat_i==1)[,unique(recipient_duns),by='action_date_year_quarter']
contractors_holding_small_projects[,contractor_quarter_small_projects:=paste(V1,action_date_year_quarter,sep='_')]
contractors_holding_small_projects=unique(contractors_holding_small_projects$contractor_quarter_small_projects)

# contractors holding "only" large projects in a given quarter
contractors_holding_only_large_projects=setdiff(contractors_holding_large_projects,
                                                contractors_holding_small_projects)

# contractors holding "only" small projects in a given quarter
contractors_holding_only_small_projects=setdiff(contractors_holding_small_projects,
                                                contractors_holding_large_projects)

# contractors holding "both" large & small projects in a given quarter
contractors_holding_both_large_and_small_projects=intersect(contractors_holding_large_projects,
                                                contractors_holding_small_projects)


# large projects held by contractor holding at least one small project
reg_df[,contractor_quarter:=paste(recipient_duns,
                                  action_date_year_quarter,
                                  sep='_')]

reg_df[,treat_new:=case_when(treat_i==1 ~ 1,
                             treat_i==0 & !(recipient_duns%in%small_contractors)~0,
                             treat_i==0 & recipient_duns%in%small_contractors~NaN)]


reg_df[,treat_only_small:=case_when(treat_i==1 & contractor_quarter%in%contractors_holding_only_small_projects~1,
                                              treat_i==1 & contractor_quarter%in%contractors_holding_both_large_and_small_projects~0,
                                              treat_i==0 & contractor_quarter%in%contractors_holding_only_large_projects~0,
                                              treat_i==0 & contractor_quarter%in%contractors_holding_both_large_and_small_projects~NaN)]


reg_df[,treat_small_with_large_new:=case_when(treat_i==1 & contractor_quarter%in%contractors_holding_only_small_projects~0,
                                              treat_i==1 & contractor_quarter%in%contractors_holding_both_large_and_small_projects~1,
                                              treat_i==0 & contractor_quarter%in%contractors_holding_only_large_projects~0,
                                              treat_i==0 & contractor_quarter%in%contractors_holding_both_large_and_small_projects~NaN)]

# already adjusted above, but to be super cautius!
reg_df_subset=subset(reg_df,!(treat_i==0 & recipient_duns%in%small_contractors))

reg_df_subset[,wins_percentage_delay:=Winsorize(100*percentage_delay,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

reg_df_subset[,winsorized_delay:=Winsorize(delay,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

# time spent in the project so far/total time of the project
# if project was active in previous quarter
reg_df_subset[,project_quarter_stage:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1),as.numeric(lag(action_date_year_quarter,1)-initial_start_date)/as.numeric(lag(last_reported_end_date,1)-initial_start_date),NaN)]

# (action_date_year_quarter-90) to get beginning of the quarter

reg_df_subset[,wins_project_quarter_stage:=Winsorize(project_quarter_stage,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]
```

```{r contractor_one_type,include=FALSE}
one_type_contractors=reg_df[,n_distinct(treat_i),by='recipient_duns']
one_type_contractors=unique(subset(one_type_contractors,V1==1 &
                                     !is.na(recipient_duns))$recipient_duns)

reg_df_one_type=subset(reg_df,recipient_duns%in%one_type_contractors)

reg_df_one_type[,wins_percentage_delay:=Winsorize(100*percentage_delay,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

# time spent in the project so far/total time of the project
# if project was active in previous quarter
reg_df_one_type[,project_quarter_stage:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1),as.numeric(lag(action_date_year_quarter,1)-initial_start_date)/as.numeric(lag(last_reported_end_date,1)-initial_start_date),NaN)]

# (action_date_year_quarter-90) to get beginning of the quarter

reg_df_one_type[,wins_project_quarter_stage:=Winsorize(project_quarter_stage,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]
```

```{r contractor_two_type, include=FALSE}
two_type_contractors=reg_df[,n_distinct(treat_i),by='recipient_duns']
two_type_contractors=unique(subset(two_type_contractors,V1==2 &
                                     !is.na(recipient_duns))$recipient_duns)

reg_df_two_type=subset(reg_df,recipient_duns%in%two_type_contractors)

reg_df_two_type[,wins_percentage_delay:=Winsorize(100*percentage_delay,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

# time spent in the project so far/total time of the project
# if project was active in previous quarter
reg_df_two_type[,project_quarter_stage:=ifelse(contract_award_unique_key==lag(contract_award_unique_key,1),as.numeric(lag(action_date_year_quarter,1)-initial_start_date)/as.numeric(lag(last_reported_end_date,1)-initial_start_date),NaN)]

# (action_date_year_quarter-90) to get beginning of the quarter

reg_df_two_type[,wins_project_quarter_stage:=Winsorize(project_quarter_stage,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

```

# Demeaned delay rate (in percentage)

* Subtract the average pre-quickpay delay rate from each observation

```{r demeaned_plot_one_type,echo=FALSE,results='asis'}

mean_delay=reg_df_subset[!is.na(wins_percentage_delay) 
                  & action_date_year_quarter<=as.Date('2012-06-30'), 
              mean(wins_percentage_delay),  
              by = c('action_date_year_quarter','treat_new')]
mean_delay[,year_quarter:=format(action_date_year_quarter,"%Y-%b")]
mean_delay=mean_delay[order(action_date_year_quarter,treat_new)]

pre_qp_mean_small=mean(subset(mean_delay,
                         action_date_year_quarter<=as.Date('2011-04-27') &
                           treat_new==1)$V1,na.rm=T)
pre_qp_mean_large=mean(subset(mean_delay,
                              action_date_year_quarter<=as.Date('2011-04-27') &
                                treat_new==0)$V1,na.rm=T)

mean_delay[,demeaned_delay:=ifelse(treat_new==1,
                                   V1-pre_qp_mean_small,
                                   V1-pre_qp_mean_large)]

mean_delay[,business_type:=ifelse(treat_new==1,"S","O")]

ggplot(mean_delay, aes(x=year_quarter,
                       y=demeaned_delay, 
                       group = business_type))+
  geom_line(aes(linetype=business_type, color=business_type),alpha=0.7) +    
  scale_x_discrete(limits=mean_delay$year_quarter)+
  geom_vline(xintercept =10.2,alpha=0.8,size=0.15,linetype="solid")+
  theme_minimal()+
  labs(x="Time", 
       y = "Average percentage delay rate")+
  scale_linetype_manual(name  ="",
                        breaks=c("S", "O"),
                        labels=c("Treated","Control"),
                        values=c("solid","dashed"))+
  scale_color_manual(name  ="",
                     breaks=c("S", "O"),
                     labels=c("Treated","Control"),
                     values=c('black','black'))+
  scale_shape_manual(name  ="",
                     breaks=c("S", "O"),
                     labels=c("Treated","Control"),
                     values=c(16,17))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))+
  coord_fixed(ratio=2)
# 
# ggsave(path=figures_folder,
#        bg="white",
#        width = 8,
#        height = 5,
#        filename = "pc_delay_demeaned_one_type.png")
```

```{r stargazer_format, include=FALSE}
# Code to extract only the inner part (nested within tabular) of table from stargazer
# We will use this along with threeparttable in latex later 
# Code adapted from Patrick Baylis's blog on the topic:
# https://www.patrickbaylis.com/blog/2019-11-25-r-reg-tables/
make_tex_pieces <- function(stargazer_output) {
  # Split up into header, footer, and inner
  idx0 <- grep("begin{tabular}", stargazer_output, fixed = T) # Start of \begin{tabular}
  idx1 <- grep("end{tabular}", stargazer_output, fixed = T) # End of \begin{tabular}
  idx2<-grep("Adjusted",stargazer_output,fixed=T)
  
  tex_header <- c(stargazer_output[idx0],"\\toprule")
  tex_footer <- c("\\bottomrule", stargazer_output[idx1])
  tex_inner<-c(stargazer_output[(idx0+3):idx2])
  
  # Remove [-1.8ex] and replace \hline with \midrule
  tex_inner <- gsub("\\\\[-[\\.0-9]+ex]", "", tex_inner)
  
  tex_inner <- gsub("\\hline ", "\\midrule", tex_inner)
  # Return these as a 3 element list so that the user can insert header rows (column labels)
  # and footer rows (summary statistics, fixed effects)
  # list(header = tex_header, inner = tex_inner, footer = tex_footer)
  c(tex_header,tex_inner,tex_footer)
}
```

# Baseline Regressions

$$ PercentDelay_{it} = \beta_0 + \beta_1 Treat_i + \beta_2 Post_t + \beta_3 (Treat_i \times Post_t) + e_{it}$$ 

$$ \begin{aligned} PercentDelay_{it} &=& \alpha+\beta_0 Treat_i + \beta_1 Post_t + \beta_2 (Treat_i \times Post_t)\\
&+&  X_i + (Post_t \times X_i) + \mu_t + \theta_{firm} + \lambda_{task}+ \epsilon_{it}
\end{aligned}$$


```{r baseline_regressions, echo=FALSE, results='asis'}
# Baseline Regressions 
baseline_reg=felm(wins_percentage_delay~treat_new+
                     post_t:treat_new+
                     post_t|
                    0| # no fixed effects
                    0| # no IV
                    contract_award_unique_key, # clustered at project level
                  data=reg_df_subset, 
                  exactDOF = TRUE, 
                  cmethod = "reghdfe")
# time fixed effects also included in the following specs
controls_and_no_fe=felm(wins_percentage_delay~treat_new+
                           post_t:treat_new+
                           post_t+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            0|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
# time fixed effects also included in the following specs
controls_and_time_fe=felm(wins_percentage_delay~treat_new+
                             post_t:treat_new+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_time_task_fe=felm(wins_percentage_delay~treat_new+
                              post_t:treat_new+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_all_fe=felm(wins_percentage_delay~treat_new+
                            post_t:treat_new+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
base_table<-stargazer(baseline_reg,
          controls_and_no_fe,
          controls_and_time_fe,
          controls_time_task_fe,
          controls_and_all_fe,
          title = "Effect of QuickPay on project delay rates",
          dep.var.labels="$PercentDelay_{it}$",
          dep.var.caption = "",
          covariate.labels = c("$Treat_i$","$Post_t$","$Treat_i \\times Post_t$","Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          digits=2,
          digits.extra=2,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(c("Duration, Budget, Bids","No",rep("Yes",4)),
                           c("$Post_t \\times$  (Duration, Budget, Bids)","No",rep("Yes",4)),
                           c("Project stage","No",rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:winsorized_initial_budget_i',
                   'post_t:number_of_offers_received',
                   'wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level."),
          header=F)
# 
# base_table_tex=make_tex_pieces(base_table)
# # Write to file
# write(base_table_tex,
#       paste0(tables_folder,"/base_table.tex"))

```

## Days of delay

```{r baseline_regressions_days_of_delay, echo=FALSE, results='asis'}

# Baseline Regressions 
baseline_reg=felm(winsorized_delay~treat_new+
                     post_t:treat_new+
                     post_t|
                    0| # no fixed effects
                    0| # no IV
                    contract_award_unique_key, # clustered at project level
                  data=reg_df_subset, 
                  exactDOF = TRUE, 
                  cmethod = "reghdfe")
# time fixed effects also included in the following specs
controls_and_no_fe=felm(winsorized_delay~treat_new+
                           post_t:treat_new+
                           post_t+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            0|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
# time fixed effects also included in the following specs
controls_and_time_fe=felm(winsorized_delay~treat_new+
                             post_t:treat_new+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_time_task_fe=felm(winsorized_delay~treat_new+
                              post_t:treat_new+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_all_fe=felm(winsorized_delay~treat_new+
                            post_t:treat_new+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
base_table<-stargazer(baseline_reg,
          controls_and_no_fe,
          controls_and_time_fe,
          controls_time_task_fe,
          controls_and_all_fe,
          title = "Effect of QuickPay on project delay rates",
          dep.var.labels="$DelayDays_{it}$",
          dep.var.caption = "",
          covariate.labels = c("$Treat_i$","$Post_t$","$Treat_i \\times Post_t$","Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          digits=2,
          digits.extra=2,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(c("Duration, Budget, Bids","No",rep("Yes",4)),
                           c("$Post_t \\times$  (Duration, Budget, Bids)","No",rep("Yes",4)),
                           c("Project stage","No",rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:winsorized_initial_budget_i',
                   'post_t:number_of_offers_received',
                   'wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level."),
          header=F)
```
# Event study

$PercentDelay_{it}=\beta_0 + \beta_1 Treat_i + \beta_2 Treat_i \times Quarter_t + Controls + \gamma_{task} + \theta_{naics}+\lambda_{quarter}+\epsilon_{it}$

```{r event_study, echo=FALSE, results='asis'}

reg_df_subset[,relative_quarter:=case_when(action_date_year_quarter=="2010-03-31"~-5,
                  action_date_year_quarter=="2010-06-30"~-4,
                  action_date_year_quarter=="2010-09-30"~-3,
                  action_date_year_quarter=="2010-12-31"~-2,
                  action_date_year_quarter=="2011-03-31"~-1,
                  action_date_year_quarter=="2011-06-30"~0,
                  action_date_year_quarter=="2011-09-30"~1,
                  action_date_year_quarter=="2011-12-31"~2,
                  action_date_year_quarter=="2012-03-31"~3,
                  action_date_year_quarter=="2012-06-30"~4)]
reg_df_subset[, time_to_treat := ifelse(treat_new==1, relative_quarter, 0)]

mod_twfe = fixest::feols(wins_percentage_delay ~ i(time_to_treat, treat_new, ref = -1) +
                    	   	  treat_new+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|   
		  naics_code+product_or_service_code+action_date_year_quarter,        
		 cluster = ~contract_award_unique_key,
		 data = reg_df_subset)

# Default event study plot
# fixest::iplot(mod_twfe,
#       xlab = 'Quarter relative to QuickPay',
#       main = 'Effect on Average Percentage Delay Rate',
#       grid=F,
#       ylim.add=0.25,
#       zero.par=list(lwd=0.25),
#       ref.line.par = list(col = "black", lty=3, lwd=0.8), #lty= linetype, lwd=linewidth
#       pt.join = T,
#       x=c(-5:4))

data_event_study=fixest::iplot(mod_twfe,only.params=T,
      x=c(-5:4))$prms
setDT(data_event_study)[,`Quarter relative to QuickPay`:=as.factor(x)]

ggplot(data_event_study,aes(x=`Quarter relative to QuickPay`,
                            y=y,
                            group=1))+
  geom_point(size=1.5,alpha=0.7)+
  geom_errorbar(aes(ymin = ci_low, 
                    ymax = ci_high),
                width=0.01,
                size=0.25,
                alpha=0.7)+
#  geom_line(alpha=0.7,size=0.25)+
  geom_hline(yintercept =0,alpha=0.6,size=0.15)+
  geom_vline(xintercept =5.5,alpha=0.8,size=0.15,linetype="dashed")+
  theme_minimal()+ 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(size=11),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
    legend.text = element_text(size=11))+
  theme(legend.position="bottom")+
  ylab("Point estimate \n (Percentage Delay Rate)")+ 
  #ylim(-1.05, 2.5)+
  scale_y_continuous(breaks = seq(-1, 3, 1))+
  coord_fixed(ratio=1)

# ggsave(path=figures_folder,
#        width = 8,
#        height = 5,
#        bg="white",
#        filename = "event_study_plot.png")
```

# Parallel Trends Test

```{r parallel_trends_test, echo=FALSE, results='asis'}
df_qn<-unique(reg_df_subset,by='action_date_year_quarter')[,"action_date_year_quarter"]
df_qn=df_qn[order(action_date_year_quarter)][,quarter_number:=seq.int(nrow(df_qn))]
reg_df_subset=merge(reg_df_subset,df_qn,by='action_date_year_quarter')

# Baseline Regressions 
m1=felm(wins_percentage_delay~treat_new+
                     quarter_number:treat_new+
                    quarter_number|
                    0| # no fixed effects
                    0| # no IV
                    contract_award_unique_key, # clustered at project level
                  data=subset(reg_df_subset, post_t==0),
                  exactDOF = TRUE, 
                  cmethod = "reghdfe")

# time fixed effects also included in the following specs

m2=felm(wins_percentage_delay~treat_new+
                           quarter_number:treat_new+
                           quarter_number+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            quarter_number:log(1+winsorized_initial_duration_in_days_i)+
                            quarter_number:log(1+winsorized_initial_budget_i)+
                            quarter_number:number_of_offers_received|
                            0|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset, post_t==0),
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
# time fixed effects also included in the following specs
m3=felm(wins_percentage_delay~treat_new+
                             quarter_number:treat_new+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            quarter_number:log(1+winsorized_initial_duration_in_days_i)+
                            quarter_number:log(1+winsorized_initial_budget_i)+
                            quarter_number:number_of_offers_received|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset, post_t==0), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
m4=felm(wins_percentage_delay~treat_new+
                              quarter_number:treat_new+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            quarter_number:log(1+winsorized_initial_duration_in_days_i)+
                            quarter_number:log(1+winsorized_initial_budget_i)+
                            quarter_number:number_of_offers_received|
                            product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset, post_t==0), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
m5=felm(wins_percentage_delay~treat_new+
                            quarter_number:treat_new+
                           log(wins_project_quarter_stage)+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            quarter_number:log(1+winsorized_initial_duration_in_days_i)+
                            quarter_number:log(1+winsorized_initial_budget_i)+
                            quarter_number:number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset, post_t==0), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

pt=stargazer(m1,m2,m3,m4,m5,
          title = "Linear Time Trend Before QuickPay",
          dep.var.labels="$PercentDelay_{it}$",
          dep.var.caption = "",
          covariate.labels = c("$Treat_i$","$QuarterNum$","$Treat_i \\times QuarterNum$","Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          digits=2,
          digits.extra=2,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(c("Duration, Budget, Bids","No",rep("Yes",4)),
                           c("$Post_t \\times$  (Duration, Budget, Bids)","No",rep("Yes",4)),
                           c("Project stage","No",rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'quarter_number:winsorized_initial_duration_in_days_i',
                   'quarter_number:winsorized_initial_budget_i',
                   'quarter_number:number_of_offers_received',
                   'wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level.",
                  "Observations are for quarters before quickpay."),
          header=F)
# 
# pt_table_tex=make_tex_pieces(pt)
# # Write to file
# write(pt_table_tex,
#       paste0(tables_folder,"/parallel_trends_test_one_type.tex"))

```

# Placebo Test

```{r placebo_tables, echo=FALSE, results='asis'}
reg_df_placebo=subset(reg_df_subset,post_t==0)

reg_df_placebo[,wins_percentage_delay:=Winsorize(100*percentage_delay,
                               probs=c(0.025,0.975),
                               na.rm=T)]

reg_df_placebo[,wins_project_quarter_stage:=Winsorize(project_quarter_stage,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

reg_df_placebo[,winsorized_initial_duration_in_days_i:=
                    Winsorize(initial_duration_in_days_i,
                    probs=c(0.025,0.975),
                    na.rm=T)]

# InitialBudget_i

reg_df_placebo[,winsorized_initial_budget_i:=
                    Winsorize(base_and_all_options_value,                    
                              probs=c(0.025,0.975),
                              na.rm=T)]
for(i in 3:5){
  print(i)
  reg_df_placebo[,placebo_post_t:=ifelse(quarter_number>=i,1,0)]  
  a1=felm(wins_percentage_delay~treat_new+
                treat_new:placebo_post_t+
                placebo_post_t|
                0|
                0|
                contract_award_unique_key,
              data=reg_df_placebo,
              exactDOF = TRUE, 
              cmethod = "reghdfe")
    a2=felm(wins_percentage_delay~treat_new+
                treat_new:placebo_post_t+
                placebo_post_t+  
                log(wins_project_quarter_stage)+
                log(1+winsorized_initial_duration_in_days_i)+
                log(1+winsorized_initial_budget_i)+
                number_of_offers_received+
                placebo_post_t:log(1+winsorized_initial_duration_in_days_i)+
                placebo_post_t:log(1+winsorized_initial_budget_i)+
                placebo_post_t:number_of_offers_received|
                0|
                0|
                contract_award_unique_key,
              data=reg_df_placebo,
              exactDOF = TRUE, 
              cmethod = "reghdfe")
      a3=felm(wins_percentage_delay~treat_new+
                treat_new:placebo_post_t+
                log(wins_project_quarter_stage)+
                log(1+winsorized_initial_duration_in_days_i)+
                log(1+winsorized_initial_budget_i)+
                number_of_offers_received+
                placebo_post_t:log(1+winsorized_initial_duration_in_days_i)+
                placebo_post_t:log(1+winsorized_initial_budget_i)+
                placebo_post_t:number_of_offers_received|
                action_date_year_quarter|
                0|
                contract_award_unique_key,
              data=reg_df_placebo,
              exactDOF = TRUE, 
              cmethod = "reghdfe")
        a4=felm(wins_percentage_delay~treat_new+
                treat_new:placebo_post_t+
                log(wins_project_quarter_stage)+
                log(1+winsorized_initial_duration_in_days_i)+
                log(1+winsorized_initial_budget_i)+
                number_of_offers_received+
                placebo_post_t:log(1+winsorized_initial_duration_in_days_i)+
                placebo_post_t:log(1+winsorized_initial_budget_i)+
                placebo_post_t:number_of_offers_received|
                product_or_service_code+
                action_date_year_quarter|
                0|
                contract_award_unique_key,
              data=reg_df_placebo,
              exactDOF = TRUE, 
              cmethod = "reghdfe")
        a5=felm(wins_percentage_delay~treat_new+
                treat_new:placebo_post_t+
                log(wins_project_quarter_stage)+
                log(1+winsorized_initial_duration_in_days_i)+
                log(1+winsorized_initial_budget_i)+
                number_of_offers_received+
                placebo_post_t:log(1+winsorized_initial_duration_in_days_i)+
                placebo_post_t:log(1+winsorized_initial_budget_i)+
                placebo_post_t:number_of_offers_received|
                naics_code+
                product_or_service_code+
                action_date_year_quarter|
                0|
                contract_award_unique_key,
              data=reg_df_placebo,
              exactDOF = TRUE, 
              cmethod = "reghdfe")
        
placebo_table=stargazer(a1,a2,a3,a4,a5,
          title = paste0("Placebo test: Treatment Time ",
                         as.character(unique(subset(reg_df_placebo,
                                        quarter_number==i)$action_date_year_quarter))),
          dep.var.labels="$PercentDelay_{it}$",
          dep.var.caption = "",
          covariate.labels = c("$Treat_i$","$Post$","$Treat_i \\times Post$","Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          digits=2,
          digits.extra=2,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(c("Duration, Budget, Bids","No",rep("Yes",4)),
                           c("$Post_t \\times$  (Duration, Budget, Bids)","No",rep("Yes",4)),
                           c("Project stage","No",rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'quarter_number:winsorized_initial_duration_in_days_i',
                   'quarter_number:winsorized_initial_budget_i',
                   'quarter_number:number_of_offers_received',
                   'wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level.",
                  "Observations are for quarters before quickpay."),
          header=F)
}
# placebo_folder='~/Desktop/Research/QuickPay/paper/Tables/robustness'
# 
# placebo_table_tex=make_tex_pieces(placebo_table)
# # Write to file
# write(placebo_table_tex,
#       paste0(placebo_folder,
#              "/one_type_placebo_table_time_",
#              as.character(unique(subset(reg_df_placebo,
#                 quarter_number==i)$action_date_year_quarter)),
#              ".tex"))
# }

```

# Summary statistics [Full sample]

```{r summary_stats, eval=FALSE, include=FALSE}

treated_projs_preqp=subset(reg_df,treat_i==1 & post_t==0)
control_projs_preqp=subset(reg_df,treat_i==0 & post_t==0)

# Percentage delay
mean(treated_projs_preqp$wins_percentage_delay,na.rm=T)
sd(treated_projs_preqp$wins_percentage_delay,na.rm=T)
nrow(subset(treated_projs_preqp,!is.na(wins_percentage_delay)))
min(treated_projs_preqp$wins_percentage_delay,na.rm=T)
max(treated_projs_preqp$wins_percentage_delay,na.rm=T)

mean(control_projs_preqp$wins_percentage_delay,na.rm=T)
sd(control_projs_preqp$wins_percentage_delay,na.rm=T)
nrow(subset(control_projs_preqp,!is.na(wins_percentage_delay)))
min(control_projs_preqp$wins_percentage_delay,na.rm=T) 
# because we have winsorized, min/max #s are same
# even if we cut off the tails, min/max #s will be same 
max(control_projs_preqp$wins_percentage_delay,na.rm=T)

# Initial duration
mean(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)
sd(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)
nrow(subset(treated_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(winsorized_initial_duration_in_days_i)))
min(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)
max(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)

mean(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)
sd(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)
nrow(subset(control_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(winsorized_initial_duration_in_days_i)))
min(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)
max(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)

# Initial budget
mean(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)
sd(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)
nrow(subset(treated_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(winsorized_initial_budget_i)))
min(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)
max(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)

mean(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)
sd(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)
nrow(subset(control_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(winsorized_initial_budget_i)))
min(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)
max(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)

# Number of offers

mean(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)
sd(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)
nrow(subset(treated_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(number_of_offers_received)))
min(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)
max(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)

mean(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)
sd(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)
nrow(subset(control_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(number_of_offers_received)))
min(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)
max(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)

# Project stage

mean(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)
sd(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)
nrow(subset(treated_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(wins_project_quarter_stage)))
min(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)
max(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)

mean(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)
sd(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)
nrow(subset(control_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(wins_project_quarter_stage)))
min(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)
max(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)


# Positive delay rate

treated_projs_preqp[,positive_delay:=ifelse(delay>0,1,0)]
control_projs_preqp[,positive_delay:=ifelse(delay>0,1,0)]

mean(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$positive_delay,na.rm=T)
sd(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$positive_delay,na.rm=T)
nrow(subset(treated_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(positive_delay)))

mean(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$positive_delay,na.rm=T)
sd(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$positive_delay,na.rm=T)
nrow(subset(control_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(positive_delay)))

# Negative delay rate

treated_projs_preqp[,negative_delay:=ifelse(delay<0,1,0)]
control_projs_preqp[,negative_delay:=ifelse(delay<0,1,0)]

mean(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$negative_delay,na.rm=T)
sd(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$negative_delay,na.rm=T)
nrow(subset(treated_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(negative_delay)))

mean(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$negative_delay,na.rm=T)
sd(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$negative_delay,na.rm=T)
nrow(subset(control_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(negative_delay)))

# Financial assistance

mean(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$receives_financial_assistance,na.rm=T)
sd(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$receives_financial_assistance,na.rm=T)
nrow(subset(treated_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(receives_financial_assistance)))

mean(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$receives_financial_assistance,na.rm=T)
sd(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$receives_financial_assistance,na.rm=T)
nrow(subset(control_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(receives_financial_assistance)))

# Competition

mean(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$competitively_awarded_i,na.rm=T)
sd(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$competitively_awarded_i,na.rm=T)
nrow(subset(treated_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(competitively_awarded_i)))

mean(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$competitively_awarded_i,na.rm=T)
sd(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$competitively_awarded_i,na.rm=T)
nrow(subset(control_projs_preqp,!is.na(wins_percentage_delay) &
                                !is.na(competitively_awarded_i)))

# Bid Metrics for Competitive Projects

mean(subset(treated_projs_preqp,competitively_awarded_i==1 &
!is.na(number_of_offers_received))$number_of_offers_received,na.rm=T)

mean(subset(treated_projs_preqp,competitively_awarded_i==1 &
!is.na(winsorized_initial_duration_in_days_i))$winsorized_initial_duration_in_days_i,na.rm=T)

mean(subset(treated_projs_preqp,competitively_awarded_i==1 &
!is.na(winsorized_initial_budget_i))$winsorized_initial_budget_i,na.rm=T)

# Number of tasks

n_distinct(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$product_or_service_code)

n_distinct(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$product_or_service_code)

# Number of industries

n_distinct(subset(treated_projs_preqp,
            !is.na(wins_percentage_delay))$naics_code)

n_distinct(subset(control_projs_preqp,
            !is.na(wins_percentage_delay))$naics_code)

```

```{r summary_stats_afterqp, eval=FALSE, include=FALSE}

treated_projs_postqp=subset(reg_df,treat_i==1 & post_t==1)
control_projs_postqp=subset(reg_df,treat_i==0 & post_t==1)

# Percentage delay
mean(treated_projs_postqp$wins_percentage_delay,na.rm=T)
sd(treated_projs_postqp$wins_percentage_delay,na.rm=T)
nrow(subset(treated_projs_postqp,!is.na(wins_percentage_delay)))
min(treated_projs_postqp$wins_percentage_delay,na.rm=T)
max(treated_projs_postqp$wins_percentage_delay,na.rm=T)

mean(control_projs_postqp$wins_percentage_delay,na.rm=T)
sd(control_projs_postqp$wins_percentage_delay,na.rm=T)
nrow(subset(control_projs_postqp,!is.na(wins_percentage_delay)))
min(control_projs_postqp$wins_percentage_delay,na.rm=T) 
# because we have winsorized, min/max #s are same
# even if we cut off the tails, min/max #s will be same 
max(control_projs_postqp$wins_percentage_delay,na.rm=T)

# Initial duration
mean(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)
sd(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)
nrow(subset(treated_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(winsorized_initial_duration_in_days_i)))
min(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)
max(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)

mean(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)
sd(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)
nrow(subset(control_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(winsorized_initial_duration_in_days_i)))
min(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)
max(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_duration_in_days_i,na.rm=T)

# Initial budget
mean(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)
sd(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)
nrow(subset(treated_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(winsorized_initial_budget_i)))
min(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)
max(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)

mean(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)
sd(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)
nrow(subset(control_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(winsorized_initial_budget_i)))
min(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)
max(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$winsorized_initial_budget_i,na.rm=T)

# Number of offers

mean(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)
sd(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)
nrow(subset(treated_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(number_of_offers_received)))
min(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)
max(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)

mean(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)
sd(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)
nrow(subset(control_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(number_of_offers_received)))
min(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)
max(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$number_of_offers_received,na.rm=T)

# Project stage

mean(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)
sd(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)
nrow(subset(treated_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(wins_project_quarter_stage)))
min(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)
max(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)

mean(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)
sd(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)
nrow(subset(control_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(wins_project_quarter_stage)))
min(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)
max(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$wins_project_quarter_stage,na.rm=T)


# Positive delay rate

treated_projs_postqp[,positive_delay:=ifelse(delay>0,1,0)]
control_projs_postqp[,positive_delay:=ifelse(delay>0,1,0)]

mean(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$positive_delay,na.rm=T)
sd(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$positive_delay,na.rm=T)
nrow(subset(treated_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(positive_delay)))

mean(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$positive_delay,na.rm=T)
sd(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$positive_delay,na.rm=T)
nrow(subset(control_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(positive_delay)))

# Negative delay rate

treated_projs_postqp[,negative_delay:=ifelse(delay<0,1,0)]
control_projs_postqp[,negative_delay:=ifelse(delay<0,1,0)]

mean(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$negative_delay,na.rm=T)
sd(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$negative_delay,na.rm=T)
nrow(subset(treated_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(negative_delay)))

mean(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$negative_delay,na.rm=T)
sd(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$negative_delay,na.rm=T)
nrow(subset(control_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(negative_delay)))

# Financial assistance

mean(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$receives_financial_assistance,na.rm=T)
sd(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$receives_financial_assistance,na.rm=T)
nrow(subset(treated_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(receives_financial_assistance)))

mean(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$receives_financial_assistance,na.rm=T)
sd(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$receives_financial_assistance,na.rm=T)
nrow(subset(control_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(receives_financial_assistance)))

# Competition

mean(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$competitively_awarded_i,na.rm=T)
sd(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$competitively_awarded_i,na.rm=T)
nrow(subset(treated_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(competitively_awarded_i)))

mean(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$competitively_awarded_i,na.rm=T)
sd(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$competitively_awarded_i,na.rm=T)
nrow(subset(control_projs_postqp,!is.na(wins_percentage_delay) &
                                !is.na(competitively_awarded_i)))

# Bid Metrics for Competitive Projects

mean(subset(treated_projs_postqp,competitively_awarded_i==1 &
!is.na(number_of_offers_received))$number_of_offers_received,na.rm=T)

mean(subset(treated_projs_postqp,competitively_awarded_i==1 &
!is.na(winsorized_initial_duration_in_days_i))$winsorized_initial_duration_in_days_i,na.rm=T)

mean(subset(treated_projs_postqp,competitively_awarded_i==1 &
!is.na(winsorized_initial_budget_i))$winsorized_initial_budget_i,na.rm=T)

# Number of tasks

n_distinct(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$product_or_service_code)

n_distinct(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$product_or_service_code)

# Number of industries

n_distinct(subset(treated_projs_postqp,
            !is.na(wins_percentage_delay))$naics_code)

n_distinct(subset(control_projs_postqp,
            !is.na(wins_percentage_delay))$naics_code)


```

# Congestion Effect

## Number of projects per contractor

### Contractors holding only small or only large projects

```{r num_projects_0,warning=FALSE, echo=FALSE, results='asis'}

active_before_qp=unique(subset(reg_df,post_t==0)$recipient_duns)
contractor_quarter=reg_df_one_type[,n_distinct(contract_award_unique_key),by=c('recipient_duns',
                                                            'action_date_year_quarter')]
setnames(contractor_quarter,'V1','num_projects')
contractor_quarter[,post_t:=ifelse(action_date_year_quarter>as.Date('2011-04-27'),1,0)]

contractor_quarter=merge(contractor_quarter,
                         unique(reg_df_one_type[,c('recipient_duns','treat_i')]),
                         by='recipient_duns')

contractor_quarter[,business_type:=ifelse(treat_i==1,"S","O")]

projects_plot=contractor_quarter[,mean(num_projects),
                by=c('action_date_year_quarter','business_type')]

ggplot(projects_plot,
       aes(x=as.factor(action_date_year_quarter),
           y=V1,
           group=business_type))+
  geom_line(aes(linetype=business_type),alpha=0.7)+
  geom_point(aes(shape=business_type),size=1.5)+
  theme_minimal()+
  labs(x="Time", 
       y = "Average number of projects per contractor")+
  scale_linetype_manual(name  ="",
                        breaks=c("S", 
                                 "O"),
                        labels=c("Treated","Control"),
                        values=c("solid","dashed"))+
  scale_shape_manual(name  ="",
                     breaks=c("S", 
                              "O"),
                     labels=c("Treated","Control"),
                     values=c(16,17))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))

m1=felm(num_projects~treat_i+
          post_t:treat_i+post_t|
          0| # no fixed effects
          0| # no IV
          recipient_duns, # clustered at the contractor level
        data=contractor_quarter,
        exactDOF = TRUE, 
        cmethod = "reghdfe")

m2=felm(num_projects~treat_i+
          post_t:treat_i|
          action_date_year_quarter| # no fixed effects
          0| # no IV
          recipient_duns, # clustered at the contractor level
        data=contractor_quarter,
        exactDOF = TRUE, 
        cmethod = "reghdfe")

num_projects_table=stargazer(m1,m2,
          digits=2,
          digits.extra=2,
          title = "Num Contractor Projects and QuickPay reform",
          dep.var.labels="Number of projects",
          dep.var.caption = "",
          covariate.labels =c("$Treat_i$",
                               "$Post_t$",
                               "$Treat_i \\times Post_t$",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(c("Time fixed effects",rep("No",1),rep("Yes",1))),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a contractor-quarter.",
                  "SEs are robust and clustered at the contractor level.",
                  "Sample restricted to contractors performing only one type of project."),
          header=F)
# 
# num_projects_table_tex=make_tex_pieces(num_projects_table)
# # Write to file
# write(num_projects_table_tex,
#       paste0(tables_folder,
#              "/congestion_num_projects.tex"))
```

### Contractors holding at least one small project are "treated"

```{r num_projects_1,warning=FALSE, eval=FALSE, echo=FALSE}

contractor_type=reg_df[,sum(treat_i),by='recipient_duns']
contractor_type[,treat_i:=ifelse(V1>0,1,0)]
contractor_type=contractor_type[,c('recipient_duns','treat_i')]

contractor_quarter=reg_df[,n_distinct(contract_award_unique_key),by=c('recipient_duns',
                                                            'action_date_year_quarter')]
setnames(contractor_quarter,'V1','num_projects')
contractor_quarter[,post_t:=ifelse(action_date_year_quarter>as.Date('2011-04-27'),1,0)]

contractor_quarter=merge(contractor_quarter,
                         contractor_type,
                         by='recipient_duns')
contractor_quarter=subset(contractor_quarter,!is.na(recipient_duns))

contractor_quarter[,business_type:=ifelse(treat_i==1,"S","O")]

projects_plot=contractor_quarter[,mean(num_projects),
                by=c('action_date_year_quarter','business_type')]

ggplot(projects_plot,
       aes(x=as.factor(action_date_year_quarter),
           y=V1,
           group=business_type))+
  geom_line(aes(linetype=business_type),alpha=0.7)+
  geom_point(aes(shape=business_type),size=1.5)+
  theme_minimal()+
  labs(x="Time", 
       y = "Average number of projects per contractor")+
  scale_linetype_manual(name  ="",
                        breaks=c("S", 
                                 "O"),
                        labels=c("Treated","Control"),
                        values=c("solid","dashed"))+
  scale_shape_manual(name  ="",
                     breaks=c("S", 
                              "O"),
                     labels=c("Treated","Control"),
                     values=c(16,17))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))

m1=felm(num_projects~treat_i+
          post_t:treat_i+post_t|
          0| # no fixed effects
          0| # no IV
          recipient_duns, # clustered at the contractor level
        data=contractor_quarter,
        exactDOF = TRUE, 
        cmethod = "reghdfe")

m2=felm(num_projects~treat_i+
          post_t:treat_i|
          action_date_year_quarter| # no fixed effects
          0| # no IV
          recipient_duns, # clustered at the contractor level
        data=contractor_quarter,
        exactDOF = TRUE, 
        cmethod = "reghdfe")

num_projects_table=stargazer(m1,m2,
          digits=2,
          digits.extra=2,
          title = "Num Contractor Projects and QuickPay reform",
          dep.var.labels="Number of projects",
          dep.var.caption = "",
          covariate.labels =c("$Treat_i$",
                               "$Post_t$",
                               "$Treat_i \\times Post_t$",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(c("Time fixed effects",rep("No",1),rep("Yes",1))),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a contractor-quarter.",
                  "SEs are robust and clustered at the contractor level."),
          header=F)
```

## Total budget 

### Contractors holding only small or only large projects

```{r budget_0,warning=FALSE, echo=FALSE, results='asis'}
contractor_quarter=reg_df_one_type[,sum(winsorized_initial_budget_i),
                                   by=c('recipient_duns',
                                        'action_date_year_quarter')]
setnames(contractor_quarter,'V1','total_budget_across_projects')
contractor_quarter[,post_t:=ifelse(action_date_year_quarter>as.Date('2011-04-27'),1,0)]

contractor_quarter=merge(contractor_quarter,
                         unique(reg_df_one_type[,c('recipient_duns','treat_i')]),
                         by='recipient_duns')

contractor_quarter[,business_type:=ifelse(treat_i==1,"S","O")]

projects_plot=contractor_quarter[,mean(total_budget_across_projects),
                by=c('action_date_year_quarter','business_type')]

ggplot(projects_plot,
       aes(x=as.factor(action_date_year_quarter),
           y=V1,
           group=business_type))+
  geom_line(aes(linetype=business_type),alpha=0.7)+
  geom_point(aes(shape=business_type),size=1.5)+
  theme_minimal()+
  labs(x="Time", 
       y = "Average budget across projects per contractor")+
  scale_linetype_manual(name  ="",
                        breaks=c("S", 
                                 "O"),
                        labels=c("Treated","Control"),
                        values=c("solid","dashed"))+
  scale_shape_manual(name  ="",
                     breaks=c("S", 
                              "O"),
                     labels=c("Treated","Control"),
                     values=c(16,17))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))

m1=felm(total_budget_across_projects~treat_i+
          post_t:treat_i+post_t|
          0| # no fixed effects
          0| # no IV
          recipient_duns, # clustered at the contractor level
        data=contractor_quarter,
        exactDOF = TRUE, 
        cmethod = "reghdfe")

m2=felm(total_budget_across_projects~treat_i+
          post_t:treat_i|
          action_date_year_quarter| # no fixed effects
          0| # no IV
          recipient_duns, # clustered at the contractor level
        data=contractor_quarter,
        exactDOF = TRUE, 
        cmethod = "reghdfe")

congestion_budget_table=stargazer(m1,m2,
          digits=2,
          digits.extra=2,
          title = "Contractor Project Budget and QuickPay reform",
          dep.var.labels="Total budget",
          dep.var.caption = "",
          covariate.labels =c("$Treat_i$",
                               "$Post_t$",
                               "$Treat_i \\times Post_t$",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(c("Time fixed effects",rep("No",1),rep("Yes",1))),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a contractor-quarter.",
                  "SEs are robust and clustered at the contractor level.",
                  "Sample restricted to contractors performing only one type of project."),
          header=F)


congestion_budget_table_tex=make_tex_pieces(congestion_budget_table)
# # Write to file
# write(congestion_budget_table_tex,
#       paste0(tables_folder,
#              "/congestion_budget_table.tex"))
```

## Number of tasks

### Contractors holding only small or only large projects

```{r tasks_0,warning=FALSE, echo=FALSE, results='asis'}

contractor_quarter=reg_df_one_type[,n_distinct(product_or_service_code),
                                   by=c('recipient_duns',
                                        'action_date_year_quarter')]
setnames(contractor_quarter,'V1','number_of_tasks')
contractor_quarter[,post_t:=ifelse(action_date_year_quarter>as.Date('2011-04-27'),1,0)]

contractor_quarter=merge(contractor_quarter,
                         unique(reg_df_one_type[,c('recipient_duns','treat_i')]),
                         by='recipient_duns')

contractor_quarter[,business_type:=ifelse(treat_i==1,"S","O")]

projects_plot=contractor_quarter[,mean(number_of_tasks),
                by=c('action_date_year_quarter','business_type')]

ggplot(projects_plot,
       aes(x=as.factor(action_date_year_quarter),
           y=V1,
           group=business_type))+
  geom_line(aes(linetype=business_type),alpha=0.7)+
  geom_point(aes(shape=business_type),size=1.5)+
  theme_minimal()+
  labs(x="Time", 
       y = "Average number of tasks per contractor")+
  scale_linetype_manual(name  ="",
                        breaks=c("S", 
                                 "O"),
                        labels=c("Treated","Control"),
                        values=c("solid","dashed"))+
  scale_shape_manual(name  ="",
                     breaks=c("S", 
                              "O"),
                     labels=c("Treated","Control"),
                     values=c(16,17))+
  theme(axis.text.x = element_text(angle = 90),
        axis.line = element_blank(),
        panel.border = element_rect(fill=NA),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.text = element_text(size=11),
        legend.position="bottom",
        legend.key.width=unit(2.5,"cm"))

m1=felm(number_of_tasks~treat_i+
          post_t:treat_i+post_t|
          0| # no fixed effects
          0| # no IV
          recipient_duns, # clustered at the contractor level
        data=contractor_quarter,
        exactDOF = TRUE, 
        cmethod = "reghdfe")

m2=felm(number_of_tasks~treat_i+
          post_t:treat_i|
          action_date_year_quarter| # no fixed effects
          0| # no IV
          recipient_duns, # clustered at the contractor level
        data=contractor_quarter,
        exactDOF = TRUE, 
        cmethod = "reghdfe")

congestion_tasks_table=stargazer(m1,m2,
          digits=2,
          digits.extra=2,
          title = "Contractor Project Tasks and QuickPay reform",
          dep.var.labels="Number of tasks",
          dep.var.caption = "",
          covariate.labels =c("$Treat_i$",
                               "$Post_t$",
                               "$Treat_i \\times Post_t$",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(c("Time fixed effects",rep("No",1),rep("Yes",1))),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a contractor-quarter.",
                  "SEs are robust and clustered at the contractor level.",
                  "Sample restricted to contractors performing only one type of project."),
          header=F)

congestion_tasks_table_tex=make_tex_pieces(congestion_tasks_table)
# # Write to file
# write(congestion_tasks_table_tex,
#       paste0(tables_folder,
#              "/congestion_tasks_table.tex"))
```

# Project portfolio: Spillover effect

## Regression 1: DID on large projects

* Sample restricted to large projects only.
* Treat is an indicator that equals one for LARGE projects that have at least one parallel small project in the same quarter, and is zero otherwise.
          
```{r project_portfolio_spillover,warning=FALSE, echo=FALSE, results='asis'}

reg_df[,treat_large_with_small:=case_when(
  treat_i==0&contractor_quarter%in%contractors_holding_both_large_and_small_projects~1,
  treat_i==0&contractor_quarter%in%contractors_holding_only_large_projects~0,
                                          treat_i==1~NaN)]
                                         

m1=felm(wins_percentage_delay~treat_large_with_small+
                            post_t:treat_large_with_small+
                            post_t|
                            0|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

m2=felm(wins_percentage_delay~treat_large_with_small+
                           log(wins_project_quarter_stage)+
                            post_t:treat_large_with_small+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received+
                            post_t|
                            0|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

m3=felm(wins_percentage_delay~treat_large_with_small+
                           log(wins_project_quarter_stage)+
                            post_t:treat_large_with_small+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

m4=felm(wins_percentage_delay~treat_large_with_small+
                           log(wins_project_quarter_stage)+
                            post_t:treat_large_with_small+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

m5=felm(wins_percentage_delay~treat_large_with_small+
                           log(wins_project_quarter_stage)+
                            post_t:treat_large_with_small+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

portfolio_large_projs_did=stargazer(m1,m2,m3,m4,m5,
          digits=2,
          digits.extra=2,
          title = "Project Portfolio and QuickPay reform",
          dep.var.labels="$PercentDelay_{it}$",
          dep.var.caption = "",
          covariate.labels =c("$Treat_i$",
                               "$Post_t$",
                               "$Treat_i \\times Post_t$",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-10pt",
          add.lines = list(
                           c("Duration, Budget, Bids",rep("No",1),rep("Yes",4)),
                           c("$Post_t \\times $  (Duration, Budget, Bids)",rep("No",1),rep("Yes",4)),                           c("Project stage",rep("No",1),rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:winsorized_initial_budget_i',
                   'post_t:number_of_offers_received',
                 'wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
           notes=c("Each observation is a project-quarter.",
                   "SEs are robust and clustered at the project level.",
                   "Sample restricted to large projects only."),
          #         "Treat is an indicator that equals one for LARGE projects that have at least one parallel small project in the same quarter, and is zero otherwise."),
          header=F)

# portfolio_large_projs_did_tex=make_tex_pieces(portfolio_large_projs_did)
# # Write to file
# write(portfolio_large_projs_did_tex,
#       paste0(tables_folder,
#              "/portfolio_large_projs_did.tex"))
```

## Regression 2: Incremental effect on small project with existing large project

* $Treat_{i,l}$ is an indicator that equals 1 for small projects with co-existing large projects in a given quarter, and is zero otherwise.
    * This depends on time, though we are not defining it explicitly.
* $Treat_{i,l}=1 \implies Treat_i = 1$. This means we have:
    * $Treat_{i,l} \times Post_t = Treat_i \times Treat_{i,l} \times Post_t$
    * $Treat_{i,l} \times Treat_i = Treat_{i,l}$
* Large projects with parallel small projects are removed to get a clean control group.

```{r project_portfolio_spillover_2, warning=FALSE, echo=FALSE, results='asis'}
# treat_small_with_large_new = 1 ==> treat_new = 1

m1=felm(wins_percentage_delay~treat_new+
          treat_small_with_large_new+
          treat_new:post_t+
          post_t:treat_small_with_large_new+
          post_t|
          0|
          0|
          contract_award_unique_key,
          data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

m2=felm(wins_percentage_delay~treat_new+
          treat_small_with_large_new+
          treat_new:post_t+
          post_t:treat_small_with_large_new+
          log(wins_project_quarter_stage)+
          log(1+winsorized_initial_duration_in_days_i)+
          log(1+winsorized_initial_budget_i)+
          number_of_offers_received+
          post_t:log(1+winsorized_initial_duration_in_days_i)+
          post_t:log(1+winsorized_initial_budget_i)+
          post_t:number_of_offers_received+
          post_t|
          0|
          0|
          contract_award_unique_key,
          data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

m3=felm(wins_percentage_delay~treat_new+
          treat_small_with_large_new+
          treat_new:post_t+
          post_t:treat_small_with_large_new+
          log(wins_project_quarter_stage)+
          log(1+winsorized_initial_duration_in_days_i)+
          log(1+winsorized_initial_budget_i)+
          number_of_offers_received+
          post_t:log(1+winsorized_initial_duration_in_days_i)+
          post_t:log(1+winsorized_initial_budget_i)+
          post_t:number_of_offers_received|
          action_date_year_quarter|
          0|
          contract_award_unique_key,
          data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

m4=felm(wins_percentage_delay~treat_new+
          treat_small_with_large_new+
          treat_new:post_t+
          post_t:treat_small_with_large_new+
          log(wins_project_quarter_stage)+
          log(1+winsorized_initial_duration_in_days_i)+
          log(1+winsorized_initial_budget_i)+
          number_of_offers_received+
          post_t:log(1+winsorized_initial_duration_in_days_i)+
          post_t:log(1+winsorized_initial_budget_i)+
          post_t:number_of_offers_received|
          product_or_service_code+action_date_year_quarter|
          0|
          contract_award_unique_key,
          data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

m5=felm(wins_percentage_delay~treat_new+
          treat_small_with_large_new+
          treat_new:post_t+
          post_t:treat_small_with_large_new+
          log(wins_project_quarter_stage)+
          log(1+winsorized_initial_duration_in_days_i)+
          log(1+winsorized_initial_budget_i)+
          number_of_offers_received+
          post_t:log(1+winsorized_initial_duration_in_days_i)+
          post_t:log(1+winsorized_initial_budget_i)+
          post_t:number_of_offers_received|
          naics_code+product_or_service_code+action_date_year_quarter|
          0|
          contract_award_unique_key,
          data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

portfolio_did=stargazer(m1,m2,m3,m4,m5,
          digits=2,
          digits.extra=2,
          title = "(Incremental effect) Project Portfolio and QuickPay reform",
          dep.var.labels="$PercentDelay_{it}$  ",
          dep.var.caption = "",
          covariate.labels =c("$Treat_i$",
                               "$Treat_{i,l}$",
                               "$Post_t$",
                               "$Treat_i \\times Post_t$",
                               "$Treat_{i,l} \\times Post_t$",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(
                           c("Duration, Budget, Bids",rep("No",1),rep("Yes",4)),
                           c("$Post_t \\times $  (Duration, Budget, Bids)",rep("No",1),rep("Yes",4)),                           c("Project stage",rep("No",1),rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:winsorized_initial_budget_i',
                   'post_t:number_of_offers_received',
                 'wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level.",
                  "Large projects with parallel small projects are removed."),
          header=F)


# portfolio_did_tex=make_tex_pieces(portfolio_did)
# # Write to file
# write(portfolio_did_tex,
#       paste0(tables_folder,
#              "/portfolio_did_tex.tex"))
```


## Regression 3: Total effect on small project with existing large project

* $Treat_{i,l}$ is an indicator that equals 1 for small projects with co-existing large projects, and is zero otherwise.
* $Treat_{i,s}$ is an indicator that equals 1 for small projects without co-existing large projects, and is zero otherwise.
* Large projects with parallel small projects are removed to get a clean control group.

```{r project_portfolio_spillover_3, warning=FALSE, echo=FALSE, results='asis'}
# treat_small_with_large_new = 1 ==> treat_new = 1

m1=felm(wins_percentage_delay~treat_only_small+
          treat_small_with_large_new+
          treat_only_small:post_t+
          post_t:treat_small_with_large_new+
          post_t|
          0|
          0|
          contract_award_unique_key,
          data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

m2=felm(wins_percentage_delay~treat_only_small+
          treat_small_with_large_new+
          treat_only_small:post_t+
          post_t:treat_small_with_large_new+
          log(wins_project_quarter_stage)+
          log(1+winsorized_initial_duration_in_days_i)+
          log(1+winsorized_initial_budget_i)+
          number_of_offers_received+
          post_t:log(1+winsorized_initial_duration_in_days_i)+
          post_t:log(1+winsorized_initial_budget_i)+
          post_t:number_of_offers_received+
          post_t|
          0|
          0|
          contract_award_unique_key,
          data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

m3=felm(wins_percentage_delay~treat_only_small+
          treat_small_with_large_new+
          treat_only_small:post_t+
          post_t:treat_small_with_large_new+
          log(wins_project_quarter_stage)+
          log(1+winsorized_initial_duration_in_days_i)+
          log(1+winsorized_initial_budget_i)+
          number_of_offers_received+
          post_t:log(1+winsorized_initial_duration_in_days_i)+
          post_t:log(1+winsorized_initial_budget_i)+
          post_t:number_of_offers_received|
          action_date_year_quarter|
          0|
          contract_award_unique_key,
          data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

m4=felm(wins_percentage_delay~treat_only_small+
          treat_small_with_large_new+
          treat_only_small:post_t+
          post_t:treat_small_with_large_new+
          log(wins_project_quarter_stage)+
          log(1+winsorized_initial_duration_in_days_i)+
          log(1+winsorized_initial_budget_i)+
          number_of_offers_received+
          post_t:log(1+winsorized_initial_duration_in_days_i)+
          post_t:log(1+winsorized_initial_budget_i)+
          post_t:number_of_offers_received|
          product_or_service_code+action_date_year_quarter|
          0|
          contract_award_unique_key,
          data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

m5=felm(wins_percentage_delay~treat_only_small+
          treat_small_with_large_new+
          treat_only_small:post_t+
          post_t:treat_small_with_large_new+
          log(wins_project_quarter_stage)+
          log(1+winsorized_initial_duration_in_days_i)+
          log(1+winsorized_initial_budget_i)+
          number_of_offers_received+
          post_t:log(1+winsorized_initial_duration_in_days_i)+
          post_t:log(1+winsorized_initial_budget_i)+
          post_t:number_of_offers_received|
          naics_code+product_or_service_code+action_date_year_quarter|
          0|
          contract_award_unique_key,
          data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

portfolio_did=stargazer(m1,m2,m3,m4,m5,
          digits=2,
          digits.extra=2,
          title = "(Total effect) Project Portfolio and QuickPay reform",
          dep.var.labels="$PercentDelay_{it}$  ",
          dep.var.caption = "",
          covariate.labels =c("$Treat_{i,s}$",
                               "$Treat_{i,l}$",
                               "$Post_t$",
                               "$Treat_{i,s} \\times Post_t$",
                               "$Treat_{i,l} \\times Post_t$",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(
                           c("Duration, Budget, Bids",rep("No",1),rep("Yes",4)),
                           c("$Post_t \\times $  (Duration, Budget, Bids)",rep("No",1),rep("Yes",4)),                           c("Project stage",rep("No",1),rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:winsorized_initial_budget_i',
                   'post_t:number_of_offers_received',
                 'wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level.",
                  "Large projects with parallel small projects are removed."),
          header=F)


# portfolio_did_tex=make_tex_pieces(portfolio_did)
# # Write to file
# write(portfolio_did_tex,
#       paste0(tables_folder,
#              "/portfolio_did_tex.tex"))
```

# Project Stage

* $t$ indicates the end of the quarter
* We want to get stage of the project at the beginning of a given quarter (before any delays materialize)

$Stage_{it}=\frac{ActionDate_{t-1}-StartDate_i}{Duration_{i,t-1}}$
$Stage_{it}=\frac{(t-1)-StartDate_i}{Duration_{i,t-1}}$

## Stage Quintile

```{r stage_quintile, eval=FALSE,  echo=FALSE, results='asis'}

reg_df_subset[,stage_quintile:=ntile(project_quarter_stage,5)]

df_main=data.frame()
for(i in 1:length(unique(reg_df_subset$stage_quintile))){
#  print(i)
  tryCatch({
  a=tidy(felm(wins_percentage_delay~treat_new+
                treat_new:post_t+
                log(1+winsorized_initial_duration_in_days_i)+
                log(1+winsorized_initial_budget_i)+
                number_of_offers_received+
                post_t:log(1+winsorized_initial_duration_in_days_i)+
                post_t:log(1+winsorized_initial_budget_i)+
                post_t:number_of_offers_received|
                naics_code+product_or_service_code+action_date_year_quarter|
                0|
                contract_award_unique_key,
              data=subset(reg_df_subset,project_quarter_stage<=1 &
                            stage_quintile==i),
              exactDOF = TRUE, 
              cmethod = "reghdfe"),
              conf.int=T)
    a=subset(a,term=='treat_new:post_t')
    a['Project stage quintile']=i
    assign(paste0("df", i), value = a)
    df_main=rbind(df_main,get(paste0("df", i)))}, error=function(e){})
}

setDT(df_main)[,`Project stage quintile`:=as.factor(`Project stage quintile`)]

#df_main[,color:=ifelse(p.value<=0.1,"black","dark grey")]

df_main[,color:="black"]

# Instead of having a zero line, show gray as p.value>0.1 & black as p.value<0.1
ggplot(df_main,
       aes(x=`Project stage quintile`,y=estimate,group=1))+
  geom_point(size=1,alpha=0.7,color=df_main$color)+
 # geom_line(alpha=0.7,size=0.25)+
  geom_errorbar(aes(ymin = conf.low, 
                    ymax = conf.high),
                width=0.05,
                size=0.25,
                alpha=0.7,
                color=df_main$color)+
  geom_hline(yintercept =0,alpha=0.6,size=0.15)+
  theme_minimal()+ 
  theme(panel.border = element_rect(color="black",fill=NA), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5))+
  theme(legend.position="bottom")+
  ylab("Point estimate \n (Percentage Delay Rate)")+ 
  coord_fixed(ratio=0.5)

# ggsave(path=figures_folder,
#        width = 8,
#        height = 5,
#        bg="white",
#        filename = "stage_quintiles.png")

min_value=subset(reg_df_subset,project_quarter_stage>=0 & project_quarter_stage<=1 & !is.na(project_quarter_stage))[,round(min(project_quarter_stage),2),by=stage_quintile][order(stage_quintile)]

setnames(min_value,'V1','Min stage')


max_value=subset(reg_df_subset,project_quarter_stage>=0 & project_quarter_stage<=1 & !is.na(project_quarter_stage))[,round(max(project_quarter_stage),2),by=stage_quintile][order(stage_quintile)]

setnames(max_value,'V1','Max stage')

stats_stage=merge(min_value,max_value,by='stage_quintile')
print(stats_stage)
```

## Logged Stage Regressions

```{r stage_regs_log, warning=FALSE, echo=FALSE, results='asis'}

m1=felm(wins_percentage_delay~treat_new+
          log(wins_project_quarter_stage)+
          post_t:treat_new+
          treat_new:log(wins_project_quarter_stage)+
          post_t:log(wins_project_quarter_stage)+
          post_t:treat_new:log(wins_project_quarter_stage)+
          post_t|
          0| # no fixed effects
          0| # no IV
          contract_award_unique_key, # clustered at project level
        data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

m2=felm(wins_percentage_delay~treat_new+
          log(wins_project_quarter_stage)+
          post_t:treat_new+
          treat_new:log(wins_project_quarter_stage)+
          post_t:log(wins_project_quarter_stage)+
          post_t:treat_new:log(wins_project_quarter_stage)+
          number_of_offers_received+
          log(1+winsorized_initial_budget_i)+
          log(1+winsorized_initial_duration_in_days_i)+
          post_t:log(1+winsorized_initial_budget_i)+
          post_t:log(1+winsorized_initial_duration_in_days_i)+
          post_t:number_of_offers_received+
          post_t|
          0| # no fixed effects
          0| # no IV
          contract_award_unique_key, # clustered at project level
        data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

m3=felm(wins_percentage_delay~treat_new+
          log(wins_project_quarter_stage)+
          post_t:treat_new+
          treat_new:log(wins_project_quarter_stage)+
          post_t:log(wins_project_quarter_stage)+
          post_t:treat_new:log(wins_project_quarter_stage)+
          number_of_offers_received+
          log(1+winsorized_initial_budget_i)+
          log(1+winsorized_initial_duration_in_days_i)+
          post_t:log(1+winsorized_initial_budget_i)+
          post_t:log(1+winsorized_initial_duration_in_days_i)+
          post_t:number_of_offers_received|
          action_date_year_quarter| # no fixed effects
          0| # no IV
          contract_award_unique_key, # clustered at project level
        data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

m4=felm(wins_percentage_delay~treat_new+
          log(wins_project_quarter_stage)+
          post_t:treat_new+
          treat_new:log(wins_project_quarter_stage)+
          post_t:log(wins_project_quarter_stage)+
          post_t:treat_new:log(wins_project_quarter_stage)+
          number_of_offers_received+
          log(1+winsorized_initial_budget_i)+
          log(1+winsorized_initial_duration_in_days_i)+
          post_t:log(1+winsorized_initial_budget_i)+
          post_t:log(1+winsorized_initial_duration_in_days_i)+
          post_t:number_of_offers_received|
          product_or_service_code+action_date_year_quarter| # no fixed effects
          0| # no IV
          contract_award_unique_key, # clustered at project level
        data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

m5=felm(wins_percentage_delay~treat_new+
          log(wins_project_quarter_stage)+
          post_t:treat_new+
          treat_new:log(wins_project_quarter_stage)+
          post_t:log(wins_project_quarter_stage)+
          post_t:treat_new:log(wins_project_quarter_stage)+
          number_of_offers_received+
          log(1+winsorized_initial_budget_i)+
          log(1+winsorized_initial_duration_in_days_i)+
          post_t:log(1+winsorized_initial_budget_i)+
          post_t:log(1+winsorized_initial_duration_in_days_i)+
          post_t:number_of_offers_received|
          product_or_service_code+naics_code+action_date_year_quarter| # no fixed effects
          0| # no IV
          contract_award_unique_key, # clustered at project level
        data=reg_df_subset,
        exactDOF = TRUE,
        cmethod = "reghdfe")

stage_log_regs=stargazer(m1,m2,m3,m4,m5,
          digits=2,
          digits.extra=2,
          title = "Project Stage and QuickPay reform",
          dep.var.labels="$PercentDelay_{it}$  ",
          dep.var.caption = "",
          covariate.labels = c("$Treat_i$",
                               "Log(Stage)",
                               "$Post_t$",
                                "$Treat_i \\times Post_t$",
                               "$Treat_i \\times$ Log(Stage)",
                               "$Post_t \\times$ Log(Stage)",
                               "$Treat_i \\times Post_t \\times$ Log(Stage)",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(
                           c("Duration, Budget, Bids",rep("No",1),rep("Yes",4)),
                           c("$Post_t \\times $  (Duration, Budget, Bids)",rep("No",1),rep("Yes",4)),                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:winsorized_initial_budget_i',
                   'post_t:number_of_offers_received'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level."),
          header=F)
# 
# stage_table_tex=make_tex_pieces(stage_log_regs)
# # Write to file
# write(stage_table_tex,
#       paste0(tables_folder,"/stage_table_tex.tex"))

```

# Contract Financing (Projects active on/before June 2010)

* $CF=1$ if project was receiving contract financing 
* Sample restricted to projects that started on or before June 2010
* Jobs act was launched in Sept 2010

```{r cf_3, echo=FALSE, results='asis'}

# Baseline Regressions 
baseline_reg=felm(wins_percentage_delay~treat_new+
                    post_t:treat_new+
                     post_t+
                    contract_financing_i+
                    post_t:contract_financing_i+
                    treat_new:contract_financing_i+
                    post_t:treat_new:contract_financing_i|
                    0| # no fixed effects
                    0| # no IV
                    contract_award_unique_key, # clustered at project level
                  data=subset(reg_df_subset,initial_start_date<=as.Date('2010-06-30')), 
                  exactDOF = TRUE, 
                  cmethod = "reghdfe")

controls_and_no_fe=felm(wins_percentage_delay~treat_new+
                            post_t+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            treat_new:contract_financing_i+
                            contract_financing_i+
                            post_t:contract_financing_i+
                            post_t:treat_new:contract_financing_i+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            0|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,initial_start_date<=as.Date('2010-06-30')), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_time_fe=felm(wins_percentage_delay~treat_new+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            contract_financing_i+ 
                            treat_new:contract_financing_i+
                            post_t:contract_financing_i+
                            post_t:treat_new:contract_financing_i+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,initial_start_date<=as.Date('2010-06-30')), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
# time fixed effects also included in the following specs
controls_time_task_fe=felm(wins_percentage_delay~treat_new+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            contract_financing_i+
                             treat_new:contract_financing_i+
                            post_t:contract_financing_i+
                            post_t:treat_new:contract_financing_i+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,initial_start_date<=as.Date('2010-06-30')), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_all_fe=felm(wins_percentage_delay~treat_new+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            contract_financing_i+
                           treat_new:contract_financing_i+
                            post_t:contract_financing_i+
                            post_t:treat_new:contract_financing_i+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,initial_start_date<=as.Date('2010-06-30')), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
contract_financing_table=stargazer(baseline_reg,
          controls_and_no_fe,
          controls_and_time_fe,
          controls_time_task_fe,
          controls_and_all_fe,
          digits=2,
          digits.extra=2,
          title = "Contract Financing and QuickPay reform",
          dep.var.labels="$PercentDelay_{it}$  ",
          dep.var.caption = "",
          covariate.labels =c("$Treat_i$",
                               "$Post_t$",
                               "$CF_i$",
                               "$Treat_i \\times Post_t$",
                               "$Post_t \\times CF_i$",
                               "$Treat_i \\times CF_i$",
                               "$Treat_i \\times Post_t \\times CF_i$",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(
                           c("Duration, Budget, Bids",rep("No",1),rep("Yes",4)),
                           c("$Post_t \\times $  (Duration, Budget, Bids)",rep("No",1),rep("Yes",4)),                           c("Project stage",rep("No",1),rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:winsorized_initial_budget_i',
                   'post_t:number_of_offers_received',
                 'wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level."),
          header=F)

# contract_financing_tex=make_tex_pieces(contract_financing_table)
# # Write to file
# write(contract_financing_tex,
#       paste0(tables_folder,"/contract_financing_table.tex"))

```

# Contract Financing (All Projects)

* $CF=1$ if project was receiving contract financing 

```{r cf_3_full_sample, echo=FALSE, results='asis'}

# Baseline Regressions 
baseline_reg=felm(wins_percentage_delay~treat_new+
                    post_t:treat_new+
                     post_t+
                    contract_financing_i+
                    post_t:contract_financing_i+
                    treat_new:contract_financing_i+
                    post_t:treat_new:contract_financing_i|
                    0| # no fixed effects
                    0| # no IV
                    contract_award_unique_key, # clustered at project level
                  data=reg_df_subset, 
                  exactDOF = TRUE, 
                  cmethod = "reghdfe")

controls_and_no_fe=felm(wins_percentage_delay~treat_new+
                            post_t+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            treat_new:contract_financing_i+
                            contract_financing_i+
                            post_t:contract_financing_i+
                            post_t:treat_new:contract_financing_i+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            0|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_time_fe=felm(wins_percentage_delay~treat_new+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            contract_financing_i+ 
                            treat_new:contract_financing_i+
                            post_t:contract_financing_i+
                            post_t:treat_new:contract_financing_i+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
# time fixed effects also included in the following specs
controls_time_task_fe=felm(wins_percentage_delay~treat_new+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            contract_financing_i+
                             treat_new:contract_financing_i+
                            post_t:contract_financing_i+
                            post_t:treat_new:contract_financing_i+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_all_fe=felm(wins_percentage_delay~treat_new+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            contract_financing_i+
                           treat_new:contract_financing_i+
                            post_t:contract_financing_i+
                            post_t:treat_new:contract_financing_i+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
contract_financing_table=stargazer(baseline_reg,
          controls_and_no_fe,
          controls_and_time_fe,
          controls_time_task_fe,
          controls_and_all_fe,
          digits=2,
          digits.extra=2,
          title = "Contract Financing (All Projects) and QuickPay reform",
          dep.var.labels="$PercentDelay_{it}$  ",
          dep.var.caption = "",
          covariate.labels =c("$Treat_i$",
                               "$Post_t$",
                               "$CF_i$",
                               "$Treat_i \\times Post_t$",
                               "$Post_t \\times CF_i$",
                               "$Treat_i \\times CF_i$",
                               "$Treat_i \\times Post_t \\times CF_i$",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(
                           c("Duration, Budget, Bids",rep("No",1),rep("Yes",4)),
                           c("$Post_t \\times $  (Duration, Budget, Bids)",rep("No",1),rep("Yes",4)),                           c("Project stage",rep("No",1),rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:winsorized_initial_budget_i',
                   'post_t:number_of_offers_received',
                 'wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level."),
          header=F)

```

# Receives Grants/Financial Assistance (Projects active on/before June 2010)

* $CF=1$ if receives_grants=='t'
* The variable "receives_grants" used to be called "receives financial assistance"

```{r receives_grants_2, echo=FALSE, results='asis'}
# Baseline Regressions 
baseline_reg=felm(wins_percentage_delay~treat_new+
                    post_t:treat_new+
                     post_t+
                    receives_financial_assistance+
                    post_t:receives_financial_assistance+
                    treat_new:receives_financial_assistance+
                    post_t:treat_new:receives_financial_assistance|
                    0| # no fixed effects
                    0| # no IV
                    contract_award_unique_key, # clustered at project level
                  data=subset(reg_df_subset,initial_start_date<=as.Date('2010-06-30')), 
                  exactDOF = TRUE, 
                  cmethod = "reghdfe")

controls_and_no_fe=felm(wins_percentage_delay~treat_new+
                            post_t+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            treat_new:receives_financial_assistance+
                            receives_financial_assistance+
                            post_t:receives_financial_assistance+
                            post_t:treat_new:receives_financial_assistance+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            0|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,initial_start_date<=as.Date('2010-06-30')), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_time_fe=felm(wins_percentage_delay~treat_new+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            receives_financial_assistance+ 
                            treat_new:receives_financial_assistance+
                            post_t:receives_financial_assistance+
                            post_t:treat_new:receives_financial_assistance+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,initial_start_date<=as.Date('2010-06-30')), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
# time fixed effects also included in the following specs
controls_time_task_fe=felm(wins_percentage_delay~treat_new+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            receives_financial_assistance+
                             treat_new:receives_financial_assistance+
                            post_t:receives_financial_assistance+
                            post_t:treat_new:receives_financial_assistance+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,initial_start_date<=as.Date('2010-06-30')), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_all_fe=felm(wins_percentage_delay~treat_new+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            receives_financial_assistance+
                           treat_new:receives_financial_assistance+
                            post_t:receives_financial_assistance+
                            post_t:treat_new:receives_financial_assistance+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,initial_start_date<=as.Date('2010-06-30')), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
financial_assistance_table=stargazer(baseline_reg,
          controls_and_no_fe,
          controls_and_time_fe,
          controls_time_task_fe,
          controls_and_all_fe,
          digits=2,
          digits.extra=2,
          title = "Receives grants and QuickPay reform",
          dep.var.labels="$PercentDelay_{it}$  ",
          dep.var.caption = "",
          covariate.labels =c("$Treat_i$",
                               "$Post_t$",
                               "$CF_i$",
                               "$Treat_i \\times Post_t$",
                               "$Post_t \\times CF_i$",
                               "$Treat_i \\times CF_i$",
                               "$Treat_i \\times Post_t \\times CF_i$",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(
                           c("Duration, Budget, Bids",rep("No",1),rep("Yes",4)),
                           c("$Post_t \\times $  (Duration, Budget, Bids)",rep("No",1),rep("Yes",4)),                           c("Project stage",rep("No",1),rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:winsorized_initial_budget_i',
                   'post_t:number_of_offers_received',
                 'wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level."),
          header=F)
# 
# financial_assistance_tex=make_tex_pieces(financial_assistance_table)
# # Write to file
# write(financial_assistance_tex,
#       paste0(tables_folder,"/financial_assistance_table_pre_qp.tex"))

```

# Receives Grants/Financial Assistance (All projects)

* $CF=1$ if receives_grants=='t'
* The variable "receives_grants" used to be called "receives financial assistance"

```{r receives_grants_2_all_projects, echo=FALSE, results='asis'}
# Baseline Regressions 
baseline_reg=felm(wins_percentage_delay~treat_new+
                    post_t:treat_new+
                     post_t+
                    receives_financial_assistance+
                    post_t:receives_financial_assistance+
                    treat_new:receives_financial_assistance+
                    post_t:treat_new:receives_financial_assistance|
                    0| # no fixed effects
                    0| # no IV
                    contract_award_unique_key, # clustered at project level
                  data=reg_df_subset, 
                  exactDOF = TRUE, 
                  cmethod = "reghdfe")

controls_and_no_fe=felm(wins_percentage_delay~treat_new+
                            post_t+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            treat_new:receives_financial_assistance+
                            receives_financial_assistance+
                            post_t:receives_financial_assistance+
                            post_t:treat_new:receives_financial_assistance+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            0|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_time_fe=felm(wins_percentage_delay~treat_new+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            receives_financial_assistance+ 
                            treat_new:receives_financial_assistance+
                            post_t:receives_financial_assistance+
                            post_t:treat_new:receives_financial_assistance+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
# time fixed effects also included in the following specs
controls_time_task_fe=felm(wins_percentage_delay~treat_new+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            receives_financial_assistance+
                             treat_new:receives_financial_assistance+
                            post_t:receives_financial_assistance+
                            post_t:treat_new:receives_financial_assistance+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_all_fe=felm(wins_percentage_delay~treat_new+
                           log(wins_project_quarter_stage)+
                            post_t:treat_new+
                            receives_financial_assistance+
                           treat_new:receives_financial_assistance+
                            post_t:receives_financial_assistance+
                            post_t:treat_new:receives_financial_assistance+
                            log(1+winsorized_initial_duration_in_days_i)+
                            log(1+winsorized_initial_budget_i)+
                            number_of_offers_received+
                            post_t:log(1+winsorized_initial_duration_in_days_i)+
                            post_t:log(1+winsorized_initial_budget_i)+
                            post_t:number_of_offers_received|
                            naics_code+product_or_service_code+action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=reg_df_subset, 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
financial_assistance_table=stargazer(baseline_reg,
          controls_and_no_fe,
          controls_and_time_fe,
          controls_time_task_fe,
          controls_and_all_fe,
          digits=2,
          digits.extra=2,
          title = "Receives grants (All Projects) and QuickPay reform",
          dep.var.labels="$PercentDelay_{it}$  ",
          dep.var.caption = "",
          covariate.labels =c("$Treat_i$",
                               "$Post_t$",
                               "$CF_i$",
                               "$Treat_i \\times Post_t$",
                               "$Post_t \\times CF_i$",
                               "$Treat_i \\times CF_i$",
                               "$Treat_i \\times Post_t \\times CF_i$",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(
                           c("Duration, Budget, Bids",rep("No",1),rep("Yes",4)),
                           c("$Post_t \\times $  (Duration, Budget, Bids)",rep("No",1),rep("Yes",4)),                           c("Project stage",rep("No",1),rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('winsorized_initial_duration_in_days_i',
                  'winsorized_initial_budget_i',
                   'number_of_offers_received',
                   'post_t:winsorized_initial_duration_in_days_i',
                   'post_t:winsorized_initial_budget_i',
                   'post_t:number_of_offers_received',
                 'wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level."),
          header=F)

```

# Competition

## Impact on bidding metrics [All projects]

```{r competition_bids, echo=FALSE, results='asis'}

select_cols_comp=c("contract_award_unique_key",
              "number_of_offers_received",
              "competitively_awarded_i",
              "other_than_full_and_open_competition_code",
              "initial_duration_in_days_i",
              "base_and_all_options_value",
              "naics_code",
              "action_date",
              "contracting_officers_determination_of_business_size_code",
              "product_or_service_code",
              "recipient_duns")

reg_df_first_reported=subset(df_first_reported, action_date<=as.Date('2012-06-30'))[,..select_cols_comp]
                            
reg_df_first_reported[,action_date_year_quarter:=as.Date(as.yearqtr(as.Date(action_date)),
                                                       frac = 1)]

setnames(reg_df_first_reported,'action_date_year_quarter','quarter_when_project_signed')
# defining as project_signed_after_quickpay to avoid clash with post_t variable later
# these are essentially the same, but defined on different samples 

reg_df_first_reported[,project_signed_after_quickpay:=
          ifelse(quarter_when_project_signed>=as.Date('2011-04-27'),1,0)]

reg_df_first_reported[,treat_i:=
          ifelse(contracting_officers_determination_of_business_size_code=="S",1,0)]

reg_df_first_reported[,winsorized_initial_duration_in_days_i:=
          Winsorize(initial_duration_in_days_i,
                    probs=c(0.05,0.95),
                    na.rm=T)]

reg_df_first_reported[,winsorized_initial_budget_i:=
          Winsorize(base_and_all_options_value,
                    probs=c(0.05,0.95),
                    na.rm=T)]

bids=felm(number_of_offers_received~treat_i+
                                  treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_first_reported,
                                      competitively_awarded_i==1),
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

duration=felm(winsorized_initial_duration_in_days_i~treat_i+
                                  treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_first_reported,
                                      competitively_awarded_i==1), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

budget=felm(winsorized_initial_budget_i~treat_i+
                                 treat_i:project_signed_after_quickpay|
                            product_or_service_code+
                            quarter_when_project_signed|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_first_reported,
                                      competitively_awarded_i==1), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")

bidding_metrics_table=stargazer(bids,
          duration,
          budget,
          digits=2,
          digits.extra=2,
          title = "Effect of Competition After QuickPay: Quickpay 2009-2011",
          dep.var.labels=c("$NumberOfBids_{it}$",
                           "$InitialDuration_{it}$",
                           "$InitialBudget_{it}$"),
          dep.var.caption = "",
          covariate.labels = c("$Treat_i$",
                               "$Treat_i \\times Post_t$"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "0pt",
          add.lines = list(c("Task fixed effects",rep("Yes",3)),
                           c("Time fixed effects",rep("Yes",3))),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level.",
                  "Sample restricted to fully competed projects."),
          header=F)
# 
# bidding_metrics_table_tex=make_tex_pieces(bidding_metrics_table)
# # Write to file
# write(bidding_metrics_table_tex,
#       paste0(tables_folder,"/bidding_metrics_table.tex"))

```

## Impact on delays

### Subsample model II

Define
$$ SA_i = \begin{cases} 1, \text{ if project was signed after QuickPay}\\
0, \text{ otherwise} \end{cases}$$

$$ SB_i = \begin{cases} 1, \text{ if project was signed before QuickPay}\\
0, \text{ otherwise} \end{cases}$$
 

```{r competition_delays_subsample, echo=FALSE, results='asis'}
reg_df_subset[,project_signed_after_quickpay:=case_when(initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter>=as.Date('2011-04-27')~1,
                                                 initial_start_date<as.Date('2011-04-27') ~ 0,
                                                 initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter<as.Date('2011-04-27')~NaN)]

reg_df_subset[,project_signed_before_quickpay:=case_when(initial_start_date<as.Date('2011-04-27') ~1,
                                                 initial_start_date>=as.Date('2011-04-27') ~0)]
```

```{r competition_subsample_ii, echo=FALSE, results='asis'}

baseline_reg=felm(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                                  post_t|
                                  0| # no fixed effects
                                  0| # no IV
                                  contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df_subset,competitively_awarded_i==1),
                                  exactDOF = TRUE,
                                  cmethod = "reghdfe")
controls_and_no_fe=felm(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                                  post_t+
                            log(wins_project_quarter_stage)|
                            0|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,competitively_awarded_i==1), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_time_fe=felm(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,competitively_awarded_i==1), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_time_task_fe=felm(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            product_or_service_code+
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,competitively_awarded_i==1), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_all_fe=felm(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            naics_code+
                            product_or_service_code+
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,competitively_awarded_i==1), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
competitive_projects_table_ii=stargazer(baseline_reg,
          controls_and_no_fe,
          controls_and_time_fe,
          controls_time_task_fe,
          controls_and_all_fe,
          digits=2,
          digits.extra=2,
          title = "Effect of QuickPay on competitively awarded projects",
          dep.var.labels="$PercentDelay_{it}$  ",
          dep.var.caption = "",
          covariate.labels = c("$Treat_i$",
                               "$SA_i$",
                               "$Post_t$",
                               "$Treat_i \\times Post_t$",
                               "$Treat_i \\times Post_t \\times SA_i $",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(
                           c("Project stage",rep("No",1),rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level.",
                  "Sample restricted to fully competed projects."),
          header=F)

# competitive_projects_tex_ii=make_tex_pieces(competitive_projects_table_ii)
# # Write to file
# write(competitive_projects_tex_ii,
#       paste0(tables_folder,"/competitive_projects_table_2.tex"))
```

```{r non_competition_subsample_ii, echo=FALSE, results='asis'}

baseline_reg=felm(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                                  post_t|
                                  0| # no fixed effects
                                  0| # no IV
                                  contract_award_unique_key, # clustered at project level
                                  data=subset(reg_df_subset,competitively_awarded_i==0),
                                  exactDOF = TRUE,
                                  cmethod = "reghdfe")
controls_and_no_fe=felm(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                                  post_t+
                            log(wins_project_quarter_stage)|
                            0|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,competitively_awarded_i==0), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_time_fe=felm(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,competitively_awarded_i==0), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_time_task_fe=felm(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            product_or_service_code+
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,competitively_awarded_i==0), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
controls_and_all_fe=felm(wins_percentage_delay~treat_new+
                                  project_signed_after_quickpay+
                                  treat_new:post_t+
                                  treat_new:post_t:project_signed_after_quickpay+
                            log(wins_project_quarter_stage)|
                            naics_code+
                            product_or_service_code+
                            action_date_year_quarter|
                            0|
                            contract_award_unique_key,
                          data=subset(reg_df_subset,competitively_awarded_i==0), 
                          exactDOF = TRUE, 
                          cmethod = "reghdfe")
non_competitive_projects_table_ii=stargazer(baseline_reg,
          controls_and_no_fe,
          controls_and_time_fe,
          controls_time_task_fe,
          controls_and_all_fe,
          digits=2,
          digits.extra=2,
          title = "Effect of QuickPay on non-competitively awarded projects",
          dep.var.labels="$PercentDelay_{it}$  ",
          dep.var.caption = "",
          covariate.labels = c("$Treat_i$",
                               "$SA_i$",
                               "$Post_t$",
                               "$Treat_i \\times Post_t$",
                               "$Treat_i \\times Post_t \\times SA_i $",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-2pt",
          add.lines = list(
                           c("Project stage",rep("No",1),rep("Yes",4)),
                           c("Time fixed effects",rep("No",2),rep("Yes",3)),
                           c("Task fixed effects",rep("No",3),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",4),rep("Yes",1))),
          omit=c('wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level.",
                  "Sample restricted to non-competed projects."),
          header=F)
# 
# non_competitive_projects_tex_ii=make_tex_pieces(non_competitive_projects_table_ii)
# # Write to file
# write(non_competitive_projects_tex_ii,
#       paste0(tables_folder,"/non_competitive_projects_table_2.tex"))

```

### Four-way interaction

We run the following model:

$$\begin{aligned} PercentDelay_{it} &=& \beta_0 +\beta_1 Treat_i+ \beta_2 StartedAfterQP_i+ \beta_3 Post_t+ \beta_4 Competitive_i\\ && +  \beta_5 (Treat_i \times Competitive_i) + \beta_6 (Post_t \times Competitive_i)\\ && +  \beta_7 (StartedAfterQP_i \times Competitive_i) +\beta_8 (Treat_i \times Post_t)\\ && + \beta_9 (Treat_i \times Post_t \times Competitive_i) \\ && + \beta_{10} (Treat_i \times Post_t \times StartedAfterQP_i )\\ && + \beta_{11} (Treat_i \times Post_t \times StartedAfterQP_i \times Competitive_i) + e_{it} \end{aligned}$$

**Interpretation:**

* $\beta_9$ is the difference between treatment effect for competitive and non-competitive projects signed before quickpay.
* $\beta_9 + \beta_{11}$ is the difference between treatment effect for competitive and non-competitive projects signed *after* quickpay.
* $\beta_{11}$ is our coefficient of interest because it tells us how much of the difference is there due to "aggressive bidding" after the policy.

```{r competition_delays_combined, echo= FALSE, results ='asis'}
baseline_reg=felm(wins_percentage_delay~treat_new+
                                   project_signed_after_quickpay+
                                   competitively_awarded_i+
                     treat_new:competitively_awarded_i+
                     post_t:competitively_awarded_i+
                     project_signed_after_quickpay:competitively_awarded_i+
                     treat_new:post_t+
                     treat_new:post_t:competitively_awarded_i+
                     treat_new:post_t:project_signed_after_quickpay+
                     treat_new:post_t:project_signed_after_quickpay:competitively_awarded_i+
                     post_t|
                                   0| # no fixed effects
                                   0| # no IV
                                   contract_award_unique_key, # clustered at project level
                                   data=reg_df_subset,
                                   exactDOF = TRUE,
                                   cmethod = "reghdfe")
controls_and_no_fe_no_age=felm(wins_percentage_delay~treat_new+
                                   project_signed_after_quickpay+
                                   competitively_awarded_i+
                     treat_new:competitively_awarded_i+
                     post_t:competitively_awarded_i+
                     project_signed_after_quickpay:competitively_awarded_i+
                     treat_new:post_t+
                     treat_new:post_t:competitively_awarded_i+
                     treat_new:post_t:project_signed_after_quickpay+
                     treat_new:post_t:project_signed_after_quickpay:competitively_awarded_i+
                            # log(1+winsorized_initial_duration_in_days_i)+
                            # log(1+winsorized_initial_budget_i)+
                            # number_of_offers_received+
                            # post_t:number_of_offers_received+
                            # post_t:log(1+winsorized_initial_duration_in_days_i)+
                            # post_t:log(1+winsorized_initial_budget_i)+
                     post_t|
                                   0| # no fixed effects
                                   0| # no IV
                                   contract_award_unique_key, # clustered at project level
                                   data=reg_df_subset,
                                   exactDOF = TRUE,
                                   cmethod = "reghdfe")
controls_and_no_fe=felm(wins_percentage_delay~treat_new+
                                   project_signed_after_quickpay+
                                   competitively_awarded_i+
                     treat_new:competitively_awarded_i+
                     post_t:competitively_awarded_i+
                     project_signed_after_quickpay:competitively_awarded_i+
                     treat_new:post_t+
                     treat_new:post_t:competitively_awarded_i+
                     treat_new:post_t:project_signed_after_quickpay+
                     treat_new:post_t:project_signed_after_quickpay:competitively_awarded_i+
                     post_t+
                            # log(1+winsorized_initial_duration_in_days_i)+
                            # log(1+winsorized_initial_budget_i)+
                            # number_of_offers_received+
                            # post_t:number_of_offers_received+
                            # post_t:log(1+winsorized_initial_duration_in_days_i)+
                            # post_t:log(1+winsorized_initial_budget_i)+
                            log(wins_project_quarter_stage)|
                                   0| # no fixed effects
                                   0| # no IV
                                   contract_award_unique_key, # clustered at project level
                                   data=reg_df_subset,
                                   exactDOF = TRUE,
                                   cmethod = "reghdfe")
controls_and_time_fe=felm(wins_percentage_delay~treat_new+
                                   project_signed_after_quickpay+
                                   competitively_awarded_i+
                     treat_new:competitively_awarded_i+
                     post_t:competitively_awarded_i+
                     project_signed_after_quickpay:competitively_awarded_i+
                     treat_new:post_t+
                     treat_new:post_t:competitively_awarded_i+
                     treat_new:post_t:project_signed_after_quickpay+
                     treat_new:post_t:project_signed_after_quickpay:competitively_awarded_i+
                            # log(1+winsorized_initial_duration_in_days_i)+
                            # log(1+winsorized_initial_budget_i)+
                            # number_of_offers_received+
                            # post_t:number_of_offers_received+
                            # post_t:log(1+winsorized_initial_duration_in_days_i)+
                            # post_t:log(1+winsorized_initial_budget_i)+
                            log(wins_project_quarter_stage)|
                                   action_date_year_quarter| # no fixed effects
                                   0| # no IV
                                   contract_award_unique_key, # clustered at project level
                                   data=reg_df_subset,
                                   exactDOF = TRUE,
                                   cmethod = "reghdfe")
controls_time_task_fe=felm(wins_percentage_delay~treat_new+
                                   project_signed_after_quickpay+
                                   competitively_awarded_i+
                     treat_new:competitively_awarded_i+
                     post_t:competitively_awarded_i+
                     project_signed_after_quickpay:competitively_awarded_i+
                     treat_new:post_t+
                     treat_new:post_t:competitively_awarded_i+
                     treat_new:post_t:project_signed_after_quickpay+
                     treat_new:post_t:project_signed_after_quickpay:competitively_awarded_i+
                            # log(1+winsorized_initial_duration_in_days_i)+
                            # log(1+winsorized_initial_budget_i)+
                            # number_of_offers_received+
                            # post_t:number_of_offers_received+
                            # post_t:log(1+winsorized_initial_duration_in_days_i)+
                            # post_t:log(1+winsorized_initial_budget_i)+
                            log(wins_project_quarter_stage)|
                                   action_date_year_quarter+
                       product_or_service_code| # no fixed effects
                                   0| # no IV
                                   contract_award_unique_key, # clustered at project level
                                   data=reg_df_subset,
                                   exactDOF = TRUE,
                                   cmethod = "reghdfe")
controls_and_all_fe=felm(wins_percentage_delay~treat_new+
                                   project_signed_after_quickpay+
                                   competitively_awarded_i+
                     treat_new:competitively_awarded_i+
                     post_t:competitively_awarded_i+
                     project_signed_after_quickpay:competitively_awarded_i+
                     treat_new:post_t+
                     treat_new:post_t:competitively_awarded_i+
                     treat_new:post_t:project_signed_after_quickpay+
                     treat_new:post_t:project_signed_after_quickpay:competitively_awarded_i+
                            # log(1+winsorized_initial_duration_in_days_i)+
                            # log(1+winsorized_initial_budget_i)+
                            # number_of_offers_received+
                            # post_t:number_of_offers_received+
                            # post_t:log(1+winsorized_initial_duration_in_days_i)+
                            # post_t:log(1+winsorized_initial_budget_i)+
                            log(wins_project_quarter_stage)|
                                   action_date_year_quarter+
                       product_or_service_code+naics_code| # no fixed effects
                                   0| # no IV
                                   contract_award_unique_key, # clustered at project level
                                   data=reg_df_subset,
                                   exactDOF = TRUE,
                                   cmethod = "reghdfe")
four_way_interaction_table=stargazer(baseline_reg,
          controls_and_no_fe_no_age,
          controls_and_no_fe,
          controls_and_time_fe,
          controls_time_task_fe,
          controls_and_all_fe,
          digits=2,
          digits.extra=2,
          title = "Effect of Competition After QuickPay: Quickpay 2009-2011",
          dep.var.labels="$PercentDelay_{it}$  ",
          dep.var.caption = "",
          covariate.labels = c("$Treat_i$",
                               "$SA_i$",
                               "$Competitive_i$",
                               "$Post_t$",
                               "$Treat_i \\times Competitive_i$",
                               "$Post_t \\times Competitive_i$",
                               "$SA_i \\times Competitive_i$",
                               "$Treat_i \\times Post_t$",
                               "$Treat_i \\times Post_t \\times Competitive_i$",
                               "$Treat_i \\times Post_t \\times SA_i$",
                               "$Treat_i \\times Post_t \\times SA_i \\times Competitive_i$",
                               "Constant"),
          object.names=FALSE, 
          model.numbers=TRUE,
          font.size = "small",
          omit.stat=c("f", "ser"),
          column.sep.width = "-3pt",
          add.lines = list(
                           # c("Duration, Budget, Bids",rep("No",1),rep("Yes",5)),
                           # c("$Post_t \\times $  (Duration, Budget, Bids)",rep("No",1),rep("Yes",5)),
                           c("Project stage",rep("No",2),rep("Yes",4)),
                           c("Time fixed effects",rep("No",3),rep("Yes",3)),
                           c("Task fixed effects",rep("No",4),rep("Yes",2)),
                           c("Industry fixed effects",rep("No",5),rep("Yes",1))),
          omit=c(
                  # 'winsorized_initial_duration_in_days_i',
                  # 'winsorized_initial_budget_i',
                  #  'number_of_offers_received',
                  #  'post_t:winsorized_initial_duration_in_days_i',
                  #  'post_t:winsorized_initial_budget_i',
                  #  'post_t:number_of_offers_received',
                   'wins_project_quarter_stage'),
          table.placement = "H",
          style="default",
          notes=c("Each observation is a project-quarter.",
                  "SEs are robust and clustered at the project level."),
          header=F)
# 
# four_way_interaction_table_tex=make_tex_pieces(four_way_interaction_table)
# # Write to file
# write(four_way_interaction_table_tex,
#       paste0(tables_folder,"/four_way_interaction_table.tex"))
```
