---
title: "QuickPay Delay Rate -- All Defense Projects"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    keep_tex: false
    number_sections: true
header-includes:
 \usepackage{booktabs,longtable,dcolumn,makecell}
 \usepackage{multirow,array}
 \usepackage{wrapfig,float}
 \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages,warning=FALSE,message=FALSE,include=FALSE}
library(tidyverse)
library(dplyr)
library(pryr)
library(DescTools) 
library(zoo) # for year quarter
library(broom)
library(fixest)
library(data.table)
library(scales)
library(MatchIt)
```

```{r read_data,include=FALSE}
reg_df=readRDS("qp_delay_rates_all_action_types.Rds")

reg_df=setDT(reg_df)

nanda_naics=c("3329",
  "2362",
  "2379",
  "5311",
  "5612",
  "5629",
  "5415",
  "4831",
  "6114",
  "4812",
  "3149",
  "3325",
  "1153",
  "3333",
  "4247",
  "3159",
  "3162",
  "3169",
  "3366",
  "3112")

reg_df[,four_digit_naics:=substr(naics_code,1,4)]
projects_to_keep=fread('~/Dropbox/data_quickpay/qp_data/projects_to_keep.csv')

reg_df=reg_df[four_digit_naics%in%nanda_naics &
                contract_award_unique_key%in%projects_to_keep$contract_award_unique_key]

```

# QuickPay Expanded Sample

* Consider ALL defense projects that started b/w FY 2010 and FY 2012
* Only consider delays not caused by action types "D","A","L","G"
* Restrict to June 30, 2012 -- QP expanded to all projects after that

## 1. Competition

```{r competition, include=FALSE}
# Competition_i
reg_df[,action_date_year_quarter:=as.Date(action_date_year_quarter)]
reg_df[,competitively_awarded_i:=ifelse(!extent_competed_code%in%c("G","B", "C","NDO"),1,0)]

# A = FULL AND OPEN COMPETITION 
# B = NOT AVAILABLE FOR COMPETITION 
# C = NOT COMPETED 
# D = FULL AND OPEN COMPETITION AFTER EXCLUSION OF SOURCES 
# E = FOLLOW ON TO COMPETED ACTION 
# F = COMPETED UNDER SAP 
# G = NOT COMPETED UNDER SAP 
# CDO = COMPETITIVE DELIVERY ORDER 
# NDO = NON-COMPETITIVE DELIVERY ORDER

reg_df[,started_after_qp:=case_when(initial_start_date>=as.Date('2011-04-27') &
                                                   action_date_year_quarter>=as.Date('2011-04-27')~1,
                                                 initial_start_date<as.Date('2011-04-27') ~ 0,
                                                 initial_start_date>=as.Date('2011-04-27') &
                                                  action_date_year_quarter<as.Date('2011-04-27')~NaN)]

reg_df[,started_qtr:=as.Date(as.yearqtr(initial_start_date))]
```

### Bid Metrics

```{r bid_metrics, include=FALSE}

initial_bids=unique(reg_df[price_structure=="Fixed" &
                  competitively_awarded_i==1],by='contract_award_unique_key')

initial_bids=initial_bids[started_qtr>=as.Date('2009-12-31')&
                           started_qtr<= as.Date('2012-06-30')]

initial_bids[,wins_initial_duration:=Winsorize(initial_duration,
                                               probs=c(0.01,0.99),
                                               na.rm=T)]
initial_bids[,wins_initial_budget:=Winsorize(initial_budget,
                                               probs=c(0.01,0.99),
                                             na.rm=T)]
initial_bids[,wins_offers:=Winsorize(number_of_offers_received,
                                               probs=c(0.01,0.99),
                                     na.rm=T)]

m1=feols(wins_initial_duration~treat_new+
          started_after_qp:treat_new|product_or_service_code+started_qtr,
      cluster=~contract_award_unique_key,
      data=initial_bids)


m2=feols(I(wins_initial_budget/1000)~treat_new+
         started_after_qp:treat_new|product_or_service_code+started_qtr,
        cluster=~contract_award_unique_key,
        data=initial_bids)


m3=feols(wins_offers~treat_new+
        started_after_qp:treat_new|product_or_service_code+started_qtr,
        cluster=~contract_award_unique_key,
        data=initial_bids)

bid_metrics=list(m1,m2,m3)

etable(bid_metrics)
```

### Delays

```{r competition_delays,include=FALSE}
#### Competition delays ####
m1=feols(wins_percentage_delay~treat_new+
          post_t:treat_new+
          started_after_qp+
          treat_new:post_t:started_after_qp+
           post_t,
      cluster=~contract_award_unique_key,
      data=reg_df[price_structure=="Fixed"&
                      competitively_awarded_i==1])

m2=feols(wins_percentage_delay~treat_new+
          post_t:treat_new+
          started_after_qp+
          treat_new:post_t:started_after_qp+
          wins_project_quarter_stage+
           post_t,
      cluster=~contract_award_unique_key,
      data=reg_df[price_structure=="Fixed"&
                      competitively_awarded_i==1])

m3=feols(wins_percentage_delay~treat_new+
          post_t:treat_new+
          started_after_qp+
          treat_new:post_t:started_after_qp+
          wins_project_quarter_stage|
          action_date_year_quarter,
      cluster=~contract_award_unique_key,
      data=reg_df[price_structure=="Fixed"&
                      competitively_awarded_i==1])

m4=feols(wins_percentage_delay~treat_new+
          post_t:treat_new+
          started_after_qp+
          treat_new:post_t:started_after_qp+
          wins_project_quarter_stage|
          product_or_service_code+action_date_year_quarter,
      cluster=~contract_award_unique_key,
      data=reg_df[price_structure=="Fixed"&
                      competitively_awarded_i==1])

m5=feols(wins_percentage_delay~treat_new+
          post_t:treat_new+
          started_after_qp+
          treat_new:post_t:started_after_qp+
          wins_project_quarter_stage|
          product_or_service_code+
           action_date_year_quarter+
           naics_code,
      cluster=~contract_award_unique_key,
      data=reg_df[price_structure=="Fixed"&
                      competitively_awarded_i==1])


competition_delays=list(m1,m2,m3,m4,m5)
```

## 2. Project stage 

```{r stage, include=FALSE}

#### Project Stage ####
m1=feols(wins_percentage_delay~treat_new+
          post_t:treat_new+
          treat_new:wins_project_quarter_stage+
          treat_new:post_t:wins_project_quarter_stage+
          post_t:wins_project_quarter_stage+
          wins_project_quarter_stage+
           post_t,
      cluster=~contract_award_unique_key,
      data=reg_df[price_structure=="Fixed"])

m2=feols(wins_percentage_delay~treat_new+
          post_t:treat_new+
          treat_new:wins_project_quarter_stage+
          treat_new:post_t:wins_project_quarter_stage+
          post_t:wins_project_quarter_stage+        
          wins_initial_duration+
          wins_initial_budget+
          wins_offers+
          post_t:wins_initial_duration+
          post_t:wins_initial_budget+
          post_t:wins_offers+
          wins_project_quarter_stage+
           post_t,
      cluster=~contract_award_unique_key,
      data=reg_df[price_structure=="Fixed"])

m3=feols(wins_percentage_delay~treat_new+
          post_t:treat_new+
          treat_new:wins_project_quarter_stage+
          treat_new:post_t:wins_project_quarter_stage+
          post_t:wins_project_quarter_stage+        
          wins_initial_duration+
          wins_initial_budget+
          wins_offers+
          post_t:wins_initial_duration+
          post_t:wins_initial_budget+
          post_t:wins_offers+
          wins_project_quarter_stage|
           action_date_year_quarter,
         cluster=~contract_award_unique_key,
      data=reg_df[price_structure=="Fixed"])

m4=feols(wins_percentage_delay~treat_new+
          post_t:treat_new+
          treat_new:wins_project_quarter_stage+
          treat_new:post_t:wins_project_quarter_stage+
          post_t:wins_project_quarter_stage+        
          wins_initial_duration+
          wins_initial_budget+
          wins_offers+
          post_t:wins_initial_duration+
          post_t:wins_initial_budget+
          post_t:wins_offers+
          wins_project_quarter_stage|
          product_or_service_code+
           action_date_year_quarter,
         cluster=~contract_award_unique_key,
      data=reg_df[price_structure=="Fixed"])

m5=feols(wins_percentage_delay~treat_new+
          post_t:treat_new+
          treat_new:wins_project_quarter_stage+
          treat_new:post_t:wins_project_quarter_stage+
          post_t:wins_project_quarter_stage+        
          wins_initial_duration+
          wins_initial_budget+
          wins_offers+
          post_t:wins_initial_duration+
          post_t:wins_initial_budget+
          post_t:wins_offers+
          wins_project_quarter_stage|
          product_or_service_code+
           action_date_year_quarter+
           naics_code,
      cluster=~contract_award_unique_key,
      data=reg_df[price_structure=="Fixed"])

stage_regs=list(m1,m2,m3,m4,m5)
```

## 3. Congestion

```{r one_type_contractor, include=FALSE}
one_type_contractors=reg_df[,n_distinct(treat_i),by='recipient_duns']
one_type_contractors=unique(subset(one_type_contractors,V1==1 &
                                     !is.na(recipient_duns))$recipient_duns)

reg_df_one_type=subset(reg_df,recipient_duns%in%one_type_contractors)

reg_df_one_type[,wins_percentage_delay:=Winsorize(100*percentage_delay,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

reg_df_one_type[,wins_project_quarter_stage:=Winsorize(project_quarter_stage,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]

reg_df_one_type[,wins_initial_duration:=
                    Winsorize(initial_duration,
                    probs=c(0.05,0.95),
                    na.rm=T)]

# InitialBudget_i
reg_df_one_type[,wins_initial_budget:=
                    Winsorize(initial_budget,                    
                              probs=c(0.05,0.95),
                              na.rm=T)]
```

### Number of projects per contractor

* Contractors holding only small or only large projects

```{r num_projects_per_contractor,include=FALSE}

contractor_quarter=reg_df_one_type[price_structure=="Fixed",
                                   n_distinct(contract_award_unique_key),by=c('recipient_duns',
                                                            'action_date_year_quarter')]
setnames(contractor_quarter,'V1','num_projects')
contractor_quarter[,post_t:=ifelse(action_date_year_quarter>as.Date('2011-04-27'),1,0)]

contractor_quarter=merge(contractor_quarter,
                         unique(reg_df_one_type[,c('recipient_duns','treat_i')]),
                         by='recipient_duns')

contractor_quarter[,business_type:=ifelse(treat_i==1,"S","O")]

m1=feols(num_projects~treat_i+
          post_t:treat_i+post_t,
          cluster=~recipient_duns, # clustered at the contractor level
        data=contractor_quarter)

m2=feols(num_projects~treat_i+
          post_t:treat_i|action_date_year_quarter,
          cluster=~recipient_duns, # clustered at the contractor level
        data=contractor_quarter)

num_projects_per_contractor=list(m1,m2)
```

### Total budget per contractor

```{r budget_per_contractor,include=FALSE}
contractor_quarter=reg_df_one_type[price_structure=="Fixed",
                                   sum(wins_initial_budget),
                                   by=c('recipient_duns',
                                        'action_date_year_quarter')]
setnames(contractor_quarter,'V1','total_budget_across_projects')
contractor_quarter[,post_t:=ifelse(action_date_year_quarter>as.Date('2011-04-27'),1,0)]

contractor_quarter=merge(contractor_quarter,
                         unique(reg_df_one_type[,c('recipient_duns','treat_i')]),
                         by='recipient_duns')

contractor_quarter[,business_type:=ifelse(treat_i==1,"S","O")]

m1=feols(I(total_budget_across_projects/100000)~treat_i+
          post_t:treat_i+post_t,
         cluster=~recipient_duns, # clustered at the contractor level
        data=contractor_quarter)

m2=feols(I(total_budget_across_projects/100000)~treat_i+
          post_t:treat_i|action_date_year_quarter,
         cluster=~recipient_duns, # clustered at the contractor level
        data=contractor_quarter)

budget_per_contractor=list(m1,m2)
```

### Number of tasks per contractor

```{r task_per_contractor,include=FALSE}
contractor_quarter=reg_df_one_type[price_structure=="Fixed",
                                   n_distinct(product_or_service_code),
                                   by=c('recipient_duns',
                                        'action_date_year_quarter')]
setnames(contractor_quarter,'V1','number_of_tasks')
contractor_quarter[,post_t:=ifelse(action_date_year_quarter>as.Date('2011-04-27'),1,0)]

contractor_quarter=merge(contractor_quarter,
                         unique(reg_df_one_type[,c('recipient_duns','treat_i')]),
                         by='recipient_duns')

contractor_quarter[,business_type:=ifelse(treat_i==1,"S","O")]

m1=feols(number_of_tasks~treat_i+
          post_t:treat_i+post_t,
        cluster=~recipient_duns, # clustered at the contractor level
        data=contractor_quarter)

m2=feols(number_of_tasks~treat_i+
          post_t:treat_i|action_date_year_quarter,
        cluster=~recipient_duns, # clustered at the contractor level
        data=contractor_quarter)

task_per_contractor=list(m1,m2)
```

## 4. Contract Financing

```{r eval=FALSE, include=FALSE}
reg_df[,contract_financing_i:=ifelse(contract_financing_code%in%c("Z",""),0,1)]
# A = FAR 52.232-16 PROGRESS PAYMENTS 
# C = PERCENTAGE OF COMPLETION PROGRESS PAYMENTS 
# D = UNUSUAL PROGRESS PAYMENTS OR ADVANCE PAYMENTS 
# E = COMMERCIAL FINANCING 
# F = PERFORMANCE-BASED FINANCING 
# Z = NOT APPLICABLE

reg_df3=unique(reg_df[price_structure=="Fixed",c('contract_award_unique_key',
                                'recipient_duns',
                                'contract_financing_i')])

contract_financing_contractor=reg_df3[,.(num_projects_receiving_financing=
                                           sum(contract_financing_i)),
                                            by='recipient_duns']

num_projects_contractor=reg_df[price_structure=="Fixed",.(num_projects_contractor=
                                           n_distinct(contract_award_unique_key)),
                                      by='recipient_duns']

contract_financing_contractor=merge(contract_financing_contractor,
                                    num_projects_contractor,by='recipient_duns')                     

contract_financing_contractor[,pc_projects_receiving_cf:=100*num_projects_receiving_financing/num_projects_contractor]

# contract_financing_contractor[,above_median_cf:=ifelse(pc_projects_receiving_cf>median(subset(contract_financing_contractor,pc_projects_receiving_cf>0)$pc_projects_receiving_cf),1,0)]


reg_df=merge(reg_df,
                    contract_financing_contractor[,c('recipient_duns',
                                                     'pc_projects_receiving_cf')],
                    by='recipient_duns',
                    all.x=T)

a=reg_df[price_structure=="Fixed"]
a[,wins_percentage_delay:=Winsorize(delay,na.rm=T)]
feols(wins_percentage_delay~treat_new+
          (wins_project_quarter_stage)+
          post_t:treat_new+
          pc_projects_receiving_cf+
          treat_new:pc_projects_receiving_cf+
          post_t:pc_projects_receiving_cf+
          post_t:treat_new:pc_projects_receiving_cf+
          wins_initial_duration+
          wins_initial_budget+
          wins_offers+
          post_t:wins_initial_duration+
          post_t:wins_initial_budget+
          post_t:wins_offers|
          product_or_service_code+
          action_date_year_quarter,
      cluster=~contract_award_unique_key,
      data=a)
# 
# ggscatter(a, x = "treat_new", y = "pc_projects_receiving_cf", 
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "pearson",
#           xlab = "Miles/(US) gallon", ylab = "Weight (1000 lbs)")

```


# Export Tables

```{r dictionary, include=FALSE}
setFixest_dict(c("wins_percentage_delay"="Percentage delay rate",
                 "action_date_year_quarter"="Year-Quarter",
                 "wins_offers"="Number of bids",
                 "treat_new"="Treat", # Clean control group
                 "treat_i"="Treat",
                 "post_t"="Post",
                 "jobs_act"="JOBS act",
              "wins_initial_duration"="Initial duration\n (in days)",
              "wins_initial_budget"="Initial budget",
              "I(wins_initial_budget/1000)"="Initial budget\n (in 000s)",
              "wins_project_quarter_stage"="Project stage",
              "wins_offers"="Number of offers",
              "positive_delay"="I(Delay>0)",
              "negative_delay"="I(Delay<0)",
              "product_or_service_code"="Task",
              "I(total_budget_across_projects/1e+05)"="Total budget \n (in 00,000s)",
              "num_projects"="Number of projects",
              "number_of_tasks"="Number of tasks",
              "naics_code"="NAICS",
              "started_after_qp"="Started after QP",
              "started_qtr"="Started Quarter",
              "recipient_duns"="Contractor",
              "awarding_sub_agency_code"="Sub-agency",
              "contract_award_unique_key"="Project ID",
              "wins_initial_budget"="Initial budget"))
```

```{r congestion_table,echo=FALSE,results='asis'}
 etable(num_projects_per_contractor,
        budget_per_contractor,
        task_per_contractor,
       digits='r2',
       title="Congestion effect -- Full sample of Fixed Price Contracts",
       fontsize='footnotesize',
       tex=T)
```

```{r bids_table, echo=FALSE, results='asis'}
etable(bid_metrics,
       digits='r2',
       fontsize='footnotesize',
       title="Full sample of competitively-awarded fixed Price Contracts",
       tex=T)
```

```{r competition_delays_table, echo=FALSE, results='asis'}
etable(competition_delays,
       drop=c("Number of offers",
              "Initial duration",
              "Initial budget",
              "Project stage"),
       extralines = list("Controls"=c("No",rep("Yes",
                                        length(competition_delays)-1))),
       title="Full sample of competitively-awarded fixed Price Contracts",
       notes="Controls include initial budget, offers, duration, their interaction with post, and project stage.",
       digits='r2',
       fontsize='footnotesize',
       tex=T)
```

```{r stage_table, echo=FALSE, results='asis'}
etable(stage_regs,
       drop=c("Number of offers",
              "Initial duration",
              "Initial budget"),
       extralines = list("Controls"=c("No",rep("Yes",
                                        length(stage_regs)-1))),
       title="Full sample of Fixed Price Contracts",
       notes="Controls include initial budget, offers, duration, their interaction with post.",
       digits='r2',
       fontsize='footnotesize',
       tex=T)
```

